---
title: "02/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Experiment design

There are 4 independent animal groups, and 2 time points. The goal is to test difference between groups at every time point. Observations are proportions between 0 and 1, which suggests the proportion of bones that are formed. 


## two sample t test 


### use R package `pwr`

```{r, echo=F}
library(pwr)
# set effect size d=0.3
# pwr.t.test(n=10, d = 10, sig.level = 0.05, alternative = "greater")
```

### Use R package `power.t.test`

[power.t.test](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/power.t.test.html)


```{r, echo=F}
d=0.3; SD=0.2
#power.t.test(power = .80, delta = d, alternative = "one.sided", sig.level=0.05, sd=SD)
```

```{r, echo=F}
library(ggplot2)
d=seq(0.1, 1, by=0.1); SD=0.2
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "one.sided", sig.level=0.05, sd=SD)
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "blue")+
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=0.2")

```

```{r, echo=F}
d=0.1; SD=seq(0.1, 1, by=0.1)
sample_size=numeric()
for (i in 1:length(SD))
{
  test=power.t.test(power = .80, delta = d, alternative = "one.sided", sig.level=0.05, sd=SD[i])
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(SD, sample_size), aes(x=SD, y=sample_size, group=1)) +
  geom_line(color="red")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "blue")+
  geom_point()+
  xlab("SD:standard deviation")+
  ylab("n:sample size")+
  ggtitle("power=0.8; mean diffrence d=0.1")
```

#### Parameter settings in the experiement 

```{r, echo=T}
d=0.3; SD=0.15 
power.t.test(power = .80, delta = d, alternative = "two.sided", sig.level=0.05, sd=SD)
power.t.test(n=5, delta = d, alternative = "two.sided", sig.level=0.05, sd=SD)
power.t.test(n=10, delta = d, alternative = "two.sided", sig.level=0.05, sd=SD)
```


```{r, echo=T, eval=F}
For power analysis, we have used function-power.t.test in statistical software R version 4.1.2 to calculate sample size required to achieve desired power, with  Type 1 error probability of 0.05. With group mean difference 30% and standard variation of 15%, at least 5 animals /group/time points are needed to obtain 80% power, and it will be significantly increased to 98% when there are 10  animals /group/time point. 
```

### use formular 

use formular in [this paper](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3826013/)

$sample-size=2*SD^2(1.96+0.842)^2/d^2$

```{r, echo=F}
d=0.3; SD=0.2
n=2*SD^2*(1.96+0.842)^2/d^2

```

### manual calculation 

```{r, echo=F}
mean=1.65; p_a=0.3; sample_size=7; SD=0.2

power=1-pnorm(1.65-p_a/(SD/sqrt(5)))

```