---
title: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## study 1

### Problem setting: 

there are 3 groups and bone width will be measured before surgery and 4 months after. It aims to test if there is change between pro-surgery and post surgery within each group and across different groups 


### two paired sample  t test to test within group different 


```{r, echo=F, message=F, warning=F}
library(ggplot2)
d=seq(0.1, 1, by=0.01); SD=0.2
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="paired") # paired two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  #geom_vline(xintercept=0.13, colour="blue") +
  #geom_text(aes(x=0.13, label="d=0.13", y=10), colour="blue", angle=90, vjust = 1.2, text=element_text(size=11))+
  #geom_hline(yintercept=21, colour="blue") +
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=0.2")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

```

* use `power.t.test` with option `alternative = "two.sided"`, `type="paired"`


### two sample t test to test between group different



```{r, echo=F, message=F, warning=F}
library(ggplot2)
d=seq(0.1, 1, by=0.01); SD=0.2
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="two.sample") # two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  #geom_vline(xintercept=0.13, colour="blue") +
  #geom_text(aes(x=0.13, label="d=0.13", y=10), colour="blue", angle=90, vjust = 1.2, text=element_text(size=11))+
  #geom_hline(yintercept=21, colour="blue") +
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=0.2")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

```


* use `power.t.test` with option `alternative = "two.sided"`, `type="two.sample"`


## study 3: sample size calculation 

### Problem setting

two samples: group 1 and 2 are matched, like case control sample. Observed samples are pain evaluations, numerical number between 0 and 100. Individuals are measured at multiple occasions, before surgery, during surgery, 1-day, 2-day, 3-day, 4-day, 5-day, 6-day, 7-day, and 14-day.  




### paired two sample t test by function `power.t.test`

When look at one single occasion, two sample paired t test could be used. 


[power.t.test](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/power.t.test.html)


two paired sample t-test works for case-control studies or repeated-measures designs, e.g. before and after an experiment. 

* use `power.t.test` with option `alternative = "two.sided"`, `type="paired"`
* when mean difference is 0.13, standard deviation is 0.2, 21 subjects are required to achieve 80% power. 


```{r, echo=F, message=F, warning=F}
library(ggplot2)
d=seq(0.1, 1, by=0.01); SD=0.2
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="paired") # paired two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  geom_vline(xintercept=0.13, colour="blue") +
  geom_text(aes(x=0.13, label="d=0.13", y=10), colour="blue", angle=90, vjust = 1.2, text=element_text(size=11))+
  geom_hline(yintercept=21, colour="blue") +
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=0.2")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

```


## statistical software 

```{r, echo=F}
R.version
```