---
title: "10/17/2022"
output: html_document
date: '2022-10-17'
---


```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
set.seed(123)
```


```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
```


## trueness

```{r, echo=F, message=F, warning=F}
trueness=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_trueness.csv", header=T))
methods2=c("FGAS_LS", "FGAS_IOS", "FGAS_CBCT", "FHAS_LS", "FHAS_IOS", "FHAS_CBCT")
trueness=trueness %>% mutate(methods=rep(methods2, each=20)) # add new column with unique sample ID's 
```

### anova test 

```{r, echo=F, message=F, warning=F}
ggplot(trueness, aes(x=methods, y=Angle, fill=methods)) +
  geom_boxplot()

LM <- lm(Angle~ methods, data=trueness)
anova(LM)

#summary(LM)

```

* small p value, `2.097e-09` suggests `Angle` are not ALL equal across 6 methods

#### anova test for `FGAS`

```{r, echo=F, message=F, warning=F}
anova(lm(Angle~ methods, data=trueness[1:60,]))
```


#### anova test for `FHAS`

```{r, echo=F, message=F, warning=F}
anova(lm(Angle~ methods, data=trueness[61:120,]))
```


### Cronbach’s Alpha test 

```{r, echo=F, message=F, warning=F}
library(ltm)

FGAS_Angle=data.frame(FGAS_CBCT=trueness %>% filter(methods=="FGAS_CBCT") %>% dplyr::select(Angle) %>% pull, FGAS_IOS=trueness %>% filter(methods=="FGAS_IOS") %>% dplyr::select(Angle) %>% pull, FGAS_LS=trueness %>% filter(methods=="FGAS_LS") %>% dplyr::select(Angle) %>% pull) # dplyr::select  use select function from package dplyr 
#FGAS_Angle=data.frame(FGAS_CBCT=trueness$Angle[41:60], FGAS_IOS=trueness$Angle[21:40], FGAS_LS=trueness$Angle[1:20])
FGAS_alpha=cronbach.alpha(FGAS_Angle)
FGAS_alpha$alpha

FHAS_Angle=data.frame(FHAS_CBCT=trueness %>% filter(methods=="FHAS_CBCT") %>% dplyr::select(Angle) %>% pull, FHAS_IOS=trueness %>% filter(methods=="FHAS_IOS") %>% dplyr::select(Angle) %>% pull, FHAS_LS=trueness %>% filter(methods=="FHAS_LS") %>% dplyr::select(Angle) %>% pull) # dplyr::select  use select function from package dplyr
#FHAS_Angle=data.frame(FHAS_CBCT=trueness$Angle[101:120], FHAS_IOS=trueness$Angle[81:100], FHAS_LS=trueness$Angle[61:80])

FHAS_alpha=cronbach.alpha(FHAS_Angle)
FHAS_alpha$alpha

########################
#library(psych)
#alpha(FGAS_Angle)
#alpha(FHAS_Angle)
```


### pairwise comparisons 

```{r, echo=F, message=F, warning=F}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(Angle)%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(Angle)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* non paired two sample t test is used 

* `mean_difference` is mean difference of `group1-group2`


## precision 



```{r, echo=F, message=F, warning=F}
precision=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_precision.csv", header=T))

precision_angle=precision %>%  dplyr::select(ends_with("Angle")) %>% slice_tail(n = 191) # the last 191 rows as precision 
methods3=colnames(precision_angle)
precision_angle_long=data.frame(vs_distance=c(precision_angle$FG.LS.Angle, precision_angle$FG.IOS.Angle, precision_angle$FG.CBCT.Angle, precision_angle$FH.LS.Angle, precision_angle$FH.IOS.Angle, precision_angle$FH.CBCT.Angle), methods=rep(methods3, each=191))
```



### anova test 

```{r, echo=F, message=F, warning=F}
ggplot(precision_angle_long, aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()

LM <- lm(vs_distance~ methods, data=precision_angle_long)
anova(LM)

#summary(LM)

```

* p value `7.445e-12` indicates strong evidence of non-equal vs distance across 6 methods. 


### pairwise comparisons 

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_angle_long %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_angle_long %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* two sample t test is used 
* `mean_difference` is mean difference of `group1-group2`
