---
title: '2022'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## projects 


1. [Feb-Cem](2022_Feb.html)
2. [Feb-Lobat](2022_Feb2.html)
3. [Feb-Essa](2022_Feb3.html)
4. [Feb-Soni](2022_Feb4.html)
5. [Feb-Mohamed](2022_Feb5_Lauren.html)
6. [Mar-Lisa](2022_Mar1_Lisa.html)
7. [Mar-Marinho](2022_Mar2_Marinho.html)
8. [Mar-Kate](2022_Mar3_kate.html)
9. [Apr-Kofina](2022_Apr1_Kofina.html)
10. [Apr-Megan](2022_Apr2_Megan.html)
11. [May-shuwei](2022_May1_Shuwei.html)
12. [May-Mariana](2022_May2_Mariana.html)
13. [Jun-Jacob](2022_Jun1_Jacob.html)
14. [Jun-Scott](2022_Jun2_Scott.html)
15. [Sep-Juan](2022_Sep1_Juan.html)
16. [Sep-Vidya](2022_Sep2_Vidya.html)
17. [Sep-Chloe](2022_Sep3_Chole.html)
18. [Oct-Ajitesh](2022_Oct1_Ajitesh.html)
19. [Dec-Teerarat](2022_DEc1_Teerarat.html)
20. [Dec-Kelley](2022_Dec2_Kelley.html)
21. [Dec-Arndt](2022_Dec3_Arndt.html)

##  progress 


```{r, echo=F, message=F, warning=F}
###### https://rstudio-pubs-static.s3.amazonaws.com/215319_ac67755c296b441dac7b24b48fc30156.html
project_progress=data.frame(project=seq(1,21), progress=c(100, 100, 100, 100, 100, 100, 100, 100, 100, 100, 100, 100,100,100,100, 100,90, 70,0,0,0))
bp.y <- ggplot(data =project_progress, aes(x = factor(project), y = progress)) + 
    geom_bar(stat = "identity", aes(fill = progress))+ 
  labs(x = "project")+
  geom_text(aes(label=progress), position=position_dodge(width=0.8), vjust=0.25, color="black")+  # add numbers over bars+
coord_flip()+ 
 theme_gray() +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank(),
          axis.ticks.x = element_blank(), axis.text.y = element_text(size = 13), 
          axis.title.y = element_text(size = 12, margin = margin(0,10,0,0), angle =90 ), # this adjusts "project" on y axis 
          legend.position="none") + 
    scale_fill_distiller(name = "progress", palette = "Reds", direction = 1) + 
  theme(legend.position = "right", legend.direction = "vertical",
          legend.title = element_text(size = 15), legend.key.size = unit(1,"cm"),
          legend.text = element_text(size = 7))+
  ggtitle("as of 11/1/2022")+  # add title information 
  theme(plot.title = element_text(hjust = 0.5, size=15)) #center the title
bp.y
```


```{r, echo=F, message=F, warning=F, eval=F}
project_progress=data.frame(project=seq(1,11), progress=c(100, 100, 100, 90, 50, 80, 100, 60, 60, 90, 70))

bp.x <- ggplot(data = project_progress, aes(x = factor(project), y = progress)) + 
    geom_bar(stat = "identity", aes(fill = progress)) + theme_gray() +
  geom_text(aes(label=progress), position=position_dodge(width=0.9), vjust=-0.25)+  # add numbers over bars+
    labs(x = "project")+
   labs(y="progress (% approx)")+
  scale_fill_distiller(name = "progress", palette = "Reds", direction = 1, na.value = "transparent") +
    scale_x_discrete(breaks = seq(1,11), labels = seq(1,11)) + # list all x labels 
    theme(legend.position = "right", legend.direction = "vertical",
          legend.title = element_text(size = 15), legend.key.size = unit(1,"cm"),
          legend.text = element_text(size = 7))+
  ggtitle("as of 5/19/2022")+
  theme(plot.title = element_text(hjust = 0.5, size=15)) #center the title 
bp.x
```






