---
title: "12/16/2022"
output: html_document
date: '2022-12-16'
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr) # combine and arrange multiple 
library(kableExtra)
library(rstatix) # use anova_test function 
library(DT)
set.seed(123)
```

```{r, echo=F, warning=F, message=F}
data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202212\\Arndt\\Trueness_CompareStudies_2022_ALL DATA.csv", header=T))
# based on sleeveheight, split into 3 different balanced groups, low mediam, high, and then for each group, regress angle to sleeveheight and drillguidance   
```


## SleeveHeight


```{r, echo=F, message=F, warning=F}
  

p=ggplot(data.frame(var=rep("SleeveHeight", 140), SleeveHeight=data$SleeveHeight), aes(x=var, y=SleeveHeight))+
  geom_boxplot()
p+geom_dotplot(binaxis='y', stackdir='center', dotsize=0.6)+
  ggtitle("boxplot of SleeveHeight")+
  theme(plot.title = element_text(hjust = 0.5, size=15)) # center the title

quantile(data$SleeveHeight, probs=c(0, 0.33, 0.66,1))
```
### SleeveHeight<=3.5

* based on `SleeveHeight`, split into 3 groups (1) `SleeveHeight<=3.5`, 60 observations (2) `SleeveHeight>3.5 & SleeveHeight<=5`, 40 observations (3) `SleeveHeight>5`, 40 observations 


```{r, echo=F, message=F, warning=F}
sub_data=data%>%filter(SleeveHeight<=3.5)
reg=lm(Angle~SleeveHeight+DrillGuidance, sub_data)
SleeveHeight=sub_data%>%select(SleeveHeight) %>% pull()
DrillGuidance=sub_data%>% select(DrillGuidance) %>% pull()
#cor(SleeveHeight,DrillGuidance)
#summary(reg)
#confint(reg, 'SleeveHeight', level=0.95)

ggplot(sub_data, aes(x=SleeveHeight, y=Angle)) +   # add regression line 
  geom_point()+
  geom_smooth(method=lm)

```


* SleeveHeight=DrillGuidance, only one variable is effective 



### SleeveHeight>3.5 & SleeveHeight<=5

```{r, echo=F, message=F, warning=F}
sub_data=data%>%filter(SleeveHeight>3.5 & SleeveHeight<=5)
reg=lm(Angle~SleeveHeight+DrillGuidance, sub_data)
SleeveHeight=sub_data%>%select(SleeveHeight) %>% pull()
DrillGuidance=sub_data%>% select(DrillGuidance) %>% pull()
#cor(SleeveHeight,DrillGuidance)
#summary(reg)
#confint(reg, 'SleeveHeight', level=0.95)

ggplot(sub_data, aes(x=SleeveHeight, y=Angle)) +   # add regression line 
  geom_point()+
  geom_smooth(method=lm)
```

* correlation between SleeveHeight and DrillGuidance is 1. 

### SleeveHeight>5 

```{r, echo=F, message=F, warning=F}
sub_data=data%>%filter(SleeveHeight>5)
reg=lm(Angle~SleeveHeight+DrillGuidance, sub_data)
SleeveHeight=sub_data %>% select(SleeveHeight) %>% pull()
DrillGuidance=sub_data %>% select(DrillGuidance) %>% pull()
#cor(SleeveHeight,DrillGuidance)
#summary(reg)
#confint(reg, 'SleeveHeight', level=0.95)

ggplot(sub_data, aes(x=SleeveHeight, y=Angle)) +   # add regression line 
  geom_point()+
  geom_smooth(method=lm)
```




```{r, echo=F, message=F, warning=F}
group=rep(NA, nrow(data))
group[which(data$SleeveHeight<=3.5)]="Sleeve Height<=3.5"
group[which(data$SleeveHeight>3.5 & data$SleeveHeight<=5)]="Sleeve Height>3.5 & Sleeve Height<=5"
group[which(data$SleeveHeight>5)]="Sleeve Height>5"
data_with_group=data%>%mutate(group=group)
ggplot(data_with_group, aes(x=SleeveHeight, y=Angle, color=group, shape=group)) +
  geom_point() + 
  xlab("Sleeve Height (mm)")+ylab("Angle (mm)")+
  geom_smooth(method=lm)+
  theme(legend.position="bottom")
```

* "We use 3.5mm and 5mm as cutoff to split 140 data points to 3 groups. In each group, apply linear regression model with Angle as response and sleeve height as predictor. Coefficient estimates are presented in the Table and regression lines are shown in the graph. From parameter estimate in the table, when sleeve height is less than or equal to 3.5mm, 1mm increase in sleeve height will result in 3.57mm decrease for angle, however, when sleeve height is larger than 6mm, 1mm increase in sleeve height leads to 0.09mm increase in angle.  "


```{r, echo=F, message=F, warning=F}
parameter_estimate=c(-3.57, -1.03, 0.09)
confidence_low=c(-5.24, -1.72, -1.46)
confidence_upper=c(-1.90, -0.34, 1.65)
group=c("SleeveHeight<=3.5", "Sleeve Height>3.5 & Sleeve Height<=5","Sleeve Height>5")
pvalue=c("7.06e-05", "0.004240", "0.903")

data.frame(group=group, SleeveHeight_coefficient=parameter_estimate, CI_low=confidence_low, CI_upper=confidence_upper, pvalue=pvalue) %>% datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### two groups 


```{r, echo=F, message=F, warning=F}
group=rep(NA, nrow(data))
group[which(data$SleeveHeight<=4)]="Sleeve Height<=4"
group[which(data$SleeveHeight>4)]="Sleeve Height>4"
data_with_group=data%>%mutate(group=group)
ggplot(data_with_group, aes(x=SleeveHeight, y=Angle, color=group, shape=group)) +
  geom_point() + 
  xlab("Sleeve Height (mm)")+ylab("Angle (mm)")+
  geom_smooth(method=lm)+
  theme(legend.position="bottom")
```

```{r, echo=F, message=F, warning=F}
Angle_mean=numeric(); SleeveHeight_cutoff=c(3,3.5,4,5,6,6.25)
Angle_se=numeric()
for (i in 1:length(SleeveHeight_cutoff))
{
  obs=data %>% filter(SleeveHeight==SleeveHeight_cutoff[i]) %>% select(Angle) %>% pull()
 Angle_mean[i]=mean(obs)
 Angle_se[i]=sd(obs)/sqrt(length(obs))
}

ggplot(data, aes(x=SleeveHeight, y=Angle)) + geom_point() +
  xlab("Sleeve Height (mm)")+ylab("Angle (mm)")+
  stat_summary(aes(y = Angle,group=1), fun.y=mean, colour="red", geom="line",group=1)#+
  #geom_errorbar(aes(ymin=Angle_mean-Angle_se, ymax=Angle_mean+Angle_se), width=.1)
```


```{r, echo=F, message=F, warning=F, eval=F}
sub_data=data%>%filter(SleeveHeight<=4)
reg=lm(Angle~SleeveHeight, sub_data)
SleeveHeight=sub_data %>% select(SleeveHeight) %>% pull()
DrillGuidance=sub_data %>% select(DrillGuidance) %>% pull()
#cor(SleeveHeight,DrillGuidance)
summary(reg)
confint(reg, 'SleeveHeight', level=0.95)
```


```{r, echo=F, message=F, warning=F, eval=F}
sub_data=data%>%filter(SleeveHeight>4)
reg=lm(Angle~SleeveHeight, sub_data)
SleeveHeight=sub_data %>% select(SleeveHeight) %>% pull()
DrillGuidance=sub_data %>% select(DrillGuidance) %>% pull()
#cor(SleeveHeight,DrillGuidance)
summary(reg)
confint(reg, 'SleeveHeight', level=0.95)
```



```{r, echo=F, message=F, warning=F}
parameter_estimate=c(-2.06, 0.30)
confidence_low=c(-3.03, 0.04)
confidence_upper=c(-1.09, 0.56)
group=c("SleeveHeight<=4", "SleeveHeight>4")
pvalue=c("6.63e-05", "0.0245")

data.frame(group=group, SleeveHeight_coefficient=parameter_estimate, CI_low=confidence_low, CI_upper=confidence_upper, pvalue=pvalue) %>% datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


## CAM vs STM 

```{r, echo=F, message=F, warning=F}
CAM_angle=data$Angle[81:100]
STM_angle=data$Angle[101:120]

######### calculate power 
#power.t.test(delta =(mean(CAM_angle)-mean(STM_angle)), alternative = "two.sided", sig.level=0.05, sd=2, n=20, type="two.sample")

########### calculate effect size 
library(effsize)

#cohen.d(CAM_angle, STM_angle)
```

* CAM: Camlog, STM:Straumann
* power: when n=20, mean difference=mean(CAM_angle)-mean(STM_angle), sd=2, power=0.99 and when sd=0.4, power=1 => sample size of 20 is more than enough to have power 80%.  

* effect size: Cohen's d is 2.13, average angle deviation (AD) of CAM is 2.13 standard deviations greater than the average AD of STM.

## statistical software 

```{r, echo=F}
R.version
```