---
title: "9/14/2022"
output: html_document
date: '2022-09-14'
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
set.seed(123)
```


```{r, echo=F, warning=F, message=F}
data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202209\\Juan\\Research Valencia-Kofina implants.csv"))
```

## Age 

```{r, echo=F, message=F, warning=F}
p=ggplot(data.frame(var=rep("Age", 23), Age=data$Age), aes(x=var, y=Age))+
  geom_boxplot()
p+geom_dotplot(binaxis='y', stackdir='center', dotsize=0.6)+
  ggtitle("boxplot of Age")+
  theme(plot.title = element_text(hjust = 0.5, size=15)) # center the title


#round(mean(data$Age),2) # mean 
#round(sd(data$Age),2)  # sd 
#round(sd(data$Age)/sqrt(nrow(data)),2) # se
#min(data$Age) # minimum 
#max(data$Age) # maximum 
```




| Mean      | SD |   SE    | Range
| :---        |    :----:   |   :----:   |        ---: |
| 59.39    | 13.17   | 2.75   | (32, 73) |



## Gender 

```{r, echo=F, message=F, warning=F}
g1=ggplot(data %>% count(Gender) %>%mutate(prop=n/nrow(data)), aes(x=as.factor(Gender), y=prop, fill=as.factor(Gender))) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab("Gender (%)")+ylim(c(0,1))+
  xlab("Gender: 1=male, 2=female")+
  geom_text(aes(label=round(prop,2)*100), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title 

g2=ggplot(data %>% count(Gender), aes(x=as.factor(Gender), y=n, fill=as.factor(Gender))) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab("Gender")+
  xlab("Gender: 1=male, 2=female")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title 

figure <- ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
figure

gender_count=data %>% count(Gender) %>% select(n) %>% pull
binom.test(gender_count[1], sum(gender_count), p = 0.5)
```

* large p value of 0.4 suggests no difference between gender. 


## Race 


```{r, echo=F, warning=F, message=F}
g1=ggplot(data %>% count(Race) %>%mutate(prop=n/nrow(data)), aes(x=as.factor(Race), y=prop, fill=as.factor(Race))) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab("Race (%)")+ylim(c(0,1))+
  xlab("Race: 1=white, 2=Hispanic, 5=African American")+
  geom_text(aes(label=round(prop,2)*100), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title 

g2=ggplot(data %>% count(Race), aes(x=as.factor(Race), y=n, fill=as.factor(Race))) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab("Race")+
  xlab("Race: 1=white, 2=Hispanic, 5=African American")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

figure <- ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
figure

```

* sample size is not large enough to test the difference 


## _T1, _T2, _T3, _T4, _T5 and _T6


### trajectory plot 

```{r, echo=F, message=F, warning=F}
data_long=data.frame(Width_3mm=c(data$Width_3mm_T1, data$Width_3mm_T2, data$width_3mm_T3, data$Width_3mm_T4, data$Width_3mm_T5, data$Width_3mm_T6), time=rep(c("T1", "T2", "T3", "T4", "T5", "T6"), each=nrow(data)), individual=rep(data$Subject,6))

g1=ggplot(data=data_long,aes(x=time, y=Width_3mm, group=individual))+
  geom_line(color="red")+
  geom_point() # look at total PBI 


g2=ggplot(data.frame(Width_3mm_mean=c(mean(data$Width_3mm_T1),mean(data$Width_3mm_T2), mean(data$width_3mm_T3), mean(data$Width_3mm_T4), mean(data$Width_3mm_T5), mean(data$Width_3mm_T6)), time=c("T1", "T2", "T3", "T4", "T5", "T6")), aes(x=time, y=Width_3mm_mean, group=1))+
  ylim(c(min(data_long$Width_3mm), max(data_long$Width_3mm)))+
  geom_line(color="red")+
  geom_point()

figure <- ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
figure 

# data_long %>% filter(time=="T1") %>% summarise(mean=round(mean(Width_3mm),4), SD=round(sd(Width_3mm),4), se=round(SD/23,4), min=round(min(Width_3mm),4), max=round(max(Width_3mm), 4)) 
```




| Time | Mean      | SD |   SE    | Range
| :---        |    :----:   |   :----:   |        ---: |  :----:   |
|T1|     11.4351 |  1.7104|  0.0744|  (8.355, 14.7525)
|T2| 12.931 | 1.9366 | 0.0842 |  (8.7887, 17.1403)
|T3| 14.6584 |  1.83 | 0.0796 |  (11.3884, 19.5114)
|T4| 13.6529 | 1.8681 | 0.0812 | (9.4339, 18.0086)
|T5| 13.0122 | 1.9005 |0.0826 | (9.05, 17.1613)
|T6| 11.6519 | 1.6879 | 0.0734 | (8.7593, 14.8067)






### pairwise comparisons




```{r, echo=F, message=F, warning=F}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:6)
 for (j in 1:6)
{
  ii=ii+1
  samplei=data[,(5+i)] %>% pull
  samplej=data[,(5+j)] %>% pull
  test=t.test(samplei, samplej, paired=T)
  estimate[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[6:11], each=6), group2=rep(colnames(data)[6:11],6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,2))  
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result %>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```

* use paired two sample t test 


### test different across all time points 

```{r, echo=F, message=F, warning=F}

res.aov <- anova_test(data = data_long, dv =Width_3mm , wid = individual, within = time)
get_anova_table(res.aov)
```


* use repeated anova test 

* small p value indicates significant change over time 

## _T2-T1, T3-T2, T4-T2,  T5-T2 and T6-T2

### Width_diff_3mm





```{r, echo=F, message=F, warning=F}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric(); 
SD=numeric(); SE=numeric(); minimum=numeric(); maximum=numeric()
for (i in 1:5)
{
  current=data[,(11+i)] %>% pull
  test=t.test(current)
  estimate[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
  
  SD[i]=sd(current)
  SE[i]=SD/length(current)
  minimum[i]=min(current)
  maximum[i]=max(current)
}
data_frame(parameter=colnames(data)[12:16], mean=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4), SD=round(SD,4), SE=round(SE,4),  minimum=round(minimum,4),  maximum=round(maximum, 4)) %>%
  kbl() %>%
  kable_styling()
```

* use one sample t test to test each paramert is equal to 0 or not





```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:5)
  for (j in 1:5)
{
  ii=ii+1
  group1=data[,(11+i)] %>% pull
  group2=data[,(11+j)] %>% pull
  test=t.test(group1, group2, paired=T)
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[12:16],each=5), group2=rep(colnames(data)[12:16],5), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4)) 
result$group1[c(2:5, 7:10, 12:15, 17:20, 22:25)]="---"
result%>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```


### Buccal_3mm

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
SD=numeric(); SE=numeric(); minimum=numeric(); maximum=numeric()
for (i in 1:5)
{
  current=data[,(16+i)] %>% pull
  test=t.test(current)
  estimate[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
  
  SD[i]=sd(current)
  SE[i]=SD/length(current)
  minimum[i]=min(current)
  maximum[i]=max(current)
}
data_frame(parameter=colnames(data)[17:21], mean=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4), SD=round(SD,4), SE=round(SE,4),  minimum=round(minimum,4),  maximum=round(maximum, 4))%>%
  kbl() %>%
  kable_styling()
```


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:5)
  for (j in 1:5)
{
  ii=ii+1
  group1=data[,(16+i)] %>% pull
  group2=data[,(16+j)] %>% pull
  test=t.test(group1, group2, paired=T)
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[17:21],each=5), group2=rep(colnames(data)[17:21],5), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4)) 

result$group1[c(2:5, 7:10, 12:15, 17:20, 22:25)]="---"
result%>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```


### Lingual_3mm


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
SD=numeric(); SE=numeric(); minimum=numeric(); maximum=numeric()

for (i in 1:5)
{
  current=data[,(21+i)] %>% pull
  test=t.test(current)
  estimate[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
  
  SD[i]=sd(current)
  SE[i]=SD/length(current)
  minimum[i]=min(current)
  maximum[i]=max(current)
}
data_frame(parameter=colnames(data)[22:26], mean=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4), SD=round(SD,4), SE=round(SE,4),  minimum=round(minimum,4),  maximum=round(maximum, 4))%>%
  kbl() %>%
  kable_styling()
```


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:5)
  for (j in 1:5)
{
  ii=ii+1
  group1=data[,(21+i)] %>% pull
  group2=data[,(21+j)] %>% pull
  test=t.test(group1, group2, paired=T)
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[22:26],each=5), group2=rep(colnames(data)[22:26],5), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4)) 

result$group1[c(2:5, 7:10, 12:15, 17:20, 22:25)]="---"
result%>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```



###  Vertical_mid


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
SD=numeric(); SE=numeric(); minimum=numeric(); maximum=numeric()
for (i in 1:5)
{
  current=data[,(26+i)] %>% pull
  test=t.test(current)
  estimate[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
  
  SD[i]=sd(current)
  SE[i]=SD/length(current)
  minimum[i]=min(current)
  maximum[i]=max(current)
}
data_frame(parameter=colnames(data)[27:31], mean=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4), SD=round(SD,4), SE=round(SE,4),  minimum=round(minimum,4),  maximum=round(maximum, 4))%>%
  kbl() %>%
  kable_styling()  
```




```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:5)
  for (j in 1:5)
{
  ii=ii+1
  group1=data[,(26+i)] %>% pull
  group2=data[,(26+j)] %>% pull
  test=t.test(group1, group2, paired=T)
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[27:31],each=5), group2=rep(colnames(data)[27:31],5), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4)) 

result$group1[c(2:5, 7:10, 12:15, 17:20, 22:25)]="---"
result%>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```



###  Vertical_max


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
SD=numeric(); SE=numeric(); minimum=numeric(); maximum=numeric()
for (i in 1:5)
{
  current=data[,(31+i)] %>% pull
  test=t.test(current)
  estimate[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
  
  SD[i]=sd(current)
  SE[i]=SD/length(current)
  minimum[i]=min(current)
  maximum[i]=max(current)
}
data_frame(parameter=colnames(data)[32:36], mean=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4), SD=round(SD,4), SE=round(SE,4),  minimum=round(minimum,4),  maximum=round(maximum, 4))%>%
  kbl() %>%
  kable_styling()  
```



```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:5)
  for (j in 1:5)
{
  ii=ii+1
  group1=data[,(31+i)] %>% pull
  group2=data[,(31+j)] %>% pull
  test=t.test(group1, group2, paired=T)
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
}
result=data_frame(group1=rep(colnames(data)[32:36],each=5), group2=rep(colnames(data)[32:36],5), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=round(p_value,4)) 

result$group1[c(2:5, 7:10, 12:15, 17:20, 22:25)]="---"
result%>%
  kbl() %>%
  kable_styling()%>%
scroll_box(height = "300px")
```