---
title: "2/24/2022"
output: html_document
---

```{r setup, include=FALSE}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
```

```{r, echo=F, message=F, warning=F, results=F}
data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202202\\Mohamed\\D3_ENDO_Clicker_Survey_(Responses)_coded.csv", fileEncoding = "Latin1"))

data_2024=as_tibble(multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202202\\Mohamed\\Coded Responses – 2024.xlsx")[[1]])

data_2025=as_tibble(multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202202\\Mohamed\\Coded Responses – 2025.xlsx")[[1]])

```

## section 1



```{r, echo=F, message=F, warning=F}
questions_index=c(1,3)
questions=colnames(data)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{ # i=1
  response=data[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  figures[[i]]=
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
#g1
  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
} # for (i in 1:length(questions))
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]


annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
```

* [binomial exact test](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/binom.test.html) is used to test if pairwise occurrence rate is equal or not 


* pairwise p values are shown in matrix, for instance p value between `Disagree` and `Neutral` is 0.1796. 

## section 2

```{r, echo=F, message=F, warning=F}
questions_index=c(5,7, 9,11,13,15)
questions=colnames(data)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
   
if (i<=4)
  {   g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
}
  if (i>4)
  {
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
    
  }
  
  figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
annotate_figure(figures[[6]], top = text_grob(paste(questions[6])))
p_value_list[[6]]
```



## section 3

```{r, echo=F, message=F, warning=F}
questions_index=c(17,19, 21,23,25)
questions=colnames(data)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
     
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)  # add numbers over bars
   
 g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  
 figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
 
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
```

## section 4

```{r, echo=F, message=F, warning=F}
questions_index=c(27,29, 31,33, 35)
questions=colnames(data)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
  
  g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)  # add numbers over bars
  
  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  
 figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
```

## 2024 


### section 1 




```{r, echo=F, message=F, warning=F}
questions_index=c(1,3,5)
questions=colnames(data_2024)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{ # i=1
  response=data_2024[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2024)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  figures[[i]]=
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
#g1
  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
} # for (i in 1:length(questions))
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]


annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]


annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
```



### section 2

```{r, echo=F, message=F, warning=F}
questions_index=c(5,7, 9,11,13,15)+2
questions=colnames(data_2024)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data_2024[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2024)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
   
if (i<=4)
  {   g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
}
  if (i>4)
  {
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
    
  }
  
  figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
annotate_figure(figures[[6]], top = text_grob(paste(questions[6])))
p_value_list[[6]]
```


### section 3

```{r, echo=F, message=F, warning=F}
questions_index=c(17,19, 21,23,25)+2
questions=colnames(data_2024)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data_2024[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2024)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
     
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)  # add numbers over bars
   
 g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  
 figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
 
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
```


### section 4

```{r, echo=F, message=F, warning=F}
questions_index=c(27,29, 31,33, 35)+2
questions=colnames(data_2024)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data_2024[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2024)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
  
  g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)  # add numbers over bars
  
  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  
 figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
```

#### 6. If you answered YES to question 5, please select which additional topics you would like to see covered to improve your knowledge of advanced clinical endo. Select ALL that apply.


```{r, echo=F, message=F, warning=F}
response=data_2024 %>% select(`6. If you answered YES to question 5, please select which additional topics you would like to see covered to improve your knowledge of advanced clinical endo. Select ALL that apply.`) %>% dplyr::count(`6. If you answered YES to question 5, please select which additional topics you would like to see covered to improve your knowledge of advanced clinical endo. Select ALL that apply.`)

response=response %>% mutate(prop=round(n/nrow(data_2024),2))
response  %>%
datatable(extensions = 'Buttons',
          caption = "Summary statistics of age in TT/HT",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




## 2025 


### section 1 




```{r, echo=F, message=F, warning=F}
questions_index=c(1,3,5)
questions=colnames(data_2025)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{ # i=1
  response=data_2025[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2025)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  figures[[i]]=
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
#g1
  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
  #ggtitle(paste(questions[i]))+
  #theme(plot.title = element_text(hjust = 0.5, size=10))  #center the title 
figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
} # for (i in 1:length(questions))
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]


annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]


annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
```



### section 2

```{r, echo=F, message=F, warning=F}
questions_index=seq(7,26,by=2)
questions=colnames(data_2025)[questions_index]
figures=list()
p_value_list=list()
for (i in 1:length(questions))
{
  response=data_2025[,c(questions_index[i], questions_index[i]+1)] 
  colnames(response)=c("response_cate", "coded_response") # rename col names 
  
  response_by_group=response %>% dplyr::count(response=coded_response) %>% mutate(prop=n/nrow(data_2025)) # group response 
 
  response_cate_number=sort(unique(response$coded_response)); response_cate=numeric() 
  for (j in 1:length(response_cate_number))
    response_cate[j]=unique(response$response_cate[response$coded_response==response_cate_number[j]])
  response_by_group=response_by_group %>% mutate(response_cate=response_cate)
  
  ############ calculate p values 
  p_value_matrix=matrix(nrow=nrow(response_by_group), ncol=nrow(response_by_group))
  row.names(p_value_matrix)=response_by_group$response_cate
  colnames(p_value_matrix)=response_by_group$response_cate
  for (j in 1:(nrow(p_value_matrix)-1))
    for (k in (j+1):nrow(p_value_matrix))
  {
    bino_test=binom.test(response_by_group[j,2] %>% pull, (response_by_group[k,2] %>% pull+response_by_group[j,2] %>% pull))
    p_value_matrix[j,k]=bino_test$p.value
  }
  p_value_list[[i]]=p_value_matrix 
  ############### draw the figure 
  
   
if (i<=8)
  {   g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("%")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
}
  if (i>8)
  {
    g1=ggplot(response_by_group, aes(x=response_cate, y=prop, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+ylim(c(0,1))+
    xlab("")+
  geom_text(aes(label=round(prop,4)*100), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars

  g2=ggplot(response_by_group, aes(x=response_cate, y=n, fill=response_cate)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=12))+
  ylab("")+
    xlab("")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)#+  # add numbers over bars
    
  }
  
  figures[[i]]=ggarrange(g1, g2,
                   # labels = c("A", "B", "C"),
                    ncol = 2, nrow = 1)
}
annotate_figure(figures[[1]], top = text_grob(paste(questions[1])))
p_value_list[[1]]
annotate_figure(figures[[2]], top = text_grob(paste(questions[2])))
p_value_list[[2]]
annotate_figure(figures[[3]], top = text_grob(paste(questions[3])))
p_value_list[[3]]
annotate_figure(figures[[4]], top = text_grob(paste(questions[4])))
p_value_list[[4]]
annotate_figure(figures[[5]], top = text_grob(paste(questions[5])))
p_value_list[[5]]
annotate_figure(figures[[6]], top = text_grob(paste(questions[6])))
p_value_list[[6]]
annotate_figure(figures[[7]], top = text_grob(paste(questions[7])))
p_value_list[[7]]
annotate_figure(figures[[8]], top = text_grob(paste(questions[8])))
p_value_list[[8]]
annotate_figure(figures[[9]], top = text_grob(paste(questions[9])))
p_value_list[[9]]
annotate_figure(figures[[10]], top = text_grob(paste(questions[10])))
p_value_list[[10]]
```



## statistical software 

```{r, echo=F}
R.version
```