---
title: "4/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr) # combine and arrange multiple 
library(rstatix) # use anova_test function 
library(nlme) # use gls function 
library(foreign) # use interaction.plot 
set.seed(123)
```


```{r, echo=F, warning=F, message=F}
col_name1=paste("Pre-Polymerization-No Background, Cling Wrap", c("L", "a", "b"), sep="-")
col_name2=paste(rep(c("30 Minutes Post-Polymerization-No Backgroud, Cling Wrap", "30 Minutes Post-Polymerization-No Background, No Cling Wrap"), each=3),c("L", "a", "b"),sep="-")
col_name3=paste(rep(c("7 Days Post-Polymerization-No Background, No Cling Wrap", "7 Days Post-Polymerization-White Background, No Cling Wrap", "7 Days Post-Polymerization-Black Background, No Cling Wrap"), each=3),c("L", "a", "b"),sep="-")
col_name4=paste("8 Days Post-Polymerization-No Background, No Cling Wrap", c("L", "a", "b"), sep="-")
col_name5=c("Color Change_With Polymerization_at 30 min_AA-BB_DE", "Color Change_of 30 min_Effect of wrap_BB-CC_DE", "Color Change_after further polym for_8 days (20C)_CC-GG_DE","Translucency_of each at_37C_EE-FF_DE", "Color Change_at 7-8 days due to_room temp to oral temp_DD-GG_DE")
col_names=c("Material",col_name1, col_name2, col_name3, col_name4, col_name5)

Research_Measurements=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202204\\Megan\\Research_Measurements.csv", header=F))
colnames(Research_Measurements)=col_names

```





## material comparisons-annova test 

```{r, echo=F, message=F, warning=F}
material=Research_Measurements%>%select(Material) %>% pull()
anova_pvalue=numeric()
for (i in 2:ncol(Research_Measurements))
{
  sub_data=data.frame(material=material, measure=Research_Measurements[,i] %>% pull())
  reg<- lm(measure ~ material, data=sub_data)
  anova_pvalue[i]=anova(reg)$"Pr(>F)"[1]
}

anova_result=data.frame(condition=col_names[-1], p_value=anova_pvalue[-1])
knitr::kable(anova_result, "pipe")
```



* each row is one condition, under which anova test is performed to test the equality among 5 materials 

* small p value (0) indicates that they are not all equal 


## DD vs GG 

```{r, echo=F, message=F, warning=F}
condition_index=c(11,12,13) # compare with  20, 21,22
material_group=unique(material)
t_test_pvalue=numeric(); ii=0
for (i in 1:length(condition_index))
  for (j in 1:length(material_group))
{
  ii=ii+1
  sub_data=Research_Measurements %>% filter(material==material_group[j])
  t_test=t.test(sub_data %>% select(col_names[condition_index[i]])%>% pull, sub_data %>% select(col_names[condition_index[i]+9])%>% pull, conf.level=0.95)
  t_test_pvalue[ii]=t_test$p.value
}

t_test_result=matrix(t_test_pvalue, nrow=5)
rownames(t_test_result)=material_group
#colnames(t_test_result)=paste(col_names[condition_index], col_names[condition_index+9], sep="vs")
colnames(t_test_result)=paste(c("DD-L", "DD-a", "DD-b"), c("GG-L", "GG-a", "GG-b"), sep=" vs ")

knitr::kable(t_test_result, "pipe", caption="p values by two sample t test")
```

* DD: 7 Days Post-Polymerization-No Background, No Cling Wrap; GG: 8 Days Post-Polymerization-No Background, No Cling Wrap

* for each material, different conditions, DD vs GG are compared with two sample t test. 


## response profile analysis 

### No Background, (No)Cling Wrap-L

```{r, echo=F, warning=F, message=F}
# transform wide format to long format 
occasion=c("0 (pre-poly)", "30 minutes", "7 days", "8 days") # corresponds to columns 2, 5 11, 20 
obs=seq(1, nrow(Research_Measurements)*length(occasion)) # all subjects in long format 
id=rep(seq(1, nrow(Research_Measurements)), each=length(occasion))

y=numeric(); col_index=c(2,8,11,20); ii=0 # for each subject, extract measurements at different time points/occasions 
for (i in 1:nrow(Research_Measurements))
 for (j in 1:length(col_index))
 {
   ii=ii+1
   y[ii]=Research_Measurements[i,col_index[j]] %>% pull
   
 }

group=rep(material, each=length(occasion))
time=rep(occasion, nrow(Research_Measurements))
  
Research_Measurements_L=data.frame(obs=obs, id=id, group=group, y=y, time=time)

interaction.plot(time, group, y, type="b", pch=c(1,2, 3,4), xlab="Time", ylab="L", main="No Background, (No)Cling Wrap-L", col=c("blue", "green", "orange", "red"))


#model <- gls(y ~ time*group, Research_Measurements_L,  corr=corSymm(,form= ~ 1 | id), weights = varIdent(form = ~ 1 | factor(time)))

#model <- gls(y ~ time*group, Research_Measurements_L,  weights = varIdent(form = ~ 1 | time))

model <- gls(y ~ time*group, Research_Measurements_L)

#summary(model)
anova(model)
 

```

* small p value for `time:group` suggests the change pattern after 0 (pre-poly) are different across material groups. 

* four conditions are `Pre-Polymerization-No Background, Cling Wrap-L`, 
`30 Minutes Post-Polymerization-No Background, No Cling Wrap-L`, `7 Days Post-Polymerization-No Background, No Cling Wrap-L`, `8 Days Post-Polymerization-No Background, No Cling Wrap-L`, so in addition to time difference, Cling wrap is also different as only `Cling wrap` happens at Pre-Polymerization. 



### No Background, (No)Cling Wrap-a

```{r, echo=F, warning=F, message=F}
# transform wide format to long format 
occasion=c("0 (pre-poly)", "30 minutes", "7 days", "8 days") # a corresponds to columns 3, 6 12, 21 
obs=seq(1, nrow(Research_Measurements)*length(occasion)) # all subjects in long format 
id=rep(seq(1, nrow(Research_Measurements)), each=length(occasion))

y=numeric(); col_index=c(3,9,12,21); ii=0 # for each subject, extract measurements at different time points/occasions 
for (i in 1:nrow(Research_Measurements))
 for (j in 1:length(col_index))
 {
   ii=ii+1
   y[ii]=Research_Measurements[i,col_index[j]] %>% pull
   
 }

group=rep(material, each=length(occasion))
time=rep(occasion, nrow(Research_Measurements))  
  
Research_Measurements_a=data.frame(obs=obs, id=id, group=group, y=y, time=time)

interaction.plot(time, group, y, type="b", pch=c(1,2, 3,4), xlab="Time", ylab="a", main="No Background, (No)Cling Wrap-a", col=c("blue", "green", "orange", "red"))

model <- gls(y ~ time*group, Research_Measurements_a)

#summary(model)
anova(model)
```
### No Background, (No)Cling Wrap-b


```{r, echo=F, warning=F, message=F}
# transform wide format to long format 
occasion=c("0 (pre-poly)", "30 minutes", "7 days", "8 days") # b corresponds to columns 4, 7 13, 22 
obs=seq(1, nrow(Research_Measurements)*length(occasion)) # all subjects in long format 
id=rep(seq(1, nrow(Research_Measurements)), each=length(occasion))

y=numeric(); col_index=c(4,10,13,22); ii=0 # for each subject, extract measurements at different time points/occasions 
for (i in 1:nrow(Research_Measurements))
 for (j in 1:length(col_index))
 {
   ii=ii+1
   y[ii]=Research_Measurements[i,col_index[j]] %>% pull
   
 }

group=rep(material, each=length(occasion))
time=rep(occasion, nrow(Research_Measurements))  
  
Research_Measurements_b=data.frame(obs=obs, id=id, group=group, y=y, time=time)

interaction.plot(time, group, y, type="b", pch=c(1,2, 3,4), xlab="Time", ylab="b", main="No Background, (No)Cling Wrap-b", col=c("blue", "green", "orange", "red"))

model <- gls(y ~ time*group, Research_Measurements_b)

#summary(model)
anova(model)

```



## statistical software 

```{r, echo=F}
R.version
```