---
title: "10/17/2022"
output: html_document
date: '2022-10-17'
---


```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
set.seed(123)
```


```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
```


## trueness

```{r, echo=F, message=F, warning=F}
trueness=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_trueness.csv", header=T))
methods2=c("FGAS_LS", "FGAS_IOS", "FGAS_CBCT", "FHAS_LS", "FHAS_IOS", "FHAS_CBCT")
trueness=trueness %>% mutate(methods=rep(methods2, each=20)) # add new column with unique sample ID's 
```

### anova test 

```{r, echo=F, message=F, warning=F}
f1=ggplot(trueness, aes(x=methods, y=Angle, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f2=ggplot(trueness, aes(x=methods, y=Base.3D.offset, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f3=ggplot(trueness, aes(x=methods, y=Base.distal, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f1, f2,f3, nrow=3)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)

f4=ggplot(trueness, aes(x=methods, y=Base.vestibular, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f5=ggplot(trueness, aes(x=methods, y=Base.3D.offset, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f6=ggplot(trueness, aes(x=methods, y=Base.apical, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f4, f5,f6, nrow=3)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)


f7=ggplot(trueness, aes(x=methods, y=Tip.3D.offset, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f8=ggplot(trueness, aes(x=methods, y=Tip.distal, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f9=ggplot(trueness, aes(x=methods, y=Tip.vestibular, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f10=ggplot(trueness, aes(x=methods, y=Tip.apical, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f7, f8,f9, f10, nrow=4)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)
```



```{r, echo=F, message=F, warning=F}
#anova(lm(Angle~ methods, data=trueness))
#anova(lm(Base.3D.offset~ methods, data=trueness))
#anova(lm(Base.distal~ methods, data=trueness))
#anova(lm(Base.vestibular~ methods, data=trueness))
#anova(lm(Base.apical~ methods, data=trueness))
#anova(lm(Tip.3D.offset~ methods, data=trueness))
#anova(lm(Tip.distal~ methods, data=trueness))
#anova(lm(Tip.vestibular~ methods, data=trueness))
#anova(lm(Tip.apical~ methods, data=trueness))

parameter=colnames(trueness)[3:11]
p_value=c("2.097e-09", "1.648e-06", "1.669e-08", "0.003051", "0.00843", "3.852e-07", "4.413e-08", "0.0004085", "0.003966")
data.frame(parameter=parameter, anova_p_value=p_value)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```





#### anova test for `FGAS`

```{r, echo=F, message=F, warning=F}
anova(lm(Angle~ methods, data=trueness[1:60,]))
```


#### anova test for `FHAS`

```{r, echo=F, message=F, warning=F}
anova(lm(Angle~ methods, data=trueness[61:120,]))
```


### Cronbach’s Alpha test 

```{r, echo=F, message=F, warning=F}
library(ltm)

FGAS_Angle=data.frame(FGAS_CBCT=trueness %>% filter(methods=="FGAS_CBCT") %>% dplyr::select(Angle) %>% pull, FGAS_IOS=trueness %>% filter(methods=="FGAS_IOS") %>% dplyr::select(Angle) %>% pull, FGAS_LS=trueness %>% filter(methods=="FGAS_LS") %>% dplyr::select(Angle) %>% pull) # dplyr::select  use select function from package dplyr 
#FGAS_Angle=data.frame(FGAS_CBCT=trueness$Angle[41:60], FGAS_IOS=trueness$Angle[21:40], FGAS_LS=trueness$Angle[1:20])
FGAS_alpha=cronbach.alpha(FGAS_Angle)
#round(FGAS_alpha$alpha,4)

FHAS_Angle=data.frame(FHAS_CBCT=trueness %>% filter(methods=="FHAS_CBCT") %>% dplyr::select(Angle) %>% pull, FHAS_IOS=trueness %>% filter(methods=="FHAS_IOS") %>% dplyr::select(Angle) %>% pull, FHAS_LS=trueness %>% filter(methods=="FHAS_LS") %>% dplyr::select(Angle) %>% pull) # dplyr::select  use select function from package dplyr
#FHAS_Angle=data.frame(FHAS_CBCT=trueness$Angle[101:120], FHAS_IOS=trueness$Angle[81:100], FHAS_LS=trueness$Angle[61:80])

FHAS_alpha=cronbach.alpha(FHAS_Angle)
#round(FHAS_alpha$alpha,4) 

########################
#library(psych)
#alpha(FGAS_Angle)
#alpha(FHAS_Angle)
```

* `FGAS` has alpha 0.70 and FHAS has 0.91. 


#### an example to show anova vs Cronbach’s Alpha 

```{r, echo=F, message=F, warning=F}
library(psych)
x=runif(20)
test_data=data.frame(X1=x, X2=x+1, X3=x+2)
#cronbach.alpha(test_data)
test_data_long=data.frame(group=rep(c("X1", "X2", "X3"), each=20),x=c(x, x+1, x+2))
#anova(lm(x~ group, data=test_data_long))

ggplot(test_data_long, aes(x=group, y=x, fill=group)) +
  geom_boxplot()

#ICC(test_data)
```

* in this example, x2=x1+1; x3=x1+2

* anova test suggests mean varies across 3 groups 

* Cronbach’s Alpha=1 indicates high reliability.  


### pairwise comparisons 

```{r, echo=F, message=F, warning=F}
##################
k=1
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################
k=2
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


##################
k=3
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

##################
k=4
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################
k=5
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

##################
k=6
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

##################
k=7
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################
k=8
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################
k=9
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
for (i in 1:length(methods2))
 for (j in 1:length(methods2))
{
 #  i=1; j=2
  ii=ii+1
  samplei=trueness %>% filter(methods==methods2[i])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  samplej=trueness %>% filter(methods==methods2[j])%>% dplyr::select(colnames(trueness)[2+k])%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }

result=data_frame(group1=rep(methods2, each=6), group2=rep(methods2,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
          caption = paste(colnames(trueness)[2+k]),
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

* non paired two sample t test is used 

* `mean_difference` is mean difference of `group1-group2`




## precision 



```{r, echo=F, message=F, warning=F, eval=T}
precision=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_precision.csv", header=T))
precision_data_all=list()

parameters=c("Angle", "Base.3D.offset", "Base.distal", "Base.vestibular", "Base.apical", "Tip.3D.offset", "Tip.distal", "Tip.vestibular", "Tip.apical")
for (i in 1:length(parameters))
{
precision_parameter=precision %>%  dplyr::select(ends_with(parameters[i])) %>% slice_tail(n = 191) # the last 191 rows as precision 
methods3=colnames(precision_parameter)
precision_parameter_long=data.frame(vs_distance=c(precision_parameter[,1] %>% pull, precision_parameter[,2] %>% pull, precision_parameter[,3] %>% pull, precision_parameter[,4] %>% pull, precision_parameter[,5] %>% pull, precision_parameter[,6] %>% pull), methods=rep(methods3, each=191))
precision_data_all[[i]]=precision_parameter_long
  
}

```



### anova test 

```{r, echo=F, message=F, warning=F, eval=T}

f1=ggplot(precision_data_all[[1]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f2=ggplot(precision_data_all[[2]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f3=ggplot(precision_data_all[[3]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f1, f2,f3, nrow=3)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)

###################
f4=ggplot(precision_data_all[[4]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f5=ggplot(precision_data_all[[5]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f6=ggplot(precision_data_all[[6]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f4, f5,f6, nrow=3)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)

###################
f7=ggplot(precision_data_all[[7]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f8=ggplot(precision_data_all[[8]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")
f9=ggplot(precision_data_all[[9]], aes(x=methods, y=vs_distance, fill=methods)) +
  geom_boxplot()+
  theme(legend.position = "none")

figure=ggarrange(f7, f8,f9, nrow=3)
annotate_figure(figure,
                top = text_grob("", color = "red", face = "bold", size = 14),
#                bottom = text_grob("Datasource: \n ToothGrowth data set", color = "blue",
#                                   hjust = 1, x = 1, face = "italic", size = 10),
#                left = text_grob("Tooth length", color = "green", rot = 90),
#                right = "I'm done, thanks :-)!",
#                fig.lab = "Figure 1", fig.lab.face = "bold"
)
```



```{r, echo=F, message=F, warning=F}
p_value=numeric()
for (i in 1:length(precision_data_all))
  p_value[i]=pvalue_adjust(anova(lm(vs_distance~ methods, data=precision_data_all[[i]]))$"Pr(>F)"[1]) #extract p values only 

parameters=c("Angle", "Base.3D.offset", "Base.distal", "Base.vestibular", "Base.apical", "Tip.3D.offset", "Tip.distal", "Tip.vestibular", "Tip.apical")
#p_value=c("7.445e-12", "< 2.2e-16", "1.669e-08", "0.003051", "0.00843", "3.852e-07", "4.413e-08", "0.0004085", "0.003966")
data.frame(parameter=parameters, anova_p_value=p_value)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))



```



### pairwise comparisons 

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[1]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[1]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[1]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* two sample t test is used 
* `mean_difference` is mean difference of `group1-group2`

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[2]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[2]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[2]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[3]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[3]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[3]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[4]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[4]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[4]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[5]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[5]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[5]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[6]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[6]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[6]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[7]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[7]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[7]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[8]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[8]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[8]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, echo=F, message=F, warning=F, eval=T}
p_value=numeric(); estimate=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
methods3=unique(precision_data_all[[9]]$methods)
for (i in 1:length(methods3))
 for (j in 1:length(methods3))
{
 #  i=1; j=2
  ii=ii+1
  samplei=precision_data_all[[9]] %>% filter(methods==methods3[i])%>% dplyr::select(vs_distance)%>% pull
  samplej=precision_data_all[[9]] %>% filter(methods==methods3[j])%>% dplyr::select(vs_distance)%>% pull
  test=t.test(samplei, samplej)  # non paired t test 
  estimate[ii]=test$estimate[1]-test$estimate[2]  # mean difference 
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
  
  
 }


result=data_frame(group1=rep(methods3, each=6), group2=rep(methods3,6), mean_difference=round(estimate,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 
result$group1[c(2:6, 8:12, 14:18, 20:24, 26:30, 32:36)]="---"

result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
