---
title: "4/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr) # combine and arrange multiple 
library(rstatix) # use anova_test function 
set.seed(123)
```


```{r, echo=F, warning=F, message=F}
col_name1=paste("Pre-Polymerization-No Background, Cling Wrap", c("L", "a", "b"), sep="-")
col_name2=paste(rep(c("30 Minutes Post-Polymerization-No Backgroud, Cling Wrap", "30 Minutes Post-Polymerization-No Background, No Cling Wrap"), each=3),c("L", "a", "b"),sep="-")
col_name3=paste(rep(c("7 Days Post-Polymerization-No Background, No Cling Wrap", "7 Days Post-Polymerization-White Background, No Cling Wrap", "7 Days Post-Polymerization-Black Background, No Cling Wrap"), each=3),c("L", "a", "b"),sep="-")
col_name4=paste("8 Days Post-Polymerization-No Background, No Cling Wrap", c("L", "a", "b"), sep="-")
col_name5=c("Color Change_With Polymerization_at 30 min_AA-BB_DE", "Color Change_of 30 min_Effect of wrap_BB-CC_DE", "Color Change_after further polym for_8 days (20C)_CC-GG_DE","Translucency_of each at_37C_EE-FF_DE", "Color Change_at 7-8 days due to_room temp to oral temp_DD-GG_DE")
col_names=c("Material",col_name1, col_name2, col_name3, col_name4, col_name5)

Research_Measurements=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202204\\Megan\\Research_Measurements.csv", header=F))
colnames(Research_Measurements)=col_names

```





## material comparisons-annova test 

```{r, echo=F, message=F, warning=F}
material=Research_Measurements%>%select(Material) %>% pull()
anova_pvalue=numeric()
for (i in 2:ncol(Research_Measurements))
{
  sub_data=data.frame(material=material, measure=Research_Measurements[,i] %>% pull())
  reg<- lm(measure ~ material, data=sub_data)
  anova_pvalue[i]=anova(reg)$"Pr(>F)"[1]
}

anova_result=data.frame(condition=col_names[-1], p_value=anova_pvalue[-1])
knitr::kable(anova_result, "pipe")
```



* each row is one condition, under which anova test is performed to test the equality among 5 materials 

* small p value (0) indicates that they are not all equal 


## DD vs GG 

```{r, echo=F, message=F, warning=F}
condition_index=c(11,12,13) # compare with  20, 21,22
material_group=unique(material)
t_test_pvalue=numeric(); ii=0
for (i in 1:length(condition_index))
  for (j in 1:length(material_group))
{
  ii=ii+1
  sub_data=Research_Measurements %>% filter(material==material_group[j])
  t_test=t.test(sub_data %>% select(col_names[condition_index[i]])%>% pull, sub_data %>% select(col_names[condition_index[i]+9])%>% pull, conf.level=0.95)
  t_test_pvalue[ii]=t_test$p.value
}

t_test_result=matrix(t_test_pvalue, nrow=5)
rownames(t_test_result)=material_group
#colnames(t_test_result)=paste(col_names[condition_index], col_names[condition_index+9], sep="vs")
colnames(t_test_result)=paste(c("DD-L", "DD-a", "DD-b"), c("GG-L", "GG-a", "GG-b"), sep=" vs ")

knitr::kable(t_test_result, "pipe", caption="p values by two sample t test")
```

* DD: 7 Days Post-Polymerization-No Background, No Cling Wrap; GG: 8 Days Post-Polymerization-No Background, No Cling Wrap

* for each material, different conditions, DD vs GG are compared with two sample t test. 





## statistical software 

```{r, echo=F}
R.version
```