---
title: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Since this is a balanced study design. R fucntion  [aov](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/aov) could be used to perform one way anova.  

```{r, echo=F}
set.seed(123)
```


```{r, echo=F}
data=read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202202\\Essa\\Translucency.csv", header=T)
translucency=data.frame(td=data$transclucency, materials=as.factor(data$materials))
groups=levels(translucency$materials)
```

### anova test 

Null hypothesis is $H_0:\mu_1=\mu_2=...=\mu_6$ and $H_a:Not~all~equal$

```{r, echo=F}
annova=aov(td~materials, data=translucency)
#annova
#summary(annova)

############## equivalently use linear regression 
LM <- lm(td ~ materials, data=translucency)
#anova(LM)

#summary(LM)
```

These are ANOVA results corresponding to Table 2

```{r, echo=F}
mean=numeric(); standard_deviation=numeric()
for (i in 1:length(groups))
{
  mean[i]=mean(translucency[translucency$materials==groups[i],]$td)
  standard_deviation[i]=sd(translucency[translucency$materials==groups[i],]$td)
}

anova=data.frame(Parameters=c("Translucency", groups), N=c("-", rep(20, length(groups))), mean=c("-", mean), standard_deviation=c("-", standard_deviation), F_value=c(237.7, rep(NA, length(groups))), p_value=c("<2e-16", rep("NA", length(groups))), R_square=c(0.9125, rep("NA", length(groups))))
knitr::kable(anova)
```
In this able p value is `<0.001` because it's $<10^{-16}$. 


### pairwise t test with Bonferroni Adjustment

These are p values in pairwise two sample tests, as in Table 3

```{r, echo=F}
pairwise_test=pairwise.t.test(translucency$td, translucency$materials, p.adjust.method = "bonf")
#knitr::kable(pairwise_test$p.value)

```


### two sample t test with confidence interval 

$H_0:\mu_I=\mu_J$  vs $Ha: \mu_I \neq \mu_J$. Below is the 95% confidence interval for mean difference $\mu_I-\mu_J$. $\mu_I$ is the sample mean in group $I$. 


These are other summary statistics in Table 3 

```{r, echo=F}
lower=numeric(); upper=numeric(); mean_difference=numeric(); pvalue=numeric() 
k=0
for (i in 1:(length(groups)-1))
  for (j in (i+1):length(groups))
   {
    k=k+1
    test=t.test(translucency[translucency$materials==groups[i],]$td, translucency[translucency$materials==groups[j],]$td, conf.level = 0.95)
    mean_difference[k]=mean(translucency[translucency$materials==groups[i],]$td)-mean(translucency[translucency$materials==groups[j],]$td)
    lower[k]=test$conf.int[1];upper[k]=test$conf.int[2] 
    pvalue[k]=test$p.value
    
  }
confidence_interval=data.frame(group1=groups[1:(length(groups)-1)], group2=groups[2:length(groups)], mean_difference=mean_difference, p_value=pvalue, Lower=lower, Upper=upper)
colnames(confidence_interval)=c("(I) Group", "(J) Group", "Mean Differences", "P", "95% CI Lower", "95% CI Upper")
knitr::kable(confidence_interval, "pipe")
```


## Regression (Mar2)



```{r, echo=F, eval=T}

data2=read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202202\\Essa\\CopyofEdge-chippingtest_Last.csv", header=T)
groups=colnames(data2)[seq(1, 12, b=2)]
adjust_rsquare_d=numeric(); adjust_rsquare_dsquare=numeric() 
confidence_interval_d=list(); confidence_interval_dsquare=list()
p_value_d=list(); p_value_dsquare=list()
rsquare_d=numeric(); rsquare_dsquare=numeric()
parameter_estimate_d=list(); parameter_estimate_dsquare=list()
for (i in 1:6)
{
  resp=(i-1)*2+1; pred=(i-1)*2+2
  material=data2[,c(resp, pred)] # extract response and predictor 
  material=cbind(material, material[,2]^2)
  material=material[complete.cases(material), ] # 
  reg_d=lm(material[,1]~0+material[,2]) # enforce intercept to 0 
  reg_dsquare=lm(material[,1]~0+material[,2]+material[,3]) # enforce intercept to 0
  
  parameter_estimate_d[[i]]=reg_d$coefficients
  parameter_estimate_dsquare[[i]]=reg_dsquare$coefficients
  
  adjust_rsquare_d[i]=summary(reg_d)$adj.r.squared  # extract adjusted R^2
  adjust_rsquare_dsquare[i]=summary(reg_dsquare)$adj.r.squared
  rsquare_d[i]=summary(reg_d)$r.squared
  rsquare_dsquare[i]=summary(reg_dsquare)$r.squared
  
  p_value_d[[i]]=summary(reg_d)$coefficients[,4]    # extract p value for coefficients 
  p_value_dsquare[[i]]=summary(reg_dsquare)$coefficients[,4]
  confidence_interval_d[[i]]=confint(reg_d)   # extract confidence interval 
  confidence_interval_dsquare[[i]]=confint(reg_dsquare)
}
Group=paste(rep(c("IPS.e.max.CAD.HT", "IPS.e.max.CAD.MT", "GC.Initial.HT.LiSi.blocks", "GC.Initial.LT.LiSi", "Vita.Suprinity.PC", "Celtra.Duo"), each=3), c("model1", "model2", "model2"), sep="_") 
predictor=rep(c("d", "d", "d^2"), 6)
adjust_rsquare=numeric(); rsquare=numeric()
parameter_estimate=numeric()
CI_lower=numeric(); CI_upper=numeric()
p_value=numeric()
for (i in 1:6)
{  
rsquare=c(rsquare, rsquare_d[i], rsquare_dsquare[i], "***")  
adjust_rsquare=c(adjust_rsquare, adjust_rsquare_d[i], adjust_rsquare_dsquare[i], "***")

parameter_estimate=c(parameter_estimate, parameter_estimate_d[[i]][1], parameter_estimate_dsquare[[i]][1], parameter_estimate_dsquare[[i]][2])

CI_lower=c(CI_lower, confidence_interval_d[[i]][1], confidence_interval_dsquare[[i]][1,1],confidence_interval_dsquare[[i]][2,1] )
CI_upper=c(CI_upper, confidence_interval_d[[i]][2], confidence_interval_dsquare[[i]][1,2],confidence_interval_dsquare[[i]][2,2] )
p_value=c(p_value, p_value_d[[i]][1], p_value_dsquare[[i]][1], p_value_dsquare[[i]][2])
}
summary=data.frame(Group=Group, predictor=predictor, rsquare=rsquare, adjust_rsquare=adjust_rsquare, parameter_estimate=parameter_estimate,  CI_lower=CI_lower, CI_upper=CI_upper, p_value=p_value)
knitr::kable(summary, "pipe")
```




Note $e-16=10^{-16}$. 














