---
title: "3/7/2022"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
set.seed(123)
```





## Problem 

Each individual has 5 measurements alignment, marginal ridge, buccolingual, occlusal relationship and overjet, measured manually and digitally and end up with one final score. (1) sample size needed to detect the difference between manual and digital measurements (2) if there is difference, which factor of 5 measurements drives the difference? All those observations are numeric numbers. 

## sample size calculation-paired two sample t test by  package `power.t.test`

[power.t.test](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/power.t.test.html)

* use `power.t.test` with option `alternative = "two.sided"`, `type="paired"`
* when mean difference is 0.1, standard deviation is 0.2, 33 subjects are required to achieve 80% power. 


```{r, echo=F}
library(ggplot2)
d=seq(0.1, 1, by=0.02); SD=0.2
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="paired") # paired two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  geom_hline(yintercept=0.8, linetype="dashed", color = "blue")+
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=0.2")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

```

## test the difference-two sample t test 

```{r, echo=F, message=F, warning=F}
data1=read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202203\\Lisa\\ABO Model Scores from digital CR-E through Ortho Share 360.csv")
data2=read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202203\\Lisa\\ABO Model Scores from Manual Measurement using ABO Gauge.csv")
colnames(data2)=colnames(data1)
data=rbind(data1, data2)
```

```{r, echo=F, message=F, warning=F}
two_sample_ttest=t.test(data1$Total, data2$Total, paired=T)
two_sample_ttest
```

* there is significant difference between digital `total` and manual 

* on average  digital `Total` is bigger than manual, digital total-manual total=5.27 


## individual pairwise test 

```{r, echo=F, warning=F, message=F}
variable=colnames(data1)[2:7]
p_value=numeric(); mean_diff=numeric()
for (i in 1:length(variable))
{
  two_sample_ttest=t.test(data1[,i+1], data2[,i+1], paired=T)
  p_value[i]=two_sample_ttest$p.value
  mean_diff[i]=two_sample_ttest$estimate
}
knitr::kable(data.frame(variable=variable,mean_difference=mean_diff, p_value=p_value))
```
* mean difference=digital-manual 
* `A` drives the difference most, followed by `MR`, `BLI`, `OR`, `O`.  

## intro rater reliability 

Use standard deviation to measure reliability. Standard deviations for both manual and digital is 0.58.  

```{r, echo=F, eval=F, message=F}
manual=c(30,29,30)
sd(manual)
digital=c(33,33,32)
sd(digital)
```


## statistical software 

```{r, echo=F}
R.version
```
