---
title: "9/28/2022"
output: html_document
date: '2022-09-28'
---


```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
set.seed(123)
```

## Saline 

### mean and standard deviation

```{r, echo=F, message=F, warning=F}
data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202209\\Vidya\\Vidya-saline stats.csv", header = T))
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
```

```{r, echo=F, message=F, warning=F}

brands=unique(data$File)
mean_OCP=numeric(); SD_Icorr=numeric()
mean_Icorr=numeric(); SD_OCP=numeric()
for (i in 1:length(brands))
{
  sub_data=data %>% filter(File==brands[i])
  mean_OCP[i]=sub_data%>%summarise(mean=mean(OCP..mV..1.hr))%>% pull()
  SD_OCP[i]=sub_data%>%summarise(SD=sd(OCP..mV..1.hr)) %>% pull()
  
  mean_Icorr[i]=sub_data%>%summarise(mean=mean(Icorr..nA.))%>% pull()
  SD_Icorr[i]=sub_data%>%summarise(SD=sd(Icorr..nA.))%>% pull()
}

data.frame(File=brands, mean_OCP=round(mean_OCP,4),  SD_OCP=round(SD_OCP,4), mean_Icorr=round(mean_Icorr,4),  SD_Icorr=round(SD_Icorr,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

#%>%
#  kbl() %>%
#  kable_styling()%>%
#scroll_box(height = "300px")
```


### pairwise comparisons 


#### OCP 


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data$File)
for (i in 1:length(brands))
 for (j in 1:length(brands))  
{
   ii=ii+1
  group1=data %>% filter(File==brands[i])%>% select(OCP..mV..1.hr) %>% pull
  group2=data %>% filter(File==brands[j])%>% select(OCP..mV..1.hr) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
 }

result=data_frame(group1=rep(brands,each=10), group2=rep(brands,10), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 

result$group1[c(2:10, 12:20, 22:30, 32:40, 42:50, 52:60, 62:70, 72:80, 82:90, 92:100)]="---"
result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



#### Icorr 


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data$File)
for (i in 1:length(brands))
 for (j in 1:length(brands))  
{
   ii=ii+1
  group1=data %>% filter(File==brands[i])%>% select(Icorr..nA.) %>% pull
  group2=data %>% filter(File==brands[j])%>% select(Icorr..nA.) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
 }

result=data_frame(group1=rep(brands,each=10), group2=rep(brands,10), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 

result$group1[c(2:10, 12:20, 22:30, 32:40, 42:50, 52:60, 62:70, 72:80, 82:90, 92:100)]="---"
result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

### anova 

#### OCP


```{r, echo=F, message=F, warning=F}
data1=data.frame(OCP=c(data$OCP..mV..1.hr), file=as.factor(data$File))
LM <- lm(OCP ~ file, data=data1)
anova(LM)
```

* small p value suggests OCP are not all equal across 10 brands 


#### Icorr


```{r, echo=F, message=F, warning=F}
data2=data.frame(OCP=c(data$Icorr..nA.), file=as.factor(data$File))
LM <- lm(OCP ~ file, data=data2)
anova(LM)
```


* p value, 0.6%<0.05  suggests Icorr are not all equal across 10 brands 

## NaOCI 



```{r, echo=F, message=F, warning=F}
data_NaOCI=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2022\\202209\\Vidya\\NaOCl for Stats.csv", header = T))

```

### Mean and standard deviation 

```{r, echo=F, message=F, warning=F}

brands=unique(data_NaOCI$File)
mean_OCP=numeric(); SD_Icorr=numeric()
mean_Icorr=numeric(); SD_OCP=numeric()
for (i in 1:length(brands))
{
  sub_data=data_NaOCI %>% filter(File==brands[i])
  mean_OCP[i]=sub_data%>%summarise(mean=mean(OCP..mV..1.hr))%>% pull()
  SD_OCP[i]=sub_data%>%summarise(SD=sd(OCP..mV..1.hr)) %>% pull()
  
  mean_Icorr[i]=sub_data%>%summarise(mean=mean(Icorr..nA.))%>% pull()
  SD_Icorr[i]=sub_data%>%summarise(SD=sd(Icorr..nA.))%>% pull()
}

data.frame(File=brands, mean_OCP=round(mean_OCP,4),  SD_OCP=round(SD_OCP,4), mean_Icorr=round(mean_Icorr,4),  SD_Icorr=round(SD_Icorr,4))%>%
datatable(extensions = 'Buttons',
          caption = "NaocI data",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### pairwise comparisons 


#### OCP 


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data_NaOCI$File)
for (i in 1:length(brands))
 for (j in 1:length(brands))  
{
   ii=ii+1
  group1=data_NaOCI %>% filter(File==brands[i])%>% select(OCP..mV..1.hr) %>% pull
  group2=data_NaOCI %>% filter(File==brands[j])%>% select(OCP..mV..1.hr) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
 }

result=data_frame(group1=rep(brands,each=10), group2=rep(brands,10), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 

result$group1[c(2:10, 12:20, 22:30, 32:40, 42:50, 52:60, 62:70, 72:80, 82:90, 92:100)]="---"
result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



#### Icorr 


```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data_NaOCI$File)
for (i in 1:length(brands))
 for (j in 1:length(brands))  
{
   ii=ii+1
  group1=data_NaOCI %>% filter(File==brands[i])%>% select(Icorr..nA.) %>% pull
  group2=data_NaOCI %>% filter(File==brands[j])%>% select(Icorr..nA.) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[ii]=test$estimate
  CI_lower[ii]=test$conf.int[1]
  CI_upper[ii]=test$conf.int[2]
  p_value[ii]=test$p.value
 }

result=data_frame(group1=rep(brands,each=10), group2=rep(brands,10), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 

result$group1[c(2:10, 12:20, 22:30, 32:40, 42:50, 52:60, 62:70, 72:80, 82:90, 92:100)]="---"
result%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### anova 

#### OCP


```{r, echo=F, message=F, warning=F}
data1=data.frame(OCP=c(data_NaOCI$OCP..mV..1.hr), file=as.factor(data_NaOCI$File))
LM <- lm(OCP ~ file, data=data1)
anova(LM)
```

* small p value suggests OCP are not all equal across 10 brands 


#### Icorr


```{r, echo=F, message=F, warning=F}
data2=data.frame(OCP=c(data_NaOCI$Icorr..nA.), file=as.factor(data_NaOCI$File))
LM <- lm(OCP ~ file, data=data2)
anova(LM)
```


* p value, `1.525e-15`<0.05  suggests Icorr are not all equal across 10 brands 


## saline vs naocI 

```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data_NaOCI$File)
for (i in 1:length(brands))
{
  group1=data%>% filter(File==brands[i])%>% select(OCP..mV..1.hr) %>% pull
  group2=data_NaOCI %>% filter(File==brands[i])%>% select(OCP..mV..1.hr) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
 }

result=data_frame(group1=paste(brands,"Saline", sep="_"), group2=paste(brands,"NaOCI", sep="_"), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 


result%>%
datatable(extensions = 'Buttons',
          caption="OCP",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



```{r, echo=F, message=F, warning=F}
p_value=numeric(); mean_difference=numeric(); CI_lower=numeric(); CI_upper=numeric()
ii=0
brands=unique(data_NaOCI$File)
for (i in 1:length(brands))
{
  group1=data%>% filter(File==brands[i])%>% select(Icorr..nA.) %>% pull
  group2=data_NaOCI %>% filter(File==brands[i])%>% select(Icorr..nA.) %>% pull
  
  test=t.test(group1-group2) 
  mean_difference[i]=test$estimate
  CI_lower[i]=test$conf.int[1]
  CI_upper[i]=test$conf.int[2]
  p_value[i]=test$p.value
 }

result=data_frame(group1=paste(brands,"Saline", sep="_"), group2=paste(brands,"NaOCI", sep="_"), mean_difference=round(mean_difference,2),  CI_lower=round(CI_lower,2),  CI_upper=round(CI_upper,2), p_value=pvalue_adjust(p_value)) 


result%>%
datatable(extensions = 'Buttons',
          caption="Icorr",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

