---
title: "3/8/2023"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
library(readxl)
library(multinma)
library(meta)
set.seed(123)
```



```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
  variables=colnames(data)
num_sample=numeric()
Mean=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)]
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
}

summary_data=data.frame(materials=variables, num_sample=num_sample, Mean=Mean, SD=SD, SE=SE, Range_low=range_min, Range_upper=range_max)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}


multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}


```

```{r, echo=F, message=F, warning=F, results=F}
#data1=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data Collection sheet - Final.csv", header=T))
#data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 1h.csv", header=T))
data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\DataforVAS_08052023.xlsx")
```


## one hour 

### sample data 

```{r, echo=F, message=F, warning=F}
data_1hour=data$`OneHour`[,c(1,3,8, 5,7)]
data_1hour_full=as_tibble(data_1hour[complete.cases(data_1hour), ]) 
colnames(data_1hour_full)=c("study", "treatment", "n", "mean", "sd")

data_1hour_full%>%
datatable(extensions = 'Buttons',
          caption = "one hour", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```





### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html


#data(Fleiss1993cont)

#m1 <- metacont(n.psyc, mean.psyc, sd.psyc, n.cont, mean.cont, sd.cont,
 # data = Fleiss1993cont, sm = "SMD")
#m1
#forest(m1)

######## manually create the data matrix 
study_data=matrix(nrow=11, ncol=6)
study_data[1,]=c(as.numeric(data_1hour_full[1,3:5]), as.numeric(data_1hour_full[2,3:5]))
study_data[2,]=c(as.numeric(data_1hour_full[3,3:5]), as.numeric(data_1hour_full[4,3:5]))
study_data[3,]=c(as.numeric(data_1hour_full[6,3:5]), as.numeric(data_1hour_full[5,3:5]))
study_data[4,]=c(as.numeric(data_1hour_full[7,3:5]), as.numeric(data_1hour_full[5,3:5]))
study_data[5,]=c(as.numeric(data_1hour_full[8,3:5]), as.numeric(data_1hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_1hour_full[10,3:5]), as.numeric(data_1hour_full[11,3:5]))
study_data[7,]=c(as.numeric(data_1hour_full[12,3:5]), as.numeric(data_1hour_full[14,3:5]))
study_data[8,]=c(as.numeric(data_1hour_full[13,3:5]), as.numeric(data_1hour_full[14,3:5]))
study_data[9,]=c(as.numeric(data_1hour_full[15,3:5]), as.numeric(data_1hour_full[17,3:5]))
study_data[10,]=c(as.numeric(data_1hour_full[16,3:5]), as.numeric(data_1hour_full[17,3:5]))
study_data[11,]=c(as.numeric(data_1hour_full[18,3:5]), as.numeric(data_1hour_full[19,3:5]))
study=c("Pearlman, B.", "Pereira, G.", "Pilatti, G.", "Pilatti, G.", "Santos, B.",  "Santos, B.", "Steffens, J 2011", "Steffens, J 2011", "Steffens, J 2011 @", "Steffens, J 2011 @", "Trombelli, L.")

data_meta=data.frame(study=study,samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )
colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=study

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")
m1
forest.meta(m1, layout="JAMA")


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "one hour", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


* For an individual study, a square with treatment estimate in the center and confidence interval as line extending either side of the square


* For meta-analysis results, a diamond with treatment estimate in the center and right and left side corresponding to lower and upper confidence limits

* heterogeneity (null hypothesis: all studies estimate the same effect) is measured by Cochran’s Q, which is calculated as the weighted sum of squared differences between individual study effects and the pooled effect across studies, following $\chi^2$ distribution with number of studies-1 DF. 

* $I^2$ statistic describes the percentage of variation across studies that is due to heterogeneity rather than chance
[more details](https://www.statsdirect.com/help/meta_analysis/heterogeneity.htm#:~:text=Heterogeneity%20in%20meta%2Danalysis%20refers,the%20inconsistency%20of%20studies'%20results). 

* [SMD interpretations](https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-14-30#:~:text=Firstly%2C%20the%20SMD%20can%20be,a%20large%20effect%20%5B2%5D.)

```{r, echo=T, message=F, warning=F}
n1=63; s1=21; n2=61; s2=25
# Calculate s_pooled
s_pooled <- sqrt(  # s_pooled is pooled standard deviation
  (((n1-1)*s1^2) + ((n2-1)*s2^2))/
    ((n1-1)+(n2-1))
)

# Calculate the standard error
se <- s_pooled*sqrt((1/n1)+(1/n2))
#se

mean1=10; mean2=19
(mean1-mean2)/s_pooled  # this is SMD 
```



### network meta-analysis 

```{r, echo=F, message=F, warning=F}
library(netmeta)
########### install package dmetar 
#if (!require("devtools")) {
#  install.packages("devtools")
#}
#devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)

data(TherapyFormats)

#head(TherapyFormats[1:5])

```



```{r, echo=F, eval=F}

### Analysis of arm-based data

```{r, echo=F, message=F, warning=F, eval=F}
data_arm=data %>% select(studyn, treatmentn, mean..y., standard.error..se., sample.size..n.) %>% drop_na()
data_arm$treatmentn[9]="placebo" # rename "placebo 1", "placebo 2" as placebo 
#data_arm$treatmentn[11]="placebo"
data_arm=data_arm[-11,] # remove "placebo 2" to avoid two occurances of placebos in study 9

data_arm%>%
datatable(extensions = 'Buttons',
          caption = "sub-data for arm-based analysis", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

arm_net <- set_agd_arm(data_arm, 
                      study = studyn,
                      trt = treatmentn,
                      y = mean..y., 
                      se = standard.error..se.,
                      sample_size = sample.size..n.) # use trt_ref to set reference treatment 
arm_net
plot(arm_net, weight_edges = TRUE, weight_nodes = TRUE)



* rename "placebo 1" as placebo 
* remove "placebo 2"
* each node is one treatment, 7 treatments (nodes) in total. 
* edge between two nodes indicates these two treatments are in one study, and edge width indicates how many studies involving these treatment,  e.g. 3 studies involve placebo and ibuprofen 
* node size indicates the sample size 






#### fixed effect meta-analysis


```{r, echo=F, message=F, warning=F, results=F, eval=F}
summary(normal(scale = 100))

arm_fit_FE <- nma(arm_net, 
                  trt_effects = "fixed",
                  prior_intercept = normal(scale = 100),
                  prior_trt = normal(scale = 10))
#> 
#> 
#> arm_fit_FE
#> A fixed effects NMA with a normal likelihood (identity link).
#> Inference for Stan model: normal.
#> 4 chains, each with iter=2000; warmup=1000; thin=1; 
#> post-warmup draws per chain=1000, total post-warmup draws=4000.
#> 
#>       mean se_mean   sd   2.5%   25%   50%   75% 97.5% n_eff Rhat
#> d[1]  0.53    0.01 0.46  -0.38  0.21  0.53  0.84  1.42  1624    1
#> d[2] -1.29    0.01 0.50  -2.27 -1.63 -1.29 -0.95 -0.30  1731    1
#> d[3]  0.03    0.01 0.32  -0.60 -0.18  0.04  0.24  0.66  2253    1
#> d[5] -0.30    0.00 0.21  -0.71 -0.44 -0.30 -0.17  0.10  2401    1
#> lp__ -6.63    0.06 2.35 -12.04 -7.99 -6.28 -4.92 -3.10  1719    1
#> 
#> Samples were drawn using NUTS(diag_e) at Mon Aug 29 22:15:09 2022.
#> For each parameter, n_eff is a crude measure of effective sample size,
#> and Rhat is the potential scale reduction factor on split chains (at 
#> convergence, Rhat=1).
#> 

print(arm_fit_FE, pars = c("d", "mu")) # mu: study specific intercept; d_k treatment effects 
plot_prior_posterior(arm_fit_FE)


* use $N(0,100^2)$ prior distributions for the treatment effects `d[k]`
 and study-specific intercepts `mu[j]`
* `placebo` is the reference treatment 
* `d[k]` treatment effects
* `mu[j]` study specific intercepts 



#### relative effects against placebo 

```{r, echo=F, message=F, warning=F, eval=F}
(arm_releff_FE <- relative_effects(arm_fit_FE, trt_ref = "placebo"))
plot(arm_releff_FE, ref_line = 0)


* each horizontal line of every treatment  visualizes 5 summary statistics 2.5%,25%, 50%, 75%, 97.5%. 

#### treatment ranking 

```{r, echo=F, message=F, warning=F, eval=F}
(arm_ranks <- posterior_ranks(arm_fit_FE))
plot(arm_ranks)

#(arm_rankprobs <- posterior_rank_probs(arm_fit_FE))
#plot(arm_rankprobs)


* rank the treatments by `d[k]`, the larger mean, the higher rank. ibuprofen > nimesilide > dexamethasone 8mg > ketorolac 10mg > celecoxib 200mg > 
placebo > dexamethasone 4mg 


```{r, echo=F, message=F, warning=F, eval=F}
 dat <- data.frame( 
   study = c("Jones et al. (1998)", "Lewis et al. (2004)",
 "Grant et al. (2006)", "Berry et al. (2013)",
 "Nolan et al. (2015)", "Clark et al. (2016)"),
 age1 = c( 20, 20, 20, 20, 20, 20),
 age2 = c( 40, 40, 40, 40, 40, 40),
 mean1 = c(13.4, 2.9, 55.8, 19.2, 6.6, 10.1),
 mean2 = c(15.1, 3.6, 61.2, 18.8, 8.5, 10.2),
 sd1 = c( 4.8, 1.2, 22.3, 2.9, 3.4, 3.8),
 n = c( 78, 22, 188, 35, 54, 112),
 r = c( .32, .29, .28, .41, .35, .19))

library(metafor)
 # calculate standardized mean changes (with raw score standardization)
 dat <- escalc(measure="SMCR", m1i=mean2, m2i=mean1, # "SMCR" for the standardized mean change using raw score standardization
 sd1i=sd1, ni=n, ri=r, data=dat, slab=study)

 # fit random-effects model and examine results
 res <- rma(yi, vi, data=dat)
 res 
 
 
  # create a forest and funnel plot side-by-side
 # note: the plots below have been customized a bit
 par(mfrow=c(1,2))
 forest(res)
 funnel(res)


## Reference 

* [BUGSnet](https://bugsnetsoftware.github.io/) 

*  [MetaStan](https://cran.r-project.org/web/packages/MetaStan/MetaStan.pdf)

* [Network meta-analysis: application and practice using R software](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6635665/pdf/epih-41-e2019013.pdf)

* [bayesmeta](https://cran.r-project.org/web/packages/bayesmeta/vignettes/Roever2020-bayesmeta.pdf)

* [multinma](https://dmphillippo.github.io/multinma/articles/vignette_overview.html)

* [metafor](https://www.wvbauer.com/lib/exe/fetch.php/talks:2019_viechtbauer_lsp_ma_longitudinal.pdf); longitudinal meta analysis


```




## Sample size determination 


 * [Olsen paper](https://pubmed.ncbi.nlm.nih.gov/28215182/) 


```{r, echo=T, message=F, warning=F}

mean_difference=seq(1,20); # use the median difference as mean difference  
SD=18/1.35 # use SD=IQR/1.35 
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```
* sample size with varying mean difference, given 80\% power. 


* [Santos paper](https://pubmed.ncbi.nlm.nih.gov/34031888/)

```{r, echo=T, message=F, warning=F}

mean_difference=seq(0.1,4, by=0.5); #  mean difference  
SD=max(1.48,1.21) # use SD maximum  
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
 * sample size with varying mean difference, given 80\% power.
 
 