---
title: "3/8/2023"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
library(readxl)
#install.packages("remotes")
#remotes::install_github("dmphillippo/multinma")
library(multinma)
library(meta)
library(netmeta)
########### install package dmetar 
#if (!require("devtools")) {
#  install.packages("devtools")
#}
#devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
set.seed(123)
```



```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
  variables=colnames(data)
num_sample=numeric()
Mean=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)]
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
}

summary_data=data.frame(materials=variables, num_sample=num_sample, Mean=Mean, SD=SD, SE=SE, Range_low=range_min, Range_upper=range_max)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}


multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}


```

```{r, echo=F, message=F, warning=F, results=F}
#data1=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data Collection sheet - Final.csv", header=T))
#data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 1h.csv", header=T))
#data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\DataforVAS_08052023.xlsx")
data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 09182023_han.xlsx")
```


## 1 hour 


[1 hour](2023_0301_Christos_1hour.html)



## 3 hour

[3 hour](2023_0301_Christos_3hour.html)



## 6 hour 

[6 hour](2023_0301_Christos_6hour.html)



## 8 hours


[8 hour](2023_0301_Christos_8hour.html)



## 24 hours 


[24 hours](2023_0301_Christos_24hour.html)


## 72 hours  

 * [72 hours](2023_0301_Christos_3days.html) 






## Sample size determination 


 * [Olsen paper](https://pubmed.ncbi.nlm.nih.gov/28215182/) 


```{r, echo=T, message=F, warning=F}

mean_difference=seq(1,20); # use the median difference as mean difference  
SD=18/1.35 # use SD=IQR/1.35 
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```
* sample size with varying mean difference, given 80\% power. 


* [Santos paper](https://pubmed.ncbi.nlm.nih.gov/34031888/)

```{r, echo=T, message=F, warning=F}

mean_difference=seq(0.1,4, by=0.5); #  mean difference  
SD=max(1.48,1.21) # use SD maximum  
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
 * sample size with varying mean difference, given 80\% power.
 
 
## statistical analysis 

Statistical software R (version 4.3.2) was used for all analysis. R package meta was employed to perform meta analysis, including fixed and random effect models, and drawing forest plot. 
 