---
title: "6/5/2023"
output: html_document
date: "2023-06-05"
---

```{r setup, include=FALSE}
rm(list=ls())
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(grid)
library(DT)
library(gridExtra)
library(matrixStats)
library(cowplot)
set.seed(123)
```




```{r, echo=F, warning=F, message=F}
######## adjust p values 
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
variables=colnames(data)
num_sample=numeric()
Mean=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
normality_pvalue=numeric()
for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)] # remove missing values 
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
  normality_pvalue[i]=round(shapiro.test(observation)$p.value,4)
}

summary_data=data.frame(materials=variables, num_sample=num_sample, Mean=Mean, SD=SD, SE=SE, Range_low=range_min, Range_upper=range_max, normality_pvalue=normality_pvalue)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}

```


```{r, echo=F, message=F, warning=F}
data_old=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Arndt\\Health literacy and Periodontal Health_data_for analysis.csv", header=T))
data_PRSA=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Arndt\\Health literacy and Periodontal Health_data_for analysis_PRSA.csv", header=T))
data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Arndt\\Health literacy and Periodontal Health_data_for analysis_2023_0717.csv", header=T)[1:97,])
#data%>%
#datatable(extensions = 'Buttons',
#          caption = "Sample data", 
#            options = list(dom = 'Blfrtip',
#                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
#                           lengthMenu = list(c(10,25,50,-1),
#                                             c(10,25,50,"All"))))
```

## Basic statistics 

```{r, echo=F, message=F, warning=F}
ggplot(data %>% dplyr::count(Four.Groups)%>% mutate(status=c("Periodontal Health", "Gingivitis", "Early/Moderate Periodontitis", "Severe Periodontitis")), aes(x=as.factor(Four.Groups), y=n, fill=status)) +geom_bar(stat="identity")+
  theme(legend.position="bottom")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab("n")+
  xlab("Four.Groups")+
  geom_text(aes(label=n), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
```

```{r, echo=F,message=F, warning=F}
############## age 
variable="Age"
data$Age=as.numeric(data$Age) # convert into numeric values first 
sub_data=data.frame(mean=round(c(mean(data$Age[data$Disease_Y_N=="Y"], na.rm=T), mean(data$Age[data$Disease_Y_N=="N"], na.rm=T))), sd=round(c(sd(data$Age[data$Disease_Y_N=="Y"], na.rm=T), sd(data$Age[data$Disease_Y_N=="N"], na.rm=T))), Disease=c("Y", "N"))
f1=ggplot(sub_data, aes(x=Disease, y=round(mean), fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=round(mean)), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
sub_data %>%
datatable(extensions = 'Buttons',
          caption = variable, 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
#f1
########### decayed teeth 
variable="Decayed"
data$Decayed=as.numeric(data$Decayed)
sub_data=data.frame(mean=round(c(mean(data$Decayed[data$Disease_Y_N=="Y"], na.rm=T), mean(data$Decayed[data$Disease_Y_N=="N"], na.rm=T)),1), sd=round(c(sd(data$Decayed[data$Disease_Y_N=="Y"], na.rm=T), sd(data$Decayed[data$Disease_Y_N=="N"], na.rm=T)),1), Disease=c("Y", "N"))
f2=ggplot(sub_data, aes(x=Disease, y=mean, fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
sub_data %>%
datatable(extensions = 'Buttons',
          caption = variable, 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
#f2


########### missing teeth 
variable="Missing"
data$Missing=as.numeric(data$Missing)
sub_data=data.frame(mean=round(c(mean(data$Missing[data$Disease_Y_N=="Y"], na.rm=T), mean(data$Missing[data$Disease_Y_N=="N"], na.rm=T)),1), sd=round(c(sd(data$Missing[data$Disease_Y_N=="Y"], na.rm=T), sd(data$Missing[data$Disease_Y_N=="N"], na.rm=T)),1), Disease=c("Y", "N"))
f3=ggplot(sub_data, aes(x=Disease, y=mean, fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
sub_data %>%
datatable(extensions = 'Buttons',
          caption = variable, 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
#f3

########### filled teeth 
variable="Filled"
data$Filled=as.numeric(data$Filled)
sub_data=data.frame(mean=round(c(mean(data$Filled[data$Disease_Y_N=="Y"], na.rm=T), mean(data$Filled[data$Disease_Y_N=="N"], na.rm=T)),1), sd=round(c(sd(data$Filled[data$Disease_Y_N=="Y"], na.rm=T), sd(data$Filled[data$Disease_Y_N=="N"], na.rm=T)),1), Disease=c("Y", "N"))
f4=ggplot(sub_data, aes(x=Disease, y=mean, fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="none")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
sub_data %>%
datatable(extensions = 'Buttons',
          caption = variable, 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
#f4

########### DMFT
variable="DMFT"
data$DMFT=as.numeric(data$DMFT)
sub_data=data.frame(mean=round(c(mean(data$DMFT[data$Disease_Y_N=="Y"], na.rm=T), mean(data$DMFT[data$Disease_Y_N=="N"], na.rm=T)),1), sd=round(c(sd(data$DMFT[data$Disease_Y_N=="Y"], na.rm=T), sd(data$DMFT[data$Disease_Y_N=="N"], na.rm=T)),1), Disease=c("Y", "N"))
f5=ggplot(sub_data, aes(x=Disease, y=mean, fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
sub_data %>%
datatable(extensions = 'Buttons',
          caption = variable, 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
#f5


grid.arrange(f1, f2, f3,  f4, f5, nrow=3)
```


## Health literacy 

```{r, echo=F, message=F, warning=F}
variable="REAL30D"
sub_data=data.frame(prop=c(sum(data$REAL30D>=21)/nrow(data), sum(data$REAL30D<21)/nrow(data)), class=c("adequate", "inadequate"))
ggplot(sub_data, aes(x=class, y=prop, fill=class)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("")+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
  #               position=position_dodge(.9))+
  geom_text(aes(label=round(prop*100,2)), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
geom_signif(annotations ="p=0.002", y_position =0.8  ,xmin=1, xmax=2, size=1, vjust=-0.5, textsize=3, color="red")
#binom.test(sub_data$prop[1]*nrow(data),nrow(data))
```


```{r, echo=F, message=F, warning=F}
variable="SAHL"
data$SAHL=as.numeric(data$SAHL)
sub_data=data.frame(prop=c(sum(data$SAHL>=14)/nrow(data), sum(data$SAHL<14)/nrow(data)), class=c("adequate", "inadequate"))
ggplot(sub_data, aes(x=class, y=prop, fill=class)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("")+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
  #               position=position_dodge(.9))+
  geom_text(aes(label=round(prop*100,2)), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
geom_signif(annotations ="p<0.001", y_position =1.1  ,xmin=1, xmax=2, size=1, vjust=-0.5, textsize=3, color="red")
#binom.test(sub_data$prop[1]*nrow(data),nrow(data))
```


### REAL30D vs SAHL 


```{r, echo=F, message=F, warning=F}
n11=data %>% filter(REAL30D>=21 & SAHL>=14) %>% nrow()
n12=data %>% filter(REAL30D<21 & SAHL>=14) %>% nrow()
n21=data %>% filter(REAL30D>=21 & SAHL<14) %>% nrow()
n22=data %>% filter(REAL30D<21 & SAHL<14) %>% nrow()
data.frame(variable=c("REAL30D_Adequate_SAHL_Adequate", "REAL30D_Inadequate_SAHL_Adequate", "REAL30D_Adequate_SAHL_Inadequate", "REAL30D_Inadequate_SAHL_Inadequate"), n=c(n11, n12, n21, n22)) %>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
fisher.test(matrix(c(n11, n21, n12, n22), nrow=2))
```





## OHIP 

```{r, echo=F, message=F, warning=F}
variable="OHIP"
data$OHIP=as.numeric(data$OHIP)
sub_data=data.frame(mean=round(c(mean(data$OHIP[data$Disease_Y_N=="Y"], na.rm=T), mean(data$OHIP[data$Disease_Y_N=="N"], na.rm=T)),1), sd=round(c(sd(data$OHIP[data$Disease_Y_N=="Y"], na.rm=T), sd(data$OHIP[data$Disease_Y_N=="N"], na.rm=T)),1), Disease=c("Y", "N"))
ggplot(sub_data, aes(x=Disease, y=mean, fill=Disease)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Disease")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
  geom_signif(annotations ="p<0.001", y_position =110  ,xmin=1, xmax=2, size=1, vjust=-0.5, textsize=3, color="red")

#t.test(data$OHIP[data$Disease_Y_N=="Y"], data$OHIP[data$Disease_Y_N=="N"])
```

* two sample t test was used 


```{r, echo=F, message=F, warning=F}
sub_data=data.frame(fourGroups=data$Four.Groups, OHIP=data$OHIP)
reg=lm(OHIP~as.character(fourGroups), data=sub_data)
anova(reg)
```
* one way anova of OHIP among four groups "Periodontal Health", "Gingivitis", "Early/Moderate Periodontitis", "Severe Periodontitis". 



```{r, echo=F, message=F, warning=F}
sub_data=data.frame(mean=round(c(mean(data$OHIP[data$Four.Groups=="0.00"], na.rm=T), mean(data$OHIP[data$Four.Groups=="1.00"], na.rm=T),mean(data$OHIP[data$Four.Groups=="2.00"], na.rm=T), mean(data$OHIP[data$Four.Groups=="3.00"], na.rm=T)), 1), sd=round(c(sd(data$OHIP[data$Four.Groups=="0.00"], na.rm=T), sd(data$OHIP[data$Four.Groups=="1.00"], na.rm=T), sd(data$OHIP[data$Four.Groups=="2.00"], na.rm=T),sd(data$OHIP[data$Four.Groups=="3.00"], na.rm=T)), 1), Four.Groups=c("Periodontal Health", "Gingivitis", "Early/Moderate Periodontitis", "Severe Periodontitis"))
                    
ggplot(sub_data, aes(x=Four.Groups, y=mean, fill=Four.Groups)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

```


## PRSA 



```{r, echo=F, message=F, warning=F}
variable="PRSA"
data$PRSA=as.numeric(data$PRSA)
sub_data=data.frame(mean=round(c(mean(data$PRSA[data$Age>40], na.rm=T), mean(data$PRSA[data$Age<=40], na.rm=T)),1), sd=round(c(sd(data$PRSA[data$Age>40], na.rm=T), sd(data$PRSA[data$Age<=40], na.rm=T)),1), Age=c(">40", "<=40"))
ggplot(sub_data, aes(x=Age, y=mean, fill=Age)) +geom_bar(stat="identity")+
  theme(legend.position="right")+
   theme(legend.title=element_blank())+ # remove legend title 
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  ylab(variable)+
  xlab("Age")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
                 position=position_dodge(.9))+
  geom_text(aes(label=mean), position=position_dodge(width=0.6), vjust=-0.25)+  # add numbers over bars
  ggtitle("")+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
  geom_signif(annotations ="p=0.0725", y_position =25  ,xmin=1, xmax=2, size=1, vjust=-0.5, textsize=3, color="black")

#t.test(data$PRSA[data$Age>40], data$PRSA[data$Age<=40])
```


## Relative risk 


### Age 

```{r, echo=T, message=F, warning=F}
library(epitools)
sub_data=data%>% select(Age, Disease_Y_N) 

total1=nrow(sub_data%>% filter(Age>40)); total2= nrow(sub_data%>% filter(Age<=40))
disease1=nrow(sub_data%>% filter(Age>40, Disease_Y_N=="Y")); disease2=nrow(sub_data%>% filter(Age<=40, Disease_Y_N=="Y"))

RR=(disease1/total1)/(disease2/total2)
#RR
RR_computing=riskratio.wald(matrix(c(disease1, total1, disease2, total2), nrow=2))
RR_computing$p.value
RR_computing$measure
###################
OR=disease1*(total2-disease2)/((total1-disease1)*disease2)
#OR
OR_data=matrix(c(disease1,total1-disease1,disease2, total2-disease2), nrow=2)
OR_computing=oddsratio(OR_data)
OR_computing$p.value
OR_computing$measure

```
* Relative risk is 1.15, 95% CI is (0.76, 1.74) with p value 0.53 for fisher.exact test 

* odds ratio is 3.84 , 95% CI is (1.18, 13.95) with p value of 0.03 for fisher.exact test 



### teet loose 

```{r, echo=T, message=F, warning=F}
sub_data=data%>% select(PRSA_4, Disease_Y_N) 

total1=nrow(sub_data%>% filter(PRSA_4==2)); total2= nrow(sub_data%>% filter(PRSA_4==1))
disease1=nrow(sub_data%>% filter(PRSA_4==2, Disease_Y_N=="Y")); disease2=nrow(sub_data%>% filter(PRSA_4==1, Disease_Y_N=="Y"))

RR=(disease1/total1)/(disease2/total2)
#RR
RR_computing=riskratio.wald(matrix(c(disease1, total1, disease2, total2), nrow=2))
RR_computing$p.value
RR_computing$measure
###################
OR=disease1*(total2-disease2)/((total1-disease1)*disease2)
#OR
OR_data=matrix(c(disease1,total1-disease1,disease2, total2-disease2), nrow=2)
OR_computing=oddsratio(OR_data)
OR_computing$p.value
OR_computing$measure

```

### smoking 

```{r, echo=T, message=F, warning=F}
sub_data=data%>% select(PRSA_6, Disease_Y_N) 

total1=nrow(sub_data%>% filter(PRSA_6==2)); total2= nrow(sub_data%>% filter(PRSA_6==1))
disease1=nrow(sub_data%>% filter(PRSA_6==2, Disease_Y_N=="Y")); disease2=nrow(sub_data%>% filter(PRSA_6==1, Disease_Y_N=="Y"))

RR=(disease1/total1)/(disease2/total2)
#RR
RR_computing=riskratio.wald(matrix(c(disease1, total1, disease2, total2), nrow=2))
RR_computing$p.value
RR_computing$measure
###################
OR=disease1*(total2-disease2)/((total1-disease1)*disease2)
#OR
OR_data=matrix(c(disease1,total1-disease1,disease2, total2-disease2), nrow=2)
OR_computing=oddsratio(OR_data)
OR_computing$p.value
OR_computing$measure
```


### gum receeded 

```{r, echo=T, message=F, warning=F}
sub_data=data%>% select(PRSA_5, Disease_Y_N) 

total1=nrow(sub_data%>% filter(PRSA_5==2)); total2= nrow(sub_data%>% filter(PRSA_5==1))
disease1=nrow(sub_data%>% filter(PRSA_5==2, Disease_Y_N=="Y")); disease2=nrow(sub_data%>% filter(PRSA_5==1, Disease_Y_N=="Y"))

RR=(disease1/total1)/(disease2/total2)
#RR
RR_computing=riskratio.wald(matrix(c(disease1, total1, disease2, total2), nrow=2))
RR_computing$p.value
RR_computing$measure
###################
OR=disease1*(total2-disease2)/((total1-disease1)*disease2)
#OR
OR_data=matrix(c(disease1,total1-disease1,disease2, total2-disease2), nrow=2)
OR_computing=oddsratio(OR_data)
OR_computing$p.value
OR_computing$measure
```


### gum bleeding  

```{r, echo=T, message=F, warning=F}
sub_data=data%>% select(PRSA_3, Disease_Y_N) 

total1=nrow(sub_data%>% filter(PRSA_3==2)); total2= nrow(sub_data%>% filter(PRSA_3==1))
disease1=nrow(sub_data%>% filter(PRSA_3==2, Disease_Y_N=="Y")); disease2=nrow(sub_data%>% filter(PRSA_3==1, Disease_Y_N=="Y"))

RR=(disease1/total1)/(disease2/total2)
#RR
RR_computing=riskratio.wald(matrix(c(disease1, total1, disease2, total2), nrow=2))
RR_computing$p.value
RR_computing$measure
###################
OR=disease1*(total2-disease2)/((total1-disease1)*disease2)
#OR
OR_data=matrix(c(disease1,total1-disease1,disease2, total2-disease2), nrow=2)
OR_computing=oddsratio(OR_data)
OR_computing$p.value
OR_computing$measure
```



## statistical software 

```{r, echo=F}
R.version
```


