---
title: "07/26/2023"
output: html_document
date: "2023-07-26"
---


```{r setup, include=FALSE}
rm(list=ls())
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(grid)
library(DT)
library(gridExtra)
library(matrixStats)
library(cowplot)
library(readxl)
set.seed(123)
```




```{r, echo=F, warning=F, message=F}
######## adjust p values 
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
variables=colnames(data)
num_sample=numeric()
Mean=numeric()
Median=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
normality_pvalue=numeric()
per_25_quantile=numeric()
per_75_quantile=numeric()

for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)] # remove missing values 
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  Median[i]=round(median(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  per_25_quantile[i]=round(quantile(observation, prob=0.25),4)
  per_75_quantile[i]=round(quantile(observation, prob=0.75),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
  normality_pvalue[i]=round(shapiro.test(observation)$p.value,4)
}

summary_data=data.frame(variable=variables, num_sample=num_sample, Mean=Mean, Median=Median, SD=SD, SE=SE,per_25_quantile, per_75_quantile, Range_low=range_min, Range_upper=range_max, normality_pvalue=normality_pvalue)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}


multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}

```




## Kappa 

```{r, echo=F, message=F, warning=F, results=F}
data_sheet=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202308\\Zaid\\AI - Kappa - tooth .xlsx")
```

```{r, echo=F, message=F, warning=F}
library(irr)

kappa_value_all=numeric()
for (j in 1:length(data_sheet))
{
data=t(data_sheet[[j]])
kappa_value=numeric()
kappa_pvalue=numeric()
for (i in 1:5)
{
  kappa_test=kappa2(data.frame(rate1=as.numeric(data[2:nrow(data),1]), rate2=as.numeric(data[2:nrow(data),(i+1)])))
  kappa_value[i]=round(kappa_test$value,4)
  kappa_pvalue[i]=pvalue_adjust(kappa_test$p.value)
}
kappa_value_all[j]=mean(kappa_value)
}

data.frame(kappa_value_all)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

mean(kappa_value_all)
```

* We randomly choose 20 patients, and rate all teeth in every single patient by one expert and 5 other independent raters using 1(restoration) or 0 (no restoration). Cohen's Kappa was calculated between the expert and 5 other raters across all teeth within one patient, and average them as kappa for that individual. Finally  the average kappa is calculated across all 20 patients, as 0.97 indicating [almost perfect agreement](https://www.andywills.info/rminr/irr.html#:~:text=To%20calculate%20Cohen's%20kappa%20in,kappa2%20from%20the%20irr%20package.&text=The%20key%20result%20here%20is%20Kappa%20which%20is%20your%20Cohen's,higher%20or%20lower%20than%20this), with p value less than 0.1%.   


## sample size calculation 


### two sample t test 


```{r, echo=F, message=F, warning=F}
library(ggplot2)
d=seq(0.1, 2, by=0.1); SD=1.5
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="two.sample") # two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  #geom_vline(xintercept=0.13, colour="blue") +
  #geom_text(aes(x=0.13, label="d=0.13", y=10), colour="blue", angle=90, vjust = 1.2, text=element_text(size=11))+
  #geom_hline(yintercept=21, colour="blue") +
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=1.5")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

data.frame(mean_difference=d, sample_size)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


* use `power.t.test` with option `alternative = "two.sided"`, `type="two.sample"`

* sample size is the number of individuals required in each group.   





```{r, echo=F, message=F, warning=F}
library(ggplot2)
d=seq(0.1, 2, by=0.1); SD=1
sample_size=numeric()
for (i in 1:length(d))
{
  test=power.t.test(power = .80, delta = d[i], alternative = "two.sided", sig.level=0.05, sd=SD, type="two.sample") # two sample t test 
  sample_size[i]=round(test$n)
}
ggplot(data=data.frame(d, sample_size), aes(x=d, y=sample_size, group=1)) +
  geom_line(color="red")+
  #geom_vline(xintercept=0.13, colour="blue") +
  #geom_text(aes(x=0.13, label="d=0.13", y=10), colour="blue", angle=90, vjust = 1.2, text=element_text(size=11))+
  #geom_hline(yintercept=21, colour="blue") +
  geom_point()+
  xlab("d:mean difference")+
  ylab("n:sample size")+
  ggtitle("power=0.8; SD=1")+
  theme(plot.title = element_text(hjust = 0.5, size=15))

data.frame(mean_difference=d, sample_size)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

* use `power.t.test` with option `alternative = "two.sided"`, `type="two.sample"`

* sample size is the number of individuals required in each group.   


### anova test 

```{r, echo=F, message=F, warning=F}
between_var=seq(1,5); within_var=seq(2,5)
sample_size=numeric(); k=1
for (i in 1:length(between_var))
  for (j in 1:length(within_var))
  {
    test_result=power.anova.test(groups = 5, between.var = between_var[i], within.var = within_var[j],
                 power = .90)
    sample_size[k]=round(test_result$n)
    k=k+1
  }  


data.frame(between_var=rep(between_var, each=length(within_var)), within_var=rep(within_var, length(between_var)), sample_size=sample_size)%>%
datatable(extensions = 'Buttons',
          caption = "90% power", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* assume 5 groups 

* `between_var`, `within_var` are between and within group variance. 

* sample size is the number of individuals required in each group. 
