---
title: "8 hours"
output: html_document
date: "2024-05-30"
---



## Home 


[Home](2023_0301_Christos.html)





```{r, echo=F, message=F, warning=F}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
library(meta)
library(netmeta)
library(dmetar)
```


```{r, echo=F, message=F, warning=F, results=F}

data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 09182023_han.xlsx")
```




## 8 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_8hour=data$`8 Hours`[,c(1,3,8, 5,7)]
data_8hour_full=as_tibble(data_8hour[complete.cases(data_8hour), ]) 
colnames(data_8hour_full)=c("study", "treatment", "n", "mean", "sd")


data_8hour_full%>%
datatable(extensions = 'Buttons',
          caption = "8 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



### forest plot 

#### 8 hours - ALL studies per author – no groups






```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=7, ncol=6)
study_data[1,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[1,3:5]))

study_data[2,]=c(as.numeric(data_8hour_full[7,3:5]), as.numeric(data_8hour_full[8,3:5]))

study_data[3,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[11,3:5]))
study_data[4,]=c(as.numeric(data_8hour_full[10,3:5]), as.numeric(data_8hour_full[11,3:5]))

study_data[5,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[12,3:5]))
study_data[6,]=c(as.numeric(data_8hour_full[14,3:5]), as.numeric(data_8hour_full[12,3:5]))

study_data[7,]=c(as.numeric(data_8hour_full[15,3:5]), as.numeric(data_8hour_full[16,3:5]))

#study_data[8,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[2,3:5]))
#study_data[9,]=c(as.numeric(data_8hour_full[6,3:5]), as.numeric(data_8hour_full[7,3:5]))
#study_data[10,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[10,3:5]))
#study_data[11,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[14,3:5]))




comparison=c( "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo")
             
       #      "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
      #      "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
      #      "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
      #      "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)
```

* random effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:7,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:7],
                 data = data_meta[1:7,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```



* fixed effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:7,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:7],
                 data = data_meta[1:7,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.19

`> -0.54*(7)^0.5*(-0.28+0.79)/3.92
[1]  -0.1858775`



```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen$zval.common, 4), pval=round(m.gen$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



#### 8 hours - Studies per medication


##### celecoxib 200mg


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



##### dexamethasone 8mg

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



##### etoricoxib 120mg

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,6)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,6)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


##### ketorolac 10mg


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(7)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


#### 8 hours - Studies only with dexamethazone

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


#### 8 hours - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=7
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=7
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.08

`> -0.54*(7)^0.5*(-0.43+0.64)/3.92
[1]  -0.07653781`


```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen_leave_one_out$zval.common, 4), pval=round(m.gen_leave_one_out$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### network meta-analysis 


#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 

study_data=matrix(nrow=9, ncol=6)
study_data[1,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[1,3:5]))

study_data[2,]=c(as.numeric(data_8hour_full[7,3:5]), as.numeric(data_8hour_full[8,3:5]))

study_data[3,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[11,3:5]))
study_data[4,]=c(as.numeric(data_8hour_full[10,3:5]), as.numeric(data_8hour_full[11,3:5]))

study_data[5,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[12,3:5]))
study_data[6,]=c(as.numeric(data_8hour_full[14,3:5]), as.numeric(data_8hour_full[12,3:5]))

study_data[7,]=c(as.numeric(data_8hour_full[15,3:5]), as.numeric(data_8hour_full[16,3:5]))

study_data[8,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[10,3:5]))
study_data[9,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[14,3:5]))




comparison=c( "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.3,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, srt.labels = 35
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```