---
title: "24 hours"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2024-05-30"
---

## Home 


[Home](2023_0301_Christos.html)





```{r, echo=F, message=F, warning=F}
rm(list=ls())
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
library(meta)
library(netmeta)
library(dmetar)
```


```{r, echo=F, message=F, warning=F, results=F}

data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 09182023_han.xlsx")
```


## 24 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_24hour=data$`24 Hours`[,c(1,3,8, 5,7)]
data_24hour_full=as_tibble(data_24hour[complete.cases(data_24hour), ]) 
colnames(data_24hour_full)=c("study", "treatment", "n", "mean", "sd")

data_24hour_full$study[16]="Steffens, J 2010"
data_24hour_full$study[17]="Steffens, J 2010"

data_24hour_full=data_24hour_full[-16,] 

data_24hour_full%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### forest plot 


#### 1 day - ALL studies per author – no groups





```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=6, ncol=6)
study_data[1,]=c(as.numeric(data_24hour_full[1,3:5]), as.numeric(data_24hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[9,3:5]))
study_data[3,]=c(as.numeric(data_24hour_full[10,3:5]), as.numeric(data_24hour_full[11,3:5]))

study_data[4,]=c(as.numeric(data_24hour_full[13,3:5]), as.numeric(data_24hour_full[14,3:5]))

study_data[5,]=c(as.numeric(data_24hour_full[17,3:5]), as.numeric(data_24hour_full[15,3:5]))

study_data[6,]=c(as.numeric(data_24hour_full[18,3:5]), as.numeric(data_24hour_full[19,3:5]))







comparison=c( "Pereira, G._ibuprofen 600mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_placebo",
             "Santos, B._nimesulide 100mg_vs_placebo", 
             
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 20mg_vs_placebo"
             
            )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

```


* random effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="RevMan5", sortvar = TE, 
            prediction = T, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 
```


* raw difference -0.39

`> -0.41*(6)^0.5*(0.34+1.17)/3.92
[1]  -0.3868569`



```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen$zval.random, 4), pval=round(m.gen$pval.random,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



* fixed effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 


```





#### parallel RCTs


```{r,  message=F, warning=F}
variable_include_index=c(1,4,6)

m22 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen22 <- metagen(TE = m22$TE,
                 seTE =m22$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = T,
                 random = F,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen22, layout="RevMan5", sortvar = TE, 
            prediction = F, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```





#### 1 day - Studies per surgery


MA 1 – periodontal surgery



* random effect model 

```{r, echo=F, message=F, warning=F}
##################### forest plot without Pereira
variable_include_index=c(2,3,4,5,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="RevMan5", sortvar = TE, 
            prediction = T, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```

* raw difference -0.24

`> -0.25*(5)^0.5*(0.59+1.09)/3.92
[1]  -0.2395787`


```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen$zval.random, 4), pval=round(m.gen$pval.random,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



* fixed effect model 

```{r, echo=F, message=F, warning=F}
##################### forest plot without Pereira
variable_include_index=c(2,3,4,5,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 
```


#### 1 day - Studies per medication


##### ibuprofen 600mg


* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


##### nimesulide 100mg


* fixed effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(3)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```

##### etoricoxib 120mg


* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(4,5)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(4,5)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


##### dexamethasone 8mg 


##### ketorolac 20mg

* random effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(6)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```



#### 1 day - Studies only with ibuproben



* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```

##### 1 day - Studies only with dexamethazone



#### 1 day - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=6
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=6
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.13

`> -0.45*(6)^0.5*(-0.22+0.69)/3.92
[1]  -0.13216`

```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen_leave_one_out$zval.common, 4), pval=round(m.gen_leave_one_out$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



```{r, echo=F, message=F, warning=F}

##################
data_meta%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### network meta-analysis 

#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 

study_data=matrix(nrow=7, ncol=6)
study_data[1,]=c(as.numeric(data_24hour_full[1,3:5]), as.numeric(data_24hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_24hour_full[6,3:5]), as.numeric(data_24hour_full[7,3:5]))

#study_data[3,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[9,3:5]))  # remove this one according to Chris's updated names in the email titled "Preemptive analgesia", "Sanchez-Perez, A._dexketoprofen trometamol (DKT) 25mg_vs_placebo",
study_data[3,]=c(as.numeric(data_24hour_full[10,3:5]), as.numeric(data_24hour_full[11,3:5]))

study_data[4,]=c(as.numeric(data_24hour_full[13,3:5]), as.numeric(data_24hour_full[14,3:5]))

study_data[5,]=c(as.numeric(data_24hour_full[16,3:5]), as.numeric(data_24hour_full[15,3:5]))

study_data[6,]=c(as.numeric(data_24hour_full[17,3:5]), as.numeric(data_24hour_full[18,3:5]))


study_data[7,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[10,3:5]))





comparison=c( "Pereira, G._ibuprofen 600mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_placebo",
             "Santos, B._nimesulide 100mg_vs_placebo", 
             
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 20mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_nimesulide 100mg")


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.6,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

#24 hours 
#Ibuprofen 600mg – 47
#Nimesulide 100mg – 20 
#Etoricoxib 120mg – 31
#Ketorolac 20mg – 22
#Placebo – 68 





sample_size=c(31,  47, 22, 20, 68)

max_num=163  # maximum number across all time points 

node_size <- sqrt(sample_size /max_num)*10



long.labels=m.netmeta$trts

#netgraph(m.netmeta, 
#         labels = long.labels, number.of.studies = TRUE, 
#         )


netgraph(m.netmeta, 
         labels = long.labels, 
         number.of.studies = F, 
         plastic = FALSE,  # Ensures standard network layout
         lty = rep(1, length(m.netmeta$trts)),  # Set all links to solid lines
         lwd = 2,  # Increase line width for clarity
         col = "black",  # Set edge color to black
         col.points = "red",
         cex.point=  node_size, 
         col.number = "cyan"  # Change the color of numbers on edges
)



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```



#### transitivity analysis (consistency between direct vs indir)


```{r, message=F, warning=F}
netsplit(m.netmeta)
```


```{r, message=F, warning=F}
netsplit(m.netmeta) %>% forest(fontsize = 8, spacing = .4)  # visualize the net split results 
```

```{r, message=F, warning=F}
funnel(m.netmeta, order=unique(m.netmeta$treat1), pch=seq(1:5), col=seq(1:5), linreg = T,  legend = F, digits.pval=2)
funnel(m.netmeta, order=unique(m.netmeta$treat1), pch=seq(1:5), col=seq(1:5), linreg = F,  legend = F, digits.pval=2)
```




#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.6,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```
