---
title: "09/25 2023"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---




```{r, echo=F, message=F, warning=F}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}

```




```{r, echo=F, message=F, warning=F, results=F}
data2=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202309\\Teerarat\\Peri-Implant DATA CLEAN 111023_without_header.xlsx")
```




## continuous variables 

### CORR


```{r, message=F, warning=F}
group_corr=data2$`Data CORR`

num_indi=23
Data=group_corr
Age=as.numeric(Data$Age[1:num_indi])
CBL_diagnosis_months=as.numeric(Data$CBL_diagnosis_months)[1:num_indi]
I_Torque=as.numeric(Data$I_Torque)[1:num_indi]
I_Diameter=as.numeric(Data$I_Diameter)[1:num_indi]
I_Length=as.numeric(Data$I_Length)[1:num_indi]
Time_comp_days=as.numeric(Data$Time_comp_days)[1:num_indi]
Bone_loss_mm=as.numeric(Data$Bone_loss_mm)[1:num_indi]
Bone_loss_percentage=as.numeric(Data$`Bone_loss_%`)[1:num_indi]
Bone_loss_crest=as.numeric(Data$Bone_loss_crest)[1:num_indi]
Bone_loss_post_regen_mm=as.numeric(Data$Bone_loss_post_regen_mm)[1:num_indi]
Bone_loss_post_regen_percentage=as.numeric(Data$`Bone_loss_post_regen_%`)[1:num_indi]
Month_post_regen=as.numeric(Data$Month_post_regen)[1:num_indi]
RTR_post_regen_IP=as.numeric(Data$RTR_post_regen_IP)[1:num_indi]
RTR_post_regen_CRP=as.numeric(Data$RTR_post_regen_CRP)[1:num_indi]
Time_comp_post_regen=as.numeric(Data$Time_comp_post_regen)[1:num_indi]
Post_cr_del_months=as.numeric(Data$Post_cr_del_months)[1:num_indi]
Latest_bone_levels_mm=as.numeric(Data$Latest_bone_levels_mm)[1:num_indi]
Latest_bone_levels_percentage=as.numeric(Data$`Latest_bone_levels_%`)[1:num_indi]

data_interest_corr=data.frame(Age, CBL_diagnosis_months, I_Torque, I_Diameter, I_Length, Time_comp_days, Bone_loss_mm, Bone_loss_percentage, Bone_loss_crest, Bone_loss_post_regen_mm, Bone_loss_post_regen_percentage, Month_post_regen, RTR_post_regen_IP,RTR_post_regen_CRP, Time_comp_post_regen, Post_cr_del_months, Latest_bone_levels_mm, Latest_bone_levels_percentage )

#data_interest_corr=data_interest_corr[-1,]  # remove the first subject, requested by Vrisiis 

data_summary=summary_statistics(data_interest_corr)
data_summary %>%
datatable(extensions = 'Buttons',
          caption = "CORR",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


* `num_sample` numeric samples after removing NA's  

*  Shapiro-Wilk’s test, `shapiro.test` in software R  was used to test the normality assumption. 






### restore 

```{r, echo=F, message=F, warning=F}
group_restore=data2$`Data RESTORE`

num_indi=55
Data=group_restore
Age=as.numeric(Data$Age[1:num_indi])
CBL_diagnosis_months=as.numeric(Data$CBL_diagnosis_months)[1:num_indi]
I_Torque=as.numeric(Data$I_Torque)[1:num_indi]
I_Diameter=as.numeric(Data$I_Diameter)[1:num_indi]
I_Length=as.numeric(Data$I_Length)[1:num_indi]
Time_comp_days=as.numeric(Data$Time_comp_days)[1:num_indi]
Bone_loss_mm=as.numeric(Data$Bone_loss_mm)[1:num_indi]
Bone_loss_percentage=as.numeric(Data$`Bone_loss_%`)[1:num_indi]
Bone_loss_crest=as.numeric(Data$Bone_loss_crest)[1:num_indi]
Bone_loss_post_regen_mm=as.numeric(Data$Bone_loss_post_regen_mm)[1:num_indi]
Bone_loss_post_regen_percentage=as.numeric(Data$`Bone_loss_post_regen_%`)[1:num_indi]
Month_post_regen=as.numeric(Data$Month_post_regen)[1:num_indi]
RTR_post_regen_IP=as.numeric(Data$RTR_post_regen_IP)[1:num_indi]
RTR_post_regen_CRP=as.numeric(Data$RTR_post_regen_CRP)[1:num_indi]
Time_comp_post_regen=as.numeric(Data$Time_comp_post_regen)[1:num_indi]
Post_cr_del_months=as.numeric(Data$Post_cr_del_months)[1:num_indi]
Latest_bone_levels_mm=as.numeric(Data$`Latest_bone_levels_mm...46`)[1:num_indi]
Latest_bone_levels_percentage=as.numeric(Data$`Latest_bone_levels_%...47`)[1:num_indi]

data_interest_store=data.frame(Age, CBL_diagnosis_months, I_Torque, I_Diameter, I_Length, Time_comp_days, Bone_loss_mm, Bone_loss_percentage, Bone_loss_crest, Bone_loss_post_regen_mm, Bone_loss_post_regen_percentage, Month_post_regen, RTR_post_regen_IP,RTR_post_regen_CRP, Time_comp_post_regen, Post_cr_del_months, Latest_bone_levels_mm, Latest_bone_levels_percentage )

data_summary=summary_statistics(data_interest_store)
data_summary %>%
datatable(extensions = 'Buttons',
          caption = "restore",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


### corr vs store 


```{r, message=F, warning=F}
pvalue=numeric(); wilcox_pvalue=numeric()
variable_index=c(1:9,16)
for (i in 1:length(variable_index))
{
  pvalue[i]=t.test(data_interest_corr[,variable_index[i]], data_interest_store[,variable_index[i]], na.rm=T)$p.value
  wilcox_pvalue[i]=wilcox.test(data_interest_corr[,variable_index[i]], data_interest_store[,variable_index[i]], na.rm=T)$p.value
  }
data.frame(variable=colnames(data_interest_corr)[variable_index], pvalue=pvalue_adjust(pvalue), wilcox_pvalue=pvalue_adjust(wilcox_pvalue))%>%
datatable(extensions = 'Buttons',
          caption = "corr vs restore",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* two sample t test (parametric test) was used 

* `wilcox_pvalue` is the p value of non-parametric test, Wilcoxon test






### combining corr and store

```{r, echo=F, message=F, warning=F}
data_interest_combined=rbind(data_interest_corr, data_interest_store)

data_summary=summary_statistics(data_interest_combined)
data_summary %>%
datatable(extensions = 'Buttons',
          caption = "restore",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



## categorical variables 

### CORR 


* [group corr](2023_0901_Teerarat_part1.html)


### RESTORE 


* [group restore](2023_0901_Teerarat_part2.html)



###  corr vs restore 

* [corr vs restore](2023_0901_Teerarat_part3.html)


### combining corr and restore 

* [corr and restore](2023_0901_Teerarat_part4.html)



