---
title: "3/8/2023"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
library(readxl)
#install.packages("remotes")
#remotes::install_github("dmphillippo/multinma")
library(multinma)
library(meta)
library(netmeta)
########### install package dmetar 
#if (!require("devtools")) {
#  install.packages("devtools")
#}
#devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
set.seed(123)
```



```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
  variables=colnames(data)
num_sample=numeric()
Mean=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)]
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
}

summary_data=data.frame(materials=variables, num_sample=num_sample, Mean=Mean, SD=SD, SE=SE, Range_low=range_min, Range_upper=range_max)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}


multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}


```

```{r, echo=F, message=F, warning=F, results=F}
#data1=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data Collection sheet - Final.csv", header=T))
#data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 1h.csv", header=T))
#data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\DataforVAS_08052023.xlsx")
data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 09182023_han.xlsx")
```


## 1 hour 


[1 hour](2023_0301_Christos_1hour.html)



## 3 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_3hour=data$`3 Hour`[,c(1,3,8, 5,7)]
data_3hour_full=as_tibble(data_3hour[complete.cases(data_3hour), ]) 
colnames(data_3hour_full)=c("study", "treatment", "n", "mean", "sd")
data_3hour_full=data_3hour_full[-c(1,2,3),]
#data_3hour_full$study[11]="Steffens, J 2010"
#data_3hour_full$study[12]="Steffens, J 2010"

data_3hour_full%>%
datatable(extensions = 'Buttons',
          caption = "three hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



### forest plot 


#### 3 hours - ALL studies per author – no groups



```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html


#data(Fleiss1993cont)

#m1 <- metacont(n.psyc, mean.psyc, sd.psyc, n.cont, mean.cont, sd.cont,
 # data = Fleiss1993cont, sm = "SMD")
#m1
#forest(m1)

######## manually create the data matrix 
study_data=matrix(nrow=9, ncol=6)
study_data[1,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[1,3:5]))
study_data[2,]=c(as.numeric(data_3hour_full[3,3:5]), as.numeric(data_3hour_full[1,3:5]))

study_data[3,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[6,3:5]))
study_data[4,]=c(as.numeric(data_3hour_full[5,3:5]), as.numeric(data_3hour_full[6,3:5]))

study_data[5,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_3hour_full[8,3:5]), as.numeric(data_3hour_full[9,3:5]))

study_data[7,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[10,3:5]))
study_data[8,]=c(as.numeric(data_3hour_full[12,3:5]), as.numeric(data_3hour_full[10,3:5]))

study_data[9,]=c(as.numeric(data_3hour_full[13,3:5]), as.numeric(data_3hour_full[14,3:5]))

#study_data[10,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[3,3:5]))
#study_data[11,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[5,3:5]))
#study_data[12,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[8,3:5]))
#study_data[13,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[12,3:5]))




comparison=c("Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",  
             
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo",
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo",
             
             "Trombelli, L._ketorolac 10mg_vs_placebo" 
             
         #   "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg", 
        #    "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
        #    "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
        #    "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" 
        )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:9,], sm = "SMD")
```


* random effect model 


```{r, echo=F, message=F, warning=F}
########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:9],
                 data = data_meta[1:9,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "3 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




* fixed effect model 


```{r, echo=F, message=F, warning=F}
########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:9],
                 data = data_meta[1:9,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


```

* raw difference -0.28

`> -0.81*(9)^0.5*(-0.58+1.03)/3.92
[1] -0.2789541`



#### 3 hours - Studies per medication


##### dexamethasone 4mg


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



##### celecoxib 200mg


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


##### dexamethasone 8mg 


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,7)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,7)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



##### etoricoxib 120mg 


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(6,8)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(6,8)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



##### ketorolac 10mg 


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(9)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```




#### 3	hours - Studies only with dexamethazone

* random effect model 


```{r, echo=F, message=F, warning=F}
#####################
variable_include_index=c(1, 3, 4,7)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F}
#####################
variable_include_index=c(1, 3, 4,7)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```




#### 3 hours - Sensitivity analysis

* random effect model 


```{r, echo=F, message=F, warning=F}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=9
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=9
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```
* raw difference -0.10

`> -0.81*(9)^0.5*(-0.73+0.89)/3.92
[1] -0.09918367`




### network meta-analysis 


#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 
study_data=matrix(nrow=13, ncol=6)
study_data[1,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[1,3:5]))
study_data[2,]=c(as.numeric(data_3hour_full[3,3:5]), as.numeric(data_3hour_full[1,3:5]))

study_data[3,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[6,3:5]))
study_data[4,]=c(as.numeric(data_3hour_full[5,3:5]), as.numeric(data_3hour_full[6,3:5]))

study_data[5,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_3hour_full[8,3:5]), as.numeric(data_3hour_full[9,3:5]))

study_data[7,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[10,3:5]))
study_data[8,]=c(as.numeric(data_3hour_full[12,3:5]), as.numeric(data_3hour_full[10,3:5]))

study_data[9,]=c(as.numeric(data_3hour_full[13,3:5]), as.numeric(data_3hour_full[14,3:5]))

study_data[10,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[3,3:5]))
study_data[11,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[5,3:5]))
study_data[12,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[8,3:5]))
study_data[13,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[12,3:5]))




comparison=c("Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",  
             
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo",
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo",
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
            "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg", 
            "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" 
        )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

#########################

treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")


data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.1,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, 
         )



```

* overall comparison structure 
* direct links mean there are direct comparison, otherwise indirect comparisons 
* degree of thickness represents how often we find a specific comparison
* numbers on the edge indicate how many studies involve that comparison





```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```

* higher P-score, the better it is 



#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


## 6 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_6hour=data$`6 Hours`[,c(1,3,8, 5,7)]
data_6hour_full=as_tibble(data_6hour[complete.cases(data_6hour), ]) 
colnames(data_6hour_full)=c("study", "treatment", "n", "mean", "sd")

data_6hour_full%>%
datatable(extensions = 'Buttons',
          caption = "6 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### forest plot 

#### 6 hours - ALL studies per author – no groups





```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=12, ncol=6)
study_data[1,]=c(as.numeric(data_6hour_full[1,3:5]), as.numeric(data_6hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[3,3:5]))
study_data[3,]=c(as.numeric(data_6hour_full[5,3:5]), as.numeric(data_6hour_full[3,3:5]))

study_data[4,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[7,3:5]))
study_data[5,]=c(as.numeric(data_6hour_full[8,3:5]), as.numeric(data_6hour_full[9,3:5]))

study_data[6,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[12,3:5]))
study_data[7,]=c(as.numeric(data_6hour_full[11,3:5]), as.numeric(data_6hour_full[12,3:5]))

study_data[8,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[15,3:5]))
study_data[9,]=c(as.numeric(data_6hour_full[14,3:5]), as.numeric(data_6hour_full[15,3:5]))

study_data[10,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[16,3:5]))
study_data[11,]=c(as.numeric(data_6hour_full[18,3:5]), as.numeric(data_6hour_full[16,3:5]))

study_data[12,]=c(as.numeric(data_6hour_full[19,3:5]), as.numeric(data_6hour_full[20,3:5]))

#study_data[13,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[5,3:5]))
#study_data[14,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[8,3:5]))
#study_data[15,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[11,3:5]))
#study_data[16,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[14,3:5]))
#study_data[17,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[18,3:5]))



comparison=c("Pereira, G._ibuprofen 600mg_vs_placebo",  
             
             "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Santos, B._ibuprofen 600mg_vs_placebo1",
             "Santos, B._nimesilide 100mg_vs_placebo2", 
             
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo",   
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo") 
             
         #    "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
        #     "Santos, B._ibuprofen 600mg_vs_nimesilide 100mg",
        #    "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
        #    "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
        #    "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:12,], sm = "SMD")

```


* random effect model 


```{r, echo=F, message=F, warning=F}

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:12],
                 data = data_meta[1:12,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```



* fixed effect model 


```{r, echo=F, message=F, warning=F}

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:12],
                 data = data_meta[1:12,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.22

`> -0.66*(12)^0.5*(-0.48+0.85)/3.92
[1]  -0.2157994`



#### 6 hours - Studies per surgery

MA 1 – periodontal surgery


* random effect model 


```{r, echo=F, message=F, warning=F}

##################### forest plot without Pereira
variable_include_index=2:12

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#########################
data_meta%>%
datatable(extensions = 'Buttons',
          caption = "6 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


* fixed effect model 


```{r, echo=F, message=F, warning=F}

##################### forest plot without Pereira
variable_include_index=2:12

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```
* raw difference -0.21

`> -0.61*(11)^0.5*(-0.41+0.81)/3.92
[1]  -0.206443`



#### 6 hours - Studies per medication


##### ibuprofen 600mg


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,4)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=9,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```

* fixed effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,4)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=9,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


##### dexamethasone 4mg


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=9,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



* fixed effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=9,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


##### celecoxib 200mg


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(3,8)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


* fixed effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(3,8)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


##### nimesulide 100mg


* random effect model  


```{r, echo=F, message=F, warning=F}
variable_include_index=c(5)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


##### dexamethasone 8mg

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(7,10)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(7,10)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



##### etoricoxib 120mg

* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(9,11)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


* fixed effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(9,11)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



##### ketorolac 10mg

* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(12)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


#### 6	hours - Studies only with ibuproben


* random effect model 

```{r, echo=F, message=F, warning=F}

variable_include_index=c(1,4)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


* fixed effect model 

```{r, echo=F, message=F, warning=F}

variable_include_index=c(1,4)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


#### 6	hours - Studies only with dexamethazone


* random effect model 


```{r, echo=F, message=F, warning=F}

variable_include_index=c(2,6,7,10)

m4 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen4 <- metagen(TE = m4$TE,
                 seTE =m4$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen4, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```

* fixed effect model 


```{r, echo=F, message=F, warning=F}

variable_include_index=c(2,6,7,10)

m4 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen4 <- metagen(TE = m4$TE,
                 seTE =m4$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen4, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```



#### 6 hours - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=12
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=12
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* raw difference -0.06

`> -0.66*(12)^0.5*(-0.61+0.72)/3.92
[1]  -0.206443`



### network meta-analysis 


#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 

study_data=matrix(nrow=17, ncol=6)
study_data[1,]=c(as.numeric(data_6hour_full[1,3:5]), as.numeric(data_6hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[3,3:5]))
study_data[3,]=c(as.numeric(data_6hour_full[5,3:5]), as.numeric(data_6hour_full[3,3:5]))

study_data[4,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[7,3:5]))
study_data[5,]=c(as.numeric(data_6hour_full[8,3:5]), as.numeric(data_6hour_full[9,3:5]))

study_data[6,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[12,3:5]))
study_data[7,]=c(as.numeric(data_6hour_full[11,3:5]), as.numeric(data_6hour_full[12,3:5]))

study_data[8,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[15,3:5]))
study_data[9,]=c(as.numeric(data_6hour_full[14,3:5]), as.numeric(data_6hour_full[15,3:5]))

study_data[10,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[16,3:5]))
study_data[11,]=c(as.numeric(data_6hour_full[18,3:5]), as.numeric(data_6hour_full[16,3:5]))

study_data[12,]=c(as.numeric(data_6hour_full[19,3:5]), as.numeric(data_6hour_full[20,3:5]))

study_data[13,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[5,3:5]))
study_data[14,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[8,3:5]))
study_data[15,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[11,3:5]))
study_data[16,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[14,3:5]))
study_data[17,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[18,3:5]))



comparison=c("Pereira, G._ibuprofen 600mg_vs_placebo",  
             
             "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Santos, B._ibuprofen 600mg_vs_placebo1",
             "Santos, B._nimesilide 100mg_vs_placebo2", 
             
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo",   
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo",
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
             "Santos, B._ibuprofen 600mg_vs_nimesilide 100mg",
            "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)


comparison[4]="Santos, B._ibuprofen 600mg_vs_placebo"  # unify placebo1 placebo2 into placebo 
comparison[5]="Santos, B._nimesilide 100mg_vs_placebo"
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, 
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


## 8 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_8hour=data$`8 Hours`[,c(1,3,8, 5,7)]
data_8hour_full=as_tibble(data_8hour[complete.cases(data_8hour), ]) 
colnames(data_8hour_full)=c("study", "treatment", "n", "mean", "sd")


data_8hour_full%>%
datatable(extensions = 'Buttons',
          caption = "8 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



### forest plot 

#### 8 hours - ALL studies per author – no groups






```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=7, ncol=6)
study_data[1,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[1,3:5]))

study_data[2,]=c(as.numeric(data_8hour_full[7,3:5]), as.numeric(data_8hour_full[8,3:5]))

study_data[3,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[11,3:5]))
study_data[4,]=c(as.numeric(data_8hour_full[10,3:5]), as.numeric(data_8hour_full[11,3:5]))

study_data[5,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[12,3:5]))
study_data[6,]=c(as.numeric(data_8hour_full[14,3:5]), as.numeric(data_8hour_full[12,3:5]))

study_data[7,]=c(as.numeric(data_8hour_full[15,3:5]), as.numeric(data_8hour_full[16,3:5]))

#study_data[8,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[2,3:5]))
#study_data[9,]=c(as.numeric(data_8hour_full[6,3:5]), as.numeric(data_8hour_full[7,3:5]))
#study_data[10,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[10,3:5]))
#study_data[11,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[14,3:5]))




comparison=c( "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo")
             
       #      "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
      #      "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
      #      "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
      #      "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)
```

* random effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:7,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:7],
                 data = data_meta[1:7,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```



* fixed effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:7,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:7],
                 data = data_meta[1:7,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.19

`> -0.54*(7)^0.5*(-0.28+0.79)/3.92
[1]  -0.1858775`


#### 8 hours - Studies per medication


##### celecoxib 200mg


* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(1,3)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



##### dexamethasone 8mg

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



##### etoricoxib 120mg

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,6)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(4,6)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


##### ketorolac 10mg


* random effect model 


```{r, echo=F, message=F, warning=F}
variable_include_index=c(7)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


#### 8 hours - Studies only with dexamethazone

* random effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 

```{r, echo=F, message=F, warning=F}
variable_include_index=c(2,5)
m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")
########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


#### 8 hours - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=7
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=7
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.08

`> -0.54*(7)^0.5*(-0.43+0.64)/3.92
[1]  -0.07653781`


### network meta-analysis 


#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 

study_data=matrix(nrow=9, ncol=6)
study_data[1,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[1,3:5]))

study_data[2,]=c(as.numeric(data_8hour_full[7,3:5]), as.numeric(data_8hour_full[8,3:5]))

study_data[3,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[11,3:5]))
study_data[4,]=c(as.numeric(data_8hour_full[10,3:5]), as.numeric(data_8hour_full[11,3:5]))

study_data[5,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[12,3:5]))
study_data[6,]=c(as.numeric(data_8hour_full[14,3:5]), as.numeric(data_8hour_full[12,3:5]))

study_data[7,]=c(as.numeric(data_8hour_full[15,3:5]), as.numeric(data_8hour_full[16,3:5]))

study_data[8,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[10,3:5]))
study_data[9,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[14,3:5]))




comparison=c( "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.3,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, srt.labels = 35
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```



## 24 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_24hour=data$`24 Hours`[,c(1,3,8, 5,7)]
data_24hour_full=as_tibble(data_24hour[complete.cases(data_24hour), ]) 
colnames(data_24hour_full)=c("study", "treatment", "n", "mean", "sd")

data_24hour_full$study[16]="Steffens, J 2010"
data_24hour_full$study[17]="Steffens, J 2010"

data_24hour_full=data_24hour_full[-16,] 

data_24hour_full%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### forest plot 


#### 1 day - ALL studies per author – no groups





```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=6, ncol=6)
study_data[1,]=c(as.numeric(data_24hour_full[1,3:5]), as.numeric(data_24hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[9,3:5]))
study_data[3,]=c(as.numeric(data_24hour_full[10,3:5]), as.numeric(data_24hour_full[11,3:5]))

study_data[4,]=c(as.numeric(data_24hour_full[13,3:5]), as.numeric(data_24hour_full[14,3:5]))

study_data[5,]=c(as.numeric(data_24hour_full[17,3:5]), as.numeric(data_24hour_full[15,3:5]))

study_data[6,]=c(as.numeric(data_24hour_full[18,3:5]), as.numeric(data_24hour_full[19,3:5]))







comparison=c( "Pereira, G._ibuprofen 600mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_placebo",
             "Santos, B._nimesilide 100mg_vs_placebo", 
             
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo"
             
            )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

```


* random effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 
```


* raw difference -0.39

`> -0.41*(6)^0.5*(0.34+1.17)/3.92
[1]  -0.3868569`



* fixed effect model 


```{r, echo=F, message=F, warning=F}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 
```



#### 1 day - Studies per surgery


MA 1 – periodontal surgery



* random effect model 

```{r, echo=F, message=F, warning=F}
##################### forest plot without Pereira
variable_include_index=c(2,3,4,5,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```

* raw difference -0.24

`> -0.25*(5)^0.5*(0.59+1.09)/3.92
[1]  -0.2395787`



* fixed effect model 

```{r, echo=F, message=F, warning=F}
##################### forest plot without Pereira
variable_include_index=c(2,3,4,5,6)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 
```


#### 1 day - Studies per medication


##### ibuprofen 600mg


* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


##### nimesulide 100mg


* fixed effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(3)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

##### etoricoxib 120mg


* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(4,5)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(4,5)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


##### dexamethasone 8mg 


##### ketorolac 10mg

* random effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(6)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



#### 1 day - Studies only with ibuproben



* random effect model 

```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* fixed effect model 


```{r, echo=F, message=F, warning=F}

##############
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

##### 1 day - Studies only with dexamethazone



#### 1 day - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=6
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* fixed effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=6
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.13

`> -0.45*(6)^0.5*(-0.22+0.69)/3.92
[1]  -0.13216`



```{r, echo=F, message=F, warning=F}

##################
data_meta%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### network meta-analysis 

#### random effect model 


```{r, echo=F, message=F, warning=F}

######## manually create the data matrix 

study_data=matrix(nrow=7, ncol=6)
study_data[1,]=c(as.numeric(data_24hour_full[1,3:5]), as.numeric(data_24hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_24hour_full[6,3:5]), as.numeric(data_24hour_full[7,3:5]))

#study_data[3,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[9,3:5]))  # remove this one according to Chris's updated names in the email titled "Preemptive analgesia", "Sanchez-Perez, A._dexketoprofen trometamol (DKT) 25mg_vs_placebo",
study_data[3,]=c(as.numeric(data_24hour_full[10,3:5]), as.numeric(data_24hour_full[11,3:5]))

study_data[4,]=c(as.numeric(data_24hour_full[13,3:5]), as.numeric(data_24hour_full[14,3:5]))

study_data[5,]=c(as.numeric(data_24hour_full[16,3:5]), as.numeric(data_24hour_full[15,3:5]))

study_data[6,]=c(as.numeric(data_24hour_full[17,3:5]), as.numeric(data_24hour_full[18,3:5]))


study_data[7,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[10,3:5]))





comparison=c( "Pereira, G._ibuprofen 600mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_placebo",
             "Santos, B._nimesilide 100mg_vs_placebo", 
             
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_nimesilide 100mg")


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.6,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE,  srt.labels = 35
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```



#### fixed effect model 

```{r, echo=F, message=F, warning=F}
data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.6,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```

## 72 hours  

 * [72 hours](2023_0301_Christos_3days.html) 






## Sample size determination 


 * [Olsen paper](https://pubmed.ncbi.nlm.nih.gov/28215182/) 


```{r, echo=T, message=F, warning=F}

mean_difference=seq(1,20); # use the median difference as mean difference  
SD=18/1.35 # use SD=IQR/1.35 
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```
* sample size with varying mean difference, given 80\% power. 


* [Santos paper](https://pubmed.ncbi.nlm.nih.gov/34031888/)

```{r, echo=T, message=F, warning=F}

mean_difference=seq(0.1,4, by=0.5); #  mean difference  
SD=max(1.48,1.21) # use SD maximum  
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
 * sample size with varying mean difference, given 80\% power.
 
 
## statistical analysis 

Statistical software R (version 4.3.2) was used for all analysis. R package meta was employed to perform meta analysis, including fixed and random effect models, and drawing forest plot. 
 