---
title: "3/8/2023"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(DT)
library(readxl)
library(multinma)
library(meta)
library(netmeta)
########### install package dmetar 
#if (!require("devtools")) {
#  install.packages("devtools")
#}
#devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
set.seed(123)
```



```{r, echo=F, warning=F, message=F}
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
  variables=colnames(data)
num_sample=numeric()
Mean=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)]
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
}

summary_data=data.frame(materials=variables, num_sample=num_sample, Mean=Mean, SD=SD, SE=SE, Range_low=range_min, Range_upper=range_max)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}


multiplesheets <- function(fname) {
   
  # getting info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
    
  # assigning names to data frames
  names(data_frame) <- sheets
    
  # print data frame
  print(data_frame)
}


```

```{r, echo=F, message=F, warning=F, results=F}
#data1=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data Collection sheet - Final.csv", header=T))
#data=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 1h.csv", header=T))
data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\DataforVAS_08052023.xlsx")
```


## one hour 

### sample data 

```{r, echo=F, message=F, warning=F}
data_1hour=data$`OneHour`[,c(1,3,8, 5,7)]
data_1hour_full=as_tibble(data_1hour[complete.cases(data_1hour), ]) 
colnames(data_1hour_full)=c("study", "treatment", "n", "mean", "sd")

data_1hour_full%>%
datatable(extensions = 'Buttons',
          caption = "one hour", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```





### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html


#data(Fleiss1993cont)

#m1 <- metacont(n.psyc, mean.psyc, sd.psyc, n.cont, mean.cont, sd.cont,
 # data = Fleiss1993cont, sm = "SMD")
#m1
#forest(m1)

######## manually create the data matrix 
study_data=matrix(nrow=15, ncol=6)
study_data[1,]=c(as.numeric(data_1hour_full[1,3:5]), as.numeric(data_1hour_full[2,3:5]))
study_data[2,]=c(as.numeric(data_1hour_full[3,3:5]), as.numeric(data_1hour_full[4,3:5]))
study_data[3,]=c(as.numeric(data_1hour_full[6,3:5]), as.numeric(data_1hour_full[5,3:5]))
study_data[4,]=c(as.numeric(data_1hour_full[7,3:5]), as.numeric(data_1hour_full[5,3:5]))
study_data[5,]=c(as.numeric(data_1hour_full[8,3:5]), as.numeric(data_1hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_1hour_full[10,3:5]), as.numeric(data_1hour_full[11,3:5]))
study_data[7,]=c(as.numeric(data_1hour_full[12,3:5]), as.numeric(data_1hour_full[14,3:5]))
study_data[8,]=c(as.numeric(data_1hour_full[13,3:5]), as.numeric(data_1hour_full[14,3:5]))
study_data[9,]=c(as.numeric(data_1hour_full[15,3:5]), as.numeric(data_1hour_full[17,3:5]))
study_data[10,]=c(as.numeric(data_1hour_full[16,3:5]), as.numeric(data_1hour_full[17,3:5]))
study_data[11,]=c(as.numeric(data_1hour_full[18,3:5]), as.numeric(data_1hour_full[19,3:5]))

study_data[12,]=c(as.numeric(data_1hour_full[6,3:5]), as.numeric(data_1hour_full[7,3:5]))
study_data[13,]=c(as.numeric(data_1hour_full[8,3:5]), as.numeric(data_1hour_full[10,3:5]))
study_data[14,]=c(as.numeric(data_1hour_full[12,3:5]), as.numeric(data_1hour_full[13,3:5]))
study_data[15,]=c(as.numeric(data_1hour_full[15,3:5]), as.numeric(data_1hour_full[16,3:5]))


comparison=c("Pearlman, B._ibuprofen_vs_placebo", 
             "Pereira, G._ibuprofen_vs_placebo", 
             "Pilatti, G._dexamethasone 4mg_vs_placebo", 
             "Pilatti, G._celecoxib 200mg_vs_placebo", 
             "Santos, B._ibuprofen_vs_placebo",  
             "Santos, B._nimesilide_vs_placebo", 
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg", 
             "Santos, B._ibuprofen_vs_nimesilide", 
             "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
             "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg")


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:11,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:11],
                 data = data_meta[1:11,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "one hour", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################### forest plot without Pereira
variable_include_index=c(1,3:11)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```


* For an individual study, a square with treatment estimate in the center and confidence interval as line extending either side of the square.  The size of this square is determined by the weight. 

* vertical reference lines indicates the point of no effect 


* For meta-analysis results, a diamond with treatment estimate in the center and right and left side corresponding to lower and upper confidence limits

* heterogeneity (null hypothesis: all studies estimate the same effect) is measured by Cochran’s Q, which is calculated as the weighted sum of squared differences between individual study effects and the pooled effect across studies, following $\chi^2$ distribution with number of studies-1 DF. 

* $I^2$ statistic describes the percentage of variation across studies that is due to heterogeneity rather than chance
[more details](https://www.statsdirect.com/help/meta_analysis/heterogeneity.htm#:~:text=Heterogeneity%20in%20meta%2Danalysis%20refers,the%20inconsistency%20of%20studies'%20results). 

* [SMD interpretations](https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-14-30#:~:text=Firstly%2C%20the%20SMD%20can%20be,a%20large%20effect%20%5B2%5D.)

```{r, echo=T, message=F, warning=F}
n1=63; s1=21; n2=61; s2=25
# Calculate s_pooled
s_pooled <- sqrt(  # s_pooled is pooled standard deviation
  (((n1-1)*s1^2) + ((n2-1)*s2^2))/
    ((n1-1)+(n2-1))
)

# Calculate the standard error
se <- s_pooled*sqrt((1/n1)+(1/n2))
#se

mean1=10; mean2=19
(mean1-mean2)/s_pooled  # this is SMD 
```



### network meta-analysis 

```{r, echo=F, message=F, warning=F}

############# an example 
#data(TherapyFormats)

#head(TherapyFormats[1:5])
#as.matrix(table(TherapyFormats$author))
#m.netmeta <- netmeta(TE = TE,
#                     seTE = seTE,
#                     treat1 = treat1,
#                     treat2 = treat2,
#                     studlab = author,
#                     data = TherapyFormats,
#                     sm = "SMD",
#                     fixed = TRUE,
#                     random = FALSE,
#                     reference.group = "cau",
#                     details.chkmultiarm = TRUE,
#                     sep.trts = " vs ")
#summary(m.netmeta)

#########################

treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")


data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2, versus=paste(treat1, "VS", treat2, sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, 
         )



```

* overall comparison structure 
* direct links mean there are direct comparison, otherwise indirect comparisons 
* degree of thickness represents how often we find a specific comparison
* numbers on the edge indicate how many studies involve that comparison





```{r, echo=F, message=F, warning=F, eval=T}
## Visualizing Direct and Indirect Evidence
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity: I^2=80.6%",
       label.right = "95% CI, [54.5%; 91.7%]",
       labels = long.labels)
#summary(m.netmeta)

```

* higher P-score, the better it is 



```{r, echo=F, message=F, warning=F}
#netheat(m.netmeta, nchar.trts=3, random = TRUE)
#netsplit(m.netmeta) %>% forest()
```




## three hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_3hour=data$`ThreeHours`[,c(1,3,8, 5,7)]
data_3hour_full=as_tibble(data_3hour[complete.cases(data_3hour), ]) 
colnames(data_3hour_full)=c("study", "treatment", "n", "mean", "sd")
data_3hour_full=data_3hour_full[-c(1,2,3),]
data_3hour_full$study[11]="Steffens, J 2010"
data_3hour_full$study[12]="Steffens, J 2010"

data_3hour_full%>%
datatable(extensions = 'Buttons',
          caption = "three hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html


#data(Fleiss1993cont)

#m1 <- metacont(n.psyc, mean.psyc, sd.psyc, n.cont, mean.cont, sd.cont,
 # data = Fleiss1993cont, sm = "SMD")
#m1
#forest(m1)

######## manually create the data matrix 
study_data=matrix(nrow=13, ncol=6)
study_data[1,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[1,3:5]))
study_data[2,]=c(as.numeric(data_3hour_full[3,3:5]), as.numeric(data_3hour_full[1,3:5]))

study_data[3,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[6,3:5]))
study_data[4,]=c(as.numeric(data_3hour_full[5,3:5]), as.numeric(data_3hour_full[6,3:5]))
study_data[5,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_3hour_full[8,3:5]), as.numeric(data_3hour_full[9,3:5]))
study_data[7,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[10,3:5]))
study_data[8,]=c(as.numeric(data_3hour_full[12,3:5]), as.numeric(data_3hour_full[10,3:5]))
study_data[9,]=c(as.numeric(data_3hour_full[13,3:5]), as.numeric(data_3hour_full[14,3:5]))

study_data[10,]=c(as.numeric(data_3hour_full[2,3:5]), as.numeric(data_3hour_full[3,3:5]))
study_data[11,]=c(as.numeric(data_3hour_full[4,3:5]), as.numeric(data_3hour_full[5,3:5]))
study_data[12,]=c(as.numeric(data_3hour_full[7,3:5]), as.numeric(data_3hour_full[8,3:5]))
study_data[13,]=c(as.numeric(data_3hour_full[11,3:5]), as.numeric(data_3hour_full[12,3:5]))




comparison=c("Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",  
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo",   
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
            "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg", 
            "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:9,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:9],
                 data = data_meta[1:9,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "3 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### network meta-analysis 



```{r, echo=F, message=F, warning=F}

#########################

treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")


data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.1,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, 
         )



```

* overall comparison structure 
* direct links mean there are direct comparison, otherwise indirect comparisons 
* degree of thickness represents how often we find a specific comparison
* numbers on the edge indicate how many studies involve that comparison





```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity, I^2=0",
       label.right = "95% CI, [0.0%; 79.2%]",
       labels = long.labels)
#summary(m.netmeta)
```

* higher P-score, the better it is 



## 6 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_6hour=data$`SixHours`[,c(1,3,8, 5,7)]
data_6hour_full=as_tibble(data_6hour[complete.cases(data_6hour), ]) 
colnames(data_6hour_full)=c("study", "treatment", "n", "mean", "sd")

data_6hour_full$study[17]="Steffens, J 2010"
data_6hour_full$study[18]="Steffens, J 2010"

data_6hour_full%>%
datatable(extensions = 'Buttons',
          caption = "6 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=17, ncol=6)
study_data[1,]=c(as.numeric(data_6hour_full[1,3:5]), as.numeric(data_6hour_full[2,3:5]))
study_data[2,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[3,3:5]))
study_data[3,]=c(as.numeric(data_6hour_full[5,3:5]), as.numeric(data_6hour_full[3,3:5]))
study_data[4,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[7,3:5]))
study_data[5,]=c(as.numeric(data_6hour_full[8,3:5]), as.numeric(data_6hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[12,3:5]))
study_data[7,]=c(as.numeric(data_6hour_full[11,3:5]), as.numeric(data_6hour_full[12,3:5]))
study_data[8,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[15,3:5]))
study_data[9,]=c(as.numeric(data_6hour_full[14,3:5]), as.numeric(data_6hour_full[15,3:5]))
study_data[10,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[16,3:5]))
study_data[11,]=c(as.numeric(data_6hour_full[18,3:5]), as.numeric(data_6hour_full[16,3:5]))
study_data[12,]=c(as.numeric(data_6hour_full[19,3:5]), as.numeric(data_6hour_full[20,3:5]))

study_data[13,]=c(as.numeric(data_6hour_full[4,3:5]), as.numeric(data_6hour_full[5,3:5]))
study_data[14,]=c(as.numeric(data_6hour_full[6,3:5]), as.numeric(data_6hour_full[8,3:5]))
study_data[15,]=c(as.numeric(data_6hour_full[10,3:5]), as.numeric(data_6hour_full[11,3:5]))
study_data[16,]=c(as.numeric(data_6hour_full[13,3:5]), as.numeric(data_6hour_full[14,3:5]))
study_data[17,]=c(as.numeric(data_6hour_full[17,3:5]), as.numeric(data_6hour_full[18,3:5]))



comparison=c("Pereira, G._ibuprofen_vs_placebo",  
             "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             "Santos, B._ibuprofen_vs_placebo1",
             "Santos, B._nimesilide_vs_placebo2", 
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo",   
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
             "Santos, B._ibuprofen_vs_nimesilide",
            "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:12,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:12],
                 data = data_meta[1:12,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "6 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

##################### forest plot without Pereira
variable_include_index=2:12

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



### network meta-analysis 



```{r, echo=F, message=F, warning=F}
comparison[4]="Santos, B._ibuprofen_vs_placebo"
comparison[5]="Santos, B._nimesilide_vs_placebo"
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.2,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, 
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity, 0",
       label.right = "95% CI, [0.0%; 74.6%]",
       labels = long.labels)
#summary(m.netmeta)
```

## 8 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_8hour=data$`EightHours`[,c(1,3,8, 5,7)]
data_8hour_full=as_tibble(data_8hour[complete.cases(data_8hour), ]) 
colnames(data_8hour_full)=c("study", "treatment", "n", "mean", "sd")

data_8hour_full$study[13]="Steffens, J 2010"
data_8hour_full$study[14]="Steffens, J 2010"

data_8hour_full%>%
datatable(extensions = 'Buttons',
          caption = "8 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=14, ncol=6)
study_data[1,]=c(as.numeric(data_8hour_full[2,3:5]), as.numeric(data_8hour_full[1,3:5]))
study_data[2,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[1,3:5]))

study_data[3,]=c(as.numeric(data_8hour_full[4,3:5]), as.numeric(data_8hour_full[5,3:5]))

study_data[4,]=c(as.numeric(data_8hour_full[6,3:5]), as.numeric(data_8hour_full[8,3:5]))
study_data[5,]=c(as.numeric(data_8hour_full[7,3:5]), as.numeric(data_8hour_full[8,3:5]))

study_data[6,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[11,3:5]))
study_data[7,]=c(as.numeric(data_8hour_full[10,3:5]), as.numeric(data_8hour_full[11,3:5]))

study_data[8,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[12,3:5]))
study_data[9,]=c(as.numeric(data_8hour_full[14,3:5]), as.numeric(data_8hour_full[12,3:5]))

study_data[10,]=c(as.numeric(data_8hour_full[15,3:5]), as.numeric(data_8hour_full[16,3:5]))

study_data[11,]=c(as.numeric(data_8hour_full[3,3:5]), as.numeric(data_8hour_full[2,3:5]))
study_data[12,]=c(as.numeric(data_8hour_full[6,3:5]), as.numeric(data_8hour_full[7,3:5]))
study_data[13,]=c(as.numeric(data_8hour_full[9,3:5]), as.numeric(data_8hour_full[10,3:5]))
study_data[14,]=c(as.numeric(data_8hour_full[13,3:5]), as.numeric(data_8hour_full[14,3:5]))




comparison=c( "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Sanchez-Perez, A._dexketoprofen trometamol (DKT) 25mg_vs_placebo",
             
             "Steffens, J 2011_dexamethasone 4mg_vs_placebo", 
             "Steffens, J 2011_dexamethasone 8mg_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_dexamethasone 8mg_vs_placebo", 
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
            "Steffens, J 2011_dexamethasone 4mg_vs_dexamethasone 8mg", 
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg",  
            "Steffens, J 2010_dexamethasone 8mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:10,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:10],
                 data = data_meta[1:10,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "8 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### network meta-analysis 



```{r, echo=F, message=F, warning=F}
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.3,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE, srt.labels = 35
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity, I^2=0",
       label.right = "95% CI, [0.0%; 79.2%]",
       labels = long.labels)
#summary(m.netmeta)
```


## 24 hours 

### sample data 

```{r, echo=F, message=F, warning=F}
data_24hour=data$`TwentyfourHours`[,c(1,3,8, 5,7)]
data_24hour_full=as_tibble(data_24hour[complete.cases(data_24hour), ]) 
colnames(data_24hour_full)=c("study", "treatment", "n", "mean", "sd")

data_24hour_full$study[16]="Steffens, J 2010"
data_24hour_full$study[17]="Steffens, J 2010"

data_24hour_full=data_24hour_full[-16,]

data_24hour_full%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=14, ncol=6)
study_data[1,]=c(as.numeric(data_24hour_full[1,3:5]), as.numeric(data_24hour_full[2,3:5]))

study_data[2,]=c(as.numeric(data_24hour_full[4,3:5]), as.numeric(data_24hour_full[3,3:5]))
study_data[3,]=c(as.numeric(data_24hour_full[5,3:5]), as.numeric(data_24hour_full[3,3:5]))

study_data[4,]=c(as.numeric(data_24hour_full[6,3:5]), as.numeric(data_24hour_full[7,3:5]))

study_data[5,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[9,3:5]))
study_data[6,]=c(as.numeric(data_24hour_full[10,3:5]), as.numeric(data_24hour_full[11,3:5]))

study_data[7,]=c(as.numeric(data_24hour_full[12,3:5]), as.numeric(data_24hour_full[14,3:5]))
study_data[8,]=c(as.numeric(data_24hour_full[13,3:5]), as.numeric(data_24hour_full[14,3:5]))

study_data[9,]=c(as.numeric(data_24hour_full[16,3:5]), as.numeric(data_24hour_full[15,3:5]))

study_data[10,]=c(as.numeric(data_24hour_full[17,3:5]), as.numeric(data_24hour_full[18,3:5]))

study_data[11,]=c(as.numeric(data_24hour_full[19,3:5]), as.numeric(data_24hour_full[20,3:5]))

study_data[12,]=c(as.numeric(data_24hour_full[4,3:5]), as.numeric(data_24hour_full[5,3:5]))
study_data[13,]=c(as.numeric(data_24hour_full[8,3:5]), as.numeric(data_24hour_full[10,3:5]))
study_data[14,]=c(as.numeric(data_24hour_full[12,3:5]), as.numeric(data_24hour_full[13,3:5]))





comparison=c( "Pereira, G._ibuprofen_vs_placebo", 
              
              "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Sanchez-Perez, A._dexketoprofen trometamol (DKT) 25mg_vs_placebo",
             
             "Santos, B._ibuprofen_vs_placebo",
             "Santos, B._nimesilide_vs_placebo", 
             
             "Steffens, J 2011 @_celecoxib 200mg_vs_placebo", 
             "Steffens, J 2011 @_etoricoxib 120mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Trombelli, L._ketorolac 10mg_vs_placebo", 
             
             "Vieth, M._dexamethasone 8mg IV_vs_placebo",
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
             "Santos, B._ibuprofen_vs_nimesilide",
            "Steffens, J 2011 @_celecoxib 200mg_vs_etoricoxib 120mg" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:12,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:12],
                 data = data_meta[1:12,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "24 hours", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

##################### forest plot without Pereira
variable_include_index=2:12

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```




### network meta-analysis 



```{r, echo=F, message=F, warning=F}
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.5,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE,  srt.labels = 35
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity, I^2=55.8%",
       label.right = "95% CI, [0.0%; 85.4%]",
       labels = long.labels)
#summary(m.netmeta)
```



## 3 days 

### sample data 

```{r, echo=F, message=F, warning=F}
data_3day=data$`ThreeDays`[,c(1,3,8, 5,7)]
data_3day_full=as_tibble(data_3day[complete.cases(data_3day), ]) 
colnames(data_3day_full)=c("study", "treatment", "n", "mean", "sd")

data_3day_full$study[13]="Steffens, J 2010"
data_3day_full$study[14]="Steffens, J 2010"

data_3day_full=data_3day_full[-13,] # remove row 13 as it has 0 mean and sd 

data_3day_full%>%
datatable(extensions = 'Buttons',
          caption = "3 days", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### forest plot 

```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=10, ncol=6)
study_data[1,]=c(as.numeric(data_3day_full[1,3:5]), as.numeric(data_3day_full[2,3:5]))

study_data[2,]=c(as.numeric(data_3day_full[4,3:5]), as.numeric(data_3day_full[3,3:5]))
study_data[3,]=c(as.numeric(data_3day_full[5,3:5]), as.numeric(data_3day_full[3,3:5]))

study_data[4,]=c(as.numeric(data_3day_full[6,3:5]), as.numeric(data_3day_full[7,3:5]))

study_data[5,]=c(as.numeric(data_3day_full[8,3:5]), as.numeric(data_3day_full[9,3:5]))
study_data[6,]=c(as.numeric(data_3day_full[10,3:5]), as.numeric(data_3day_full[11,3:5]))

study_data[7,]=c(as.numeric(data_3day_full[13,3:5]), as.numeric(data_3day_full[12,3:5]))

study_data[8,]=c(as.numeric(data_3day_full[14,3:5]), as.numeric(data_3day_full[15,3:5]))

study_data[9,]=c(as.numeric(data_3day_full[4,3:5]), as.numeric(data_3day_full[5,3:5]))
study_data[10,]=c(as.numeric(data_3day_full[8,3:5]), as.numeric(data_3day_full[10,3:5]))






comparison=c( "Pereira, G._ibuprofen_vs_placebo", 
              
              "Pilatti, G._dexamethasone 4mg_vs_placebo",  
             "Pilatti, G._celecoxib 200mg_vs_placebo",
             
             "Sanchez-Perez, A._dexketoprofen trometamol (DKT) 25mg_vs_placebo",
             
             "Santos, B._ibuprofen_vs_placebo",
             "Santos, B._nimesilide_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo", 
             
             "Vieth, M._dexamethasone 8mg IV_vs_placebo",
             
             "Pilatti, G._dexamethasone 4mg_vs_celecoxib 200mg",
             "Santos, B._ibuprofen_vs_nimesilide" )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)

m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[1:8,], sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison[1:8],
                 data = data_meta[1:8,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "3 days", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
##################### forest plot without Pereira
variable_include_index=2:8

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest.meta(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```



### network meta-analysis 



```{r, echo=F, message=F, warning=F}
#########################
treat1=treat2=study=character()
for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

data_meta_network=data.frame(study=study, TE=m1$TE, seTE=m1$seTE, treat1=treat1, treat2=treat2)
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.5,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

long.labels=m.netmeta$trts

netgraph(m.netmeta, 
         labels = long.labels, number.of.studies = TRUE,  srt.labels = 40, points=FALSE
         )



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "Heterogeneity, I^2=76.4%",
       label.right = "95% CI, [0.0%; 94.6%]",
       labels = long.labels)
#summary(m.netmeta)
```





## Sample size determination 


 * [Olsen paper](https://pubmed.ncbi.nlm.nih.gov/28215182/) 


```{r, echo=T, message=F, warning=F}

mean_difference=seq(1,20); # use the median difference as mean difference  
SD=18/1.35 # use SD=IQR/1.35 
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```
* sample size with varying mean difference, given 80\% power. 


* [Santos paper](https://pubmed.ncbi.nlm.nih.gov/34031888/)

```{r, echo=T, message=F, warning=F}

mean_difference=seq(0.1,4, by=0.5); #  mean difference  
SD=max(1.48,1.21) # use SD maximum  
sample_size=numeric()
for (i in 1:length(mean_difference))
  sample_size[i]=round(power.t.test(power = .80, delta = mean_difference[i], alternative = "two.sided", sig.level=0.05, sd=SD)$n)

data.frame(mean_difference, sample_size)%>%
datatable(extensions = 'Buttons',
          caption="mean difference vs sample size",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
 * sample size with varying mean difference, given 80\% power.
 
 