---
title: "3 days"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2024-05-13"
---


## Home 


[Home](2023_0301_Christos.html)



## 72 hours 


```{r, echo=F, message=F, warning=F}
rm(list=ls())
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
library(meta)
library(netmeta)
library(dmetar)
```


```{r, echo=F, message=F, warning=F, results=F}

data=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202301\\Christos\\Data for VAS 09182023_han.xlsx")
```


### sample data 

```{r, echo=F, message=F, warning=F}
data_3day=data$`3 Days`[,c(1,3,8, 5,7)]
data_3day_full=as_tibble(data_3day[complete.cases(data_3day), ]) 
colnames(data_3day_full)=c("study", "treatment", "n", "mean", "sd")


data_3day_full=data_3day_full[-13,] # remove row 13 as it has 0 mean and sd 

data_3day_full%>%
datatable(extensions = 'Buttons',
          caption = "3 days", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```




### forest plot 


#### 3 days - ALL studies per author – no groups




```{r, echo=F, message=F, warning=F}
##### https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/forest.html

######## manually create the data matrix 

study_data=matrix(nrow=4, ncol=6)
study_data[1,]=c(as.numeric(data_3day_full[1,3:5]), as.numeric(data_3day_full[2,3:5]))

study_data[2,]=c(as.numeric(data_3day_full[8,3:5]), as.numeric(data_3day_full[9,3:5]))
study_data[3,]=c(as.numeric(data_3day_full[10,3:5]), as.numeric(data_3day_full[11,3:5]))

study_data[4,]=c(as.numeric(data_3day_full[13,3:5]), as.numeric(data_3day_full[12,3:5]))








comparison=c( "Pereira, G._ibuprofen 600mg_vs_placebo", 
             
             "Santos, B._ibuprofen 600mg_vs_placebo",
             "Santos, B._nimesulide 100mg_vs_placebo", 
             
             "Steffens, J 2010_etoricoxib 120mg_vs_placebo" 
             )


data_meta=data.frame(comparison=comparison, samplesize_exp=study_data[,1], mean_exp=study_data[,2], sd_exp=study_data[,3], samplesize_contr=study_data[,4], mean_contr=study_data[,5], sd_contr=study_data[,6] )

colnames(study_data)=c("samplesize_exp", "mean_exp", "sd_exp", "samplesize_contr", "mean_contr", "sd_contr")
rownames(study_data)=comparison

data_meta=data.frame(study_data)
```


* random effect model 


```{r, echo=F, message=F, warning=F}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 


```



* fixed effect model 


```{r, echo=F, message=F, warning=F}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

########### generate object for plot 

m.gen <- metagen(TE = m1$TE,
                 seTE =m1$seTE,
                 studlab = comparison,
                 data = data_meta,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

#forest.meta(m.gen, sortvar = TE, 
#            prediction = FALSE, 
#            print.tau2 = FALSE, 
#            leftlabs = c("sudy", "g", "SE")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.10
`> -0.33*(4)^0.5*(-0.02+0.64)/3.92
[1]  -0.1043878`



```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen$zval.common, 4), pval=round(m.gen$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


#### 3 days - Studies per surgery

MA 1 – periodontal flap surgery


* random effect model 

```{r, echo=F, message=F, warning=F, eval=T}

##################### forest plot without Pereira
variable_include_index=c(2:4)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


 * fixed effect model 

```{r, echo=F, message=F, warning=F, eval=T}

##################### forest plot without Pereira
variable_include_index=c(2:4)

m2 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen2 <- metagen(TE = m2$TE,
                 seTE =m2$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen2, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.14
`> -0.41*(3)^0.5*(-0.03+0.79)/3.92
[1]  -0.1376804`



```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen2$zval.common, 4), pval=round(m.gen2$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



#### 3 days - Studies per medication


##### ibuprofen 600mg

* random effect model 

```{r, echo=F, message=F, warning=F}
##################### 
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```



* fixed effect model 

```{r, echo=F, message=F, warning=F}
##################### 
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```

##### nimesulide 100mg

* fixed effect model 


```{r, echo=F, message=F, warning=F}
##################### 
variable_include_index=c(3)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


##### dexamethasone 8mg


##### etoricoxib 120mg

* fixed effect model 


```{r, echo=F, message=F, warning=F}
##################### 
variable_include_index=c(4)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```

#### 3 days - Studies only with ibuproben



* fixed effect model 


```{r, echo=F, message=F, warning=F}
##################### 
variable_include_index=c(1,2)

m3 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[variable_include_index,], sm = "SMD")

########### generate object for plot 

m.gen3 <- metagen(TE = m3$TE,
                 seTE =m3$seTE,
                 studlab = comparison[variable_include_index],
                 data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen3, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=8,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```


#### 3 days - Studies only with dexamethazone

##### dexamethasone 8mg




#### 3 days - Sensitivity analysis


* random effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=4
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="JAMA", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=7,
            leftlabs = c("study", "SE")) # sortvar = TE: sort studies by effect size 

```



* fixed effect model 


```{r, echo=F, message=F, warning=F, eval=T}
#####################
TE_random=numeric(); seTE_random=numeric()
num_comparison=4
for (i in 1:num_comparison)
{
 m_leave_one_out <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta[-i,], sm = "SMD")
 TE_random[i]=m_leave_one_out$TE.random
 seTE_random[i]=m_leave_one_out$seTE.random
}
########### generate object for plot 
comparison_leave_one_out=paste("omitting", comparison[1:num_comparison], sep="_")
m.gen_leave_one_out <- metagen(TE = TE_random,
                 seTE =seTE_random,
                 studlab = comparison_leave_one_out,
             #    data = data_meta[variable_include_index,],
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Different treatments")

#summary(m.gen)

forest(m.gen_leave_one_out, layout="RevMan5", sortvar = TE, 
            prediction = FALSE, 
            print.tau2 = FALSE,
            fontsize=6,
            leftlabs = c("study", "SE", "g")) # sortvar = TE: sort studies by effect size 

```

* raw difference -0.07
`> -0.31*(4)^0.5*(-0.09+0.54)/3.92
[1]  -0.07117347`



```{r, echo=F, message=F, warning=F}
data.frame(Zval=round(m.gen_leave_one_out$zval.common, 4), pval=round(m.gen_leave_one_out$pval.common,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


```{r, echo=F, message=F, warning=F}


data_meta%>%
datatable(extensions = 'Buttons',
          caption = "3 days", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```








### network meta-analysis 


#### random effect model 


```{r,  message=F, warning=F, eval=T}
#########################
treat1=treat2=study=character()

for (i in 1:length(comparison))
{
  position=unlist(gregexpr('_', comparison[i]))
  treat1[i]=substring(comparison[i],position[1]+1,last=position[2]-1)
  treat2[i]=substring(comparison[i],position[3]+1,last=1000000L)
  study[i]=substring(comparison[i], 1,last=position[1]-1)
}


m1 <- metacont(samplesize_exp, mean_exp, sd_exp, samplesize_contr, mean_contr, sd_contr,
  data = data_meta, sm = "SMD")

remove_index=2 # remove one ibuprofen 600mg in Santos, B. 

data_meta_network=data.frame(study=study[-remove_index], TE=m1$TE[-remove_index], seTE=m1$seTE[-remove_index], treat1=treat1[-remove_index], treat2=treat2[-remove_index])
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.1,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = FALSE,
                     random = TRUE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")
#summary(m.netmeta)

#3 days 
#Nimesulide 100mg – 20 
#Etoricoxib 120mg – 15
#Ibuprofen 600mg – 47
#Placebo - 82
 





sample_size=c(15,  47,  20, 82)

node_size <- sqrt(sample_size / max(sample_size))*10


long.labels=m.netmeta$trts

#netgraph(m.netmeta, 
#         labels = long.labels, number.of.studies = TRUE, 
#         )


netgraph(m.netmeta, 
         labels = long.labels, 
         number.of.studies = TRUE, 
         plastic = FALSE,  # Ensures standard network layout
         lty = rep(1, length(m.netmeta$trts)),  # Set all links to solid lines
         lwd = 2,  # Increase line width for clarity
         col = "black",  # Set edge color to black
         col.points = "red",
         cex.point=  node_size, 
         col.number = "cyan"  # Change the color of numbers on edges
)



```

```{r, echo=F, message=F, warning=F}
## Visualizing Direct and Indirect Evidenc
d.evidence <- direct.evidence.plot(m.netmeta)
plot(d.evidence)
```

* a mean path length > 2 means that a comparison estimate should be interpreted with particular caution.




```{r, echo=F, message=F, warning=F}
netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```


#### transitivity analysis (consistency between direct vs indir)


```{r, message=F, warning=F}
netsplit(m.netmeta)
```

```{r, message=F, warning=F}
netsplit(m.netmeta) %>% forest(fontsize = 8, spacing = .4)  # visualize the net split results
```


```{r, message=F, warning=F}
funnel(m.netmeta, order=unique(m.netmeta$treat1), pch=seq(1:3), col=seq(1:3), linreg = T,  legend = F, digits.pval=2)
funnel(m.netmeta, order=unique(m.netmeta$treat1), pch=seq(1:3), col=seq(1:3), linreg = F,  legend = F, digits.pval=2)
```



#### fixed effect model 

```{r, echo=F, message=F, warning=F}
remove_index=2 # remove one ibuprofen 600mg in Santos, B.  check why need to remove this one????????
data_meta_network=data.frame(study=study[-remove_index], TE=m1$TE[-remove_index], seTE=m1$seTE[-remove_index], treat1=treat1[-remove_index], treat2=treat2[-remove_index], versus=paste(treat1[-remove_index], "VS", treat2[-remove_index], sep=" "))
m.netmeta <- netmeta(TE = TE,
                     seTE = seTE,
                     treat1 = treat1,
                     treat2 = treat2,
                     studlab = study,
                     tol.multiarm=0.6,
                #     tol.multiarm.se = NULL,
                     data = data_meta_network,
                     sm = "SMD",
                     fixed = TRUE,
                     random = FALSE,
                     reference.group = "placebo",
                     details.chkmultiarm = TRUE,
                     sep.trts = " vs ")



netrank(m.netmeta, small.values = "good")

forest(m.netmeta, 
       reference.group = "placebo",
       sortvar = TE,
     #  xlim = c(-1.3, 0.5),
       smlab = paste("",
                     ""),
       drop.reference.group = TRUE,
       label.left = "",
       label.right = "",
       labels = long.labels)
#summary(m.netmeta)
decomp.design(m.netmeta)
```
