---
title: "06/27/2023"
output: html_document
date: "2023-06-27"
---

```{r setup, include=FALSE}
rm(list=ls())
library(tidyverse)
library(kableExtra)
library(ggpubr)
library(rstatix) # use anova_test function 
library(grid)
library(DT)
library(gridExtra)
library(matrixStats)
library(cowplot)
set.seed(123)
```




```{r, echo=F, warning=F, message=F}
######## adjust p values 
pvalue_adjust=function(p_value)
{
  p_value_adjust=numeric()
for (i in 1:length(p_value))
{
  if (is.na(p_value[i])==T)
    p_value_adjust[i]=p_value[i]
  if (is.na(p_value[i])==F & p_value[i]<0.0001)
    p_value_adjust[i]="<0.0001"
  if (is.na(p_value[i])==F & p_value[i]>0.0001)
    p_value_adjust[i]=round(p_value[i],4)
}
  return(p_value_adjust)
}
############### summary statistics for continuous variable 
summary_statistics=function(data)
{  # each column is one variable, and row one subject 
  
variables=colnames(data)
num_sample=numeric()
Mean=numeric()
Median=numeric()
SD=numeric()
SE=numeric()
range_min=numeric()
range_max=numeric()
normality_pvalue=numeric()
per_25_quantile=numeric()
per_75_quantile=numeric()

for (i in 1:ncol(data))
{
  observation=data[,i]
  observation=observation[!is.na(observation)] # remove missing values 
  num_sample[i]=length(observation)
  Mean[i]=round(mean(observation),4)
  Median[i]=round(median(observation),4)
  SD[i]=round(sd(observation),4)
  SE[i]=round(SD[i]/sqrt(num_sample[i]),4)
  per_25_quantile[i]=round(quantile(observation, prob=0.25),4)
  per_75_quantile[i]=round(quantile(observation, prob=0.75),4)
  range_min[i]=round(min(observation),4)
  range_max[i]=round(max(observation),4)
  normality_pvalue[i]=round(shapiro.test(observation)$p.value,4)
}

summary_data=data.frame(variable=variables, num_sample=num_sample, Mean=Mean, Median=Median, SD=SD, SE=SE,per_25_quantile, per_75_quantile, Range_low=range_min, Range_upper=range_max, normality_pvalue=normality_pvalue)

summary_data%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 return(summary_data) 
}

```

```{r, echo=F, message=F, warning=F}
pre_treatment=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Matthew\\Generated Patient List_pretx.csv",stringsAsFactors=FALSE, fileEncoding="latin1", header=T))
post_treatment=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Matthew\\Generated Patient List_postx.csv",stringsAsFactors=FALSE, fileEncoding="latin1", header=T))
UserError=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Matthew\\UserError.csv",stringsAsFactors=FALSE, fileEncoding="latin1", header=F))
Pre_UserError=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Matthew\\Pre_UserError.csv",stringsAsFactors=FALSE, fileEncoding="latin1", header=F))
```


## Summary statistics 


```{r, echo=F, message=F, warning=F}
variables=pre_treatment$X[1:19]
average_pre=numeric(); sd_pre=numeric()
average_post=numeric(); sd_post=numeric()
for (i in 1:length(variables))
{
  average_pre[i]=mean(as.numeric(pre_treatment[i,2:20])); sd_pre[i]=sd(as.numeric(pre_treatment[i,2:20]))
  average_post[i]=mean(as.numeric(post_treatment[i,2:20])); sd_post[i]=sd(as.numeric(post_treatment[i,2:20]))
}
summary=data.frame(variable=rep(variables,2), average=c(average_pre, average_post), sd=c(sd_pre, sd_post), treatment=rep(c("pre", "post"), each=length(variables)))



ggplot(summary, aes(x=variable, y=average, fill=treatment)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=average-sd, ymax=average+sd), width=.2,
                 position=position_dodge(.9))+
  theme(legend.title=element_blank())+
  ylab("")+
  theme(legend.title = element_blank(), legend.text=element_text(size=9))+theme(legend.position="bottom")+
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size=7))+
 theme(text = element_text(size=10))+ # size is for labels on x axis 
  theme(axis.title = element_text(size = 13))+ # Font Size of Axis Titles
 theme(legend.spacing.x = unit(0.5, 'cm')) # add space between symbols in legend

data.frame(variable=variables, average_pre=round(average_pre,4),  sd_pre=round(sd_pre,4),  average_post=round(average_post,4), sd_post=round(sd_post,4))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

### pre vs post 

```{r, echo=F, message=F, warning=F}
pvalue=numeric(); wilcox_test_pvalue=numeric()
pre_data_matrix=matrix(nrow=19, ncol=length(variables)); colnames(pre_data_matrix)=variables 
post_data_matrix=matrix(nrow=19, ncol=length(variables)); colnames(post_data_matrix)=variables
diff_sum=numeric()
for (i in 1:length(variables))
{
  pre=as.numeric(pre_treatment[i,2:20])
  post=as.numeric(post_treatment[i,2:20])
  test=t.test(pre, post, paired=T)
  pvalue[i]=pvalue_adjust(test$p.value)
  
  pre_data_matrix[,i]=pre
  post_data_matrix[,i]=post
  
  diff_sum[i]=(sum((pre-post)^2)/(2*length(pre)))^0.5
  wilcox_test_pvalue[i]=wilcox.test(pre, post, alternative = "two.sided")$p.value
}

summary_statistics(pre_data_matrix)%>%
datatable(extensions = 'Buttons',
          caption="pre_treatment",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

summary_statistics(post_data_matrix)%>%
datatable(extensions = 'Buttons',
          caption="post_treatment",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

data.frame(variable=variables, t_test_pvalue=pvalue, wilcox_test_pvalue=pvalue_adjust(wilcox_test_pvalue))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
# Dahlberg error is diff_sum/(2*length()

```

* use two sample paired t test to test the difference between pre and post treatment.


* `wilcox_test_pvalue`, p value of non-parametric two sample wilcox test


## ICC


### post treatment 


```{r, echo=F, message=F, warning=F}
library(irr)
icc(UserError[,2:4], model ="oneway",  type = "consistency")
```



### pre treatment 


```{r, echo=F, message=F, warning=F}
library(irr)
icc(Pre_UserError[1:19,2:4], model ="oneway",  type = "consistency")
```


## Dahlberg error

###  post treatment 



```{r, echo=F, message=F, warning=F}
DahlbergError=round(abs(UserError[,2]-UserError[,3]),4)
data.frame(variable=variables, Dahlberg_error=DahlbergError)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* Dahlberg error is calculated as $D=\sqrt{\sum_{i=1}^N \frac{d_i^2}{N}}$, $d_i$ is difference between pre and post treatment for $i$ th individual, $i=1, 2, \cdots, N$, $N$ is sample size, the smaller the Dahlberg error, the more agreement between two observations. 

* V2 is Dahlberg error. 

###  pre treatment 



```{r, echo=F, message=F, warning=F}
DahlbergError=round(((Pre_UserError[1:19,2]-Pre_UserError[1:19,3])^2)^0.5,4)
data.frame(variable=variables, Dahlberg_error=DahlbergError)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


###  pre treatment-post treatment 


```{r, echo=F, message=F, warning=F}
pre_post_diff=Pre_UserError[1:19,2:4]-UserError[1:19,2:4]
DahlbergError=round(((pre_post_diff[,2]-pre_post_diff[,3])^2)^0.5,4)
data.frame(variable=variables, Dahlberg_error=DahlbergError)%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


## correlation matrix for changes

```{r, echo=F, message=F, warning=F}
change_stat=as_tibble(read.csv("C:\\Shengtong\\Research\\AllCollaboration\\2023\\202306\\Matthew\\To dr han - 2023-7-7.csv",stringsAsFactors=FALSE, fileEncoding="latin1", header=T))
change_stat1=as.matrix(change_stat[1:20,2:20])
library(reshape2)
sub_data=change_stat1
################ compute p values 
cormat2=round(cor(sub_data, method="pearson"),2)
cormat2_pvalue=matrix(nrow=nrow(cormat2), ncol=nrow(cormat2))
for (i in 1:nrow(cormat2))
  for (j in 1:ncol(cormat2))
    cormat2_pvalue[i,j]=round(cor.test(sub_data[,i], sub_data[,j], method="pearson")$p.value,4)
row.names(cormat2_pvalue)=rownames(cormat2) 
colnames(cormat2_pvalue)=rownames(cormat2) 
################
cormat_with_lables <- round(cor(sub_data),2)
sub_data_col_names=colnames(sub_data)
colnames(sub_data)=seq(1:length(sub_data_col_names))
  cormat <- round(cor(sub_data),2)
  
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
  upper_tri <- get_upper_tri(cormat)
  
melted_cormat <- melt(cormat)
melted_cormat_with_labels=melt(cormat_with_lables)

# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Heatmap
var_index=seq(1,length(sub_data_col_names), by=3)
var_index2=1:length(sub_data_col_names)
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  #theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1))+
  scale_x_continuous("", labels = change_stat$X[1:19], breaks = var_index2)+
  scale_y_continuous("", labels = change_stat$X[1:19], breaks = var_index2)#+
 #coord_fixed()

correlation_pvalue=matrix(paste(cormat2, cormat2_pvalue, sep="_"), nrow=nrow(cormat2))
rownames(correlation_pvalue)=change_stat$X[1:19]
colnames(correlation_pvalue)=change_stat$X[1:19]
############################
#ggplot(data = melted_cormat_with_labels, aes(Var2, Var1, fill = value))+
# geom_tile(color = "white")+
# scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
#   midpoint = 0, limit = c(-1,1), space = "Lab", 
#   name="Pearson\nCorrelation") +
#  theme_minimal()+ 
# theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
#    size = 10, hjust = 0.5))+
# coord_fixed()


#write.csv(cormat2, file="../../2022/202209/Juan/Juan_correlation_matrix_1208_2022.csv")
#write.csv(cormat2_pvalue, file="../../2022/202209/Juan/Juan_correlation_matrix_pvalue_1209_2022.csv")
#write.csv(correlation_pvalue, file="../../2022/202209/Juan/Juan_correlation_matrix_pvalue_0222_2023.csv")
#cormat2%>%
#datatable(extensions = 'Buttons',
#            options = list(dom = 'Blfrtip',
#                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
#                           lengthMenu = list(c(10,25,50,-1),
#                                             c(10,25,50,"All"))))

#data.frame(var_index=var_index2, variables=sub_data_col_names)%>%
#datatable(extensions = 'Buttons',
#            options = list(dom = 'Blfrtip',
#                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
#                           lengthMenu = list(c(10,25,50,-1),
#                                             c(10,25,50,"All"))))
```