---
title: "4/11/2024"
output: html_document
date: "2024-04-11"
---


```{r, echo=F, message=F, warning=F, results=F}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
#data_raw=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202403\\Youssef\\Data Averages.xlsx")
#data=as_tibble(data_raw[[1]])
data_raw=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202404\\Zainab\\Zainab_MTT assay_Percentage viability data_041024.xlsx")
data=data_raw$Sheet1
```


## summary statistics 


```{r, echo=F, message=F, warning=F}
data_day1=data[2:16,1:5]
summary=summary_statistics(data_day1)
summary%>%
datatable(extensions = 'Buttons',
          caption = "day 1",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))



data_day7=data[2:16,7:11]
summary=summary_statistics(data_day7)
summary%>%
datatable(extensions = 'Buttons',
          caption = "day 7",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



## pairwise comparisons between groups 

### day 1 

```{r, echo=F, message=F, warning=F}
data_day1=data[2:16,1:5]
k=0
pvalue=numeric()
sample1_index=numeric()
sample2_index=numeric()
for (i in 1:(ncol(data_day1)-1))
  for (j in (i+1):length(data_day1))
{
  k=k+1  
  sample1=as.numeric(data_day1[,i]); sample1_index[k]=i
  sample2=as.numeric(data_day1[,j]); sample2_index[k]=j
  two_sample_test=t.test(sample1, sample2, na.rm=T)
  pvalue[k]=two_sample_test$p.value
  }
data.frame(sample1=sample1_index, sample2=sample2_index, pvalue=pvalue_adjust(pvalue))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


```

* each row are two group index; group 1 is the control group.  

* numbers in red have been removed before the test 

* two  sample t test was used. 


### day 7 



```{r, echo=F, message=F, warning=F}
data_day7=data[2:16,7:11]
##############
library(outliers)
outlier_test <- grubbs.test(as.numeric(data_day7$`7 days`)) # https://rpubs.com/Alema/1000582
outlier_test <- grubbs.test(as.numeric(data_day7$`...11`))
#############

k=0
pvalue=numeric()
sample1_index=numeric()
sample2_index=numeric()
for (i in 1:(ncol(data_day7)-1))
  for (j in (i+1):length(data_day7))
{
  k=k+1  
  sample1=as.numeric(data_day7[,i]); sample1_index[k]=i
  sample2=as.numeric(data_day7[,j]); sample2_index[k]=j
  two_sample_test=t.test(sample1, sample2, na.rm=T)
  pvalue[k]=two_sample_test$p.value
  }
data.frame(sample1=sample1_index, sample2=sample2_index, pvalue=pvalue_adjust(pvalue))%>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


```

*  statistics [Grubbs test](https://rpubs.com/Alema/1000582) doesn't support blue numbers are outliers 


## anova test 



### day 1 

```{r, echo=T, message=F, warning=F}
anova_day1=data.frame(response= as.numeric(unlist(as.vector(data_day1[,2:5]))), covariate=rep(c("group2", "group3", "group4", "group5"), each=nrow(data_day1)))
res.aov <- aov(response ~ covariate, data = anova_day1)
# Summary of the analysis
summary(res.aov)
```

* small p value suggests group 2, 3, 4, 5 are not all equal. 

### day 7 

```{r, echo=T, message=F, warning=F}
anova_day7=data.frame(response= as.numeric(unlist(as.vector(data_day7[,2:5]))), covariate=rep(c("group2", "group3", "group4", "group5"), each=nrow(data_day7)))
res.aov <- aov(response ~ covariate, data = anova_day7)
# Summary of the analysis
summary(res.aov)
```

* large p value fails to reject the null hypothesis of group 2, 3, 4, 5 being equal. 

## comparison between different time points within a group 

```{r, echo=F, message=F, warning=F}
pvalue=numeric()
for (i in 1:ncol(data_day1))
{
 # i=1
  day1=as.numeric(data_day1[,i])
  day7=as.numeric(data_day7[,i])
  test=t.test(day1, day7, paired=T)
  pvalue[i]=test$p.value
  
}
 data.frame(group=seq(1,5), pvalue=pvalue_adjust(pvalue)) %>%
datatable(extensions = 'Buttons',
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

* day 1 and day 7 are compared in every group 
* two sample paired t test was used. 



## statistical software 

```{r, echo=F, message=F, warning=F}
R.version
```