---
title: "dentist in WI analysis"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2024-11-15"
---



```{r, echo=F, message=F, warning=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
```



```{r, echo=F, message=F, warning=F, results=F}
source(file.path(root, "analysis/Rfunctions.R"))
changeCellColor <- function(row, col){
  c(
    "function(row, data, num, index){",
    sprintf("  if(index == %d){", row-1),
    sprintf("    $('td:eq(' + %d + ')', row)", col),
    "    .css({'background-color': 'orange'});",
    "  }",
    "}"  
  )
}
```




```{r, echo=F, message=F, warning=F}
plot_function=function(title, data, legend_rows=1, var_name, num_size=3, legend_text_size=11, y_axis_text=12)
{
  
  x_var <- sym(var_name)  ########## https://stackoverflow.com/questions/4856849/looping-over-variables-in-ggplot this is the key step for the loop 

  
  y_limit=max(data$n)*1.1
g1=ggplot(data, aes(x=!!x_var, y=n, fill=!!x_var)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, y_limit))+
  ylab("n")+xlab("")+
  #theme(legend.position="", legend.title=element_text(size=10))+
  theme(legend.position="bottom", legend.title=element_blank(), legend.text = element_text(size=legend_text_size))+
  theme(axis.text.x = element_blank())+
  theme(axis.text.y = element_text(size = y_axis_text))+
  #geom_text(aes(label=practice_setting2$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  geom_text(label = with(data, paste(n, paste0("(", prop*100, "%", ")"))), vjust=-1, size=num_size)+
  ggtitle(title)+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
   guides(fill = guide_legend(nrow = legend_rows))
  return(g1)
}


side_by_side_barplot2=function(data, angle=0, num_size=3, x_text_size=10, legend_text_size=10, title, legend_rows=1)
{
  y_limit=max(data$n)*1.1
  g=ggplot(data, aes(x=gender, y=n, fill=class)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, y_limit))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom", legend.text = element_text(size=legend_text_size))+
  theme(axis.text.x = element_text(angle = angle, vjust = 0.5, size=x_text_size))+
  #geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25, size=num_size)+  # add numbers over bars
  geom_text(label = with(data, paste(n, paste0("(", prop*100, "%", ")"))),  position=position_dodge(width=0.9), vjust=-1, size=num_size)+
  #geom_text(label = with(gender_geo_data, paste(num, paste0('(', Percent, ')'))), vjust=-1)
  ggtitle(title)+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
    guides(fill = guide_legend(nrow = legend_rows))
 return(g)
  
}


side_by_side_barplot3=function(data, angle=0, num_size=3, x_text_size=10, legend_text_size=10, title, legend_rows=1, fill_var="genders_group")
{
  y_limit=max(data$n)*1.1
  g=ggplot(data, aes(x=races, y=prop, fill=!!sym(fill_var))) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0,y_limit))+
  ylab("prop")+xlab("")+
  theme(legend.position="bottom", legend.text = element_text(size=legend_text_size))+
  theme(axis.text.x = element_text(angle = angle, vjust = 0.5, size=x_text_size))+
  #geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25, size=num_size)+  # add numbers over bars
  #geom_text(label = with(data, paste(n, paste0("(", prop*100, "%", ")"))),  position=position_dodge(width=0.9), vjust=-1, size=num_size)+
    geom_text(label = with(data, paste(paste0(prop*100, "%", "(", n, ")"))),  position=position_dodge(width=0.9), vjust=-1, size=num_size)+
  #geom_text(label = with(gender_geo_data, paste(num, paste0('(', Percent, ')'))), vjust=-1)
  ggtitle(title)+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
    guides(fill = guide_legend(nrow = legend_rows))
 return(g)
  
}

```



## Home 

[Home](2024_0701_survey.html)



```{r, message=F, warning=F, results=F, eval=T}
#Dentist_Survey=multiplesheets(file.path(root, "..\\2024\\202407\\state_survey\\Dentist Survey.xlsx"))
Dentist_Survey=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\state_survey\\Dentist Survey.xlsx")
Dentist_in_WI=Dentist_Survey$`Dentist Survey` %>% filter(`direct care as a dentist in Wisconsin`=="Yes")
#save(Dentist_in_WI, file="C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\Dentist_in_WI.RData")
```


* select individuals who respond Yes to `direct care as a dentist in Wisconsin`



```{r, message=F, warning=F}
#dim(Dentist_Survey$`Dentist Survey`)
load("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\Dentist_in_WI.RData")
variables=colnames(Dentist_in_WI)
data.frame(questions=variables)%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
dim(Dentist_in_WI)
```

* in total 2295 responses and 40 questions 




```{r, message=F, warning=F}
variables_of_interest=variables[-c(6,7,19:37)]
dentist_in_WI_of_interest=Dentist_in_WI[,-c(6,7,19:37)]
num_non_missing=apply(dentist_in_WI_of_interest,2, function(x) sum(is.na(x)==F) )
data.frame(variable=variables_of_interest, non_missing=num_non_missing)%>%
datatable(extensions = 'Buttons',
          caption = " Interesting variables with non-missing numbers ",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```


## Race or Ethnicity

```{r, message=F, warning=F, eval=T}
race=dentist_in_WI_of_interest %>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(dentist_in_WI_of_interest),4))
asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries 
asia_race= race %>% filter(`Describe Your Race or Ethnicity` %in% asia)
race_new=race %>% filter(`Describe Your Race or Ethnicity` %in% asia==F) %>% add_row(`Describe Your Race or Ethnicity`="asia", n=asia_race %>% select(n) %>% sum(), prop=asia_race %>% select(prop) %>% sum()) # combine south east asia countries into one unit 

race_new2=race_new %>% filter(n>10)  %>% add_row(`Describe Your Race or Ethnicity`="other", n=race_new %>% filter(n<=10) %>% select(n) %>% sum(), prop=race_new %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 


fig=plot_function("Describe Your Race or Ethnicity", race_new2, legend_rows = 4, var_name="Describe Your Race or Ethnicity")
fig


fig=plot_function("Describe Your Race or Ethnicity (without White)", race_new2 %>% filter(`Describe Your Race or Ethnicity`!="White"), legend_rows = 3, var_name="Describe Your Race or Ethnicity")
fig

race_new2%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

stopifnot(sum(race_new2$n)==nrow(Dentist_in_WI))
```

* `asia` includes "East Asian", "Filipino", "Hmong", "Laotian", "South Asian"

* `other` aggregates categories with less than 10 responses. 



## association between race and other factors 


### race vs ages 



```{r, message=F, warning=F, results=F}
date_of_birth=dentist_in_WI_of_interest$`Date of Birth`
year_of_birth=str_sub(date_of_birth, nchar(date_of_birth)-3, nchar(date_of_birth))
ages=2024-as.numeric(year_of_birth)
mean(ages)
ggplot(data.frame(ages=ages), aes(x=ages)) + geom_histogram(color="black", fill="blue")+
  geom_vline(aes(xintercept=mean(ages)),
            color="red", linetype="dashed", size=1)
```





```{r, message=F, warning=F}
races=race_new2$`Describe Your Race or Ethnicity`
dentist_in_WI_of_interest1=dentist_in_WI_of_interest %>% mutate(ages=ages)
asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries
count_race=function(data)
{
num=sapply(races[1:6], function(x) data %>% filter(`Describe Your Race or Ethnicity` %in% x) %>% nrow())
num[7]=data %>% filter(`Describe Your Race or Ethnicity` %in% asia) %>% nrow()
num[8]=data %>% filter(!`Describe Your Race or Ethnicity` %in% c(races[1:6], asia)) %>% nrow()
return(num)
}
```





```{r, message=F, warning=F}
age_groups=paste("age", c("<40", "40-50", "50-60", "60-70", ">70"), sep=":")
age_groups_count=matrix(nrow=length(age_groups), ncol=length(races))
  age_groups_count[1,]=count_race(dentist_in_WI_of_interest1 %>% filter(ages<40))
  age_groups_count[2,]=count_race(dentist_in_WI_of_interest1 %>% filter(ages>=40 & ages<50))
  age_groups_count[3,]=count_race(dentist_in_WI_of_interest1 %>% filter(ages>=50 & ages<60))
  age_groups_count[4,]=count_race(dentist_in_WI_of_interest1 %>% filter(ages>=60 & ages<70))
  age_groups_count[5,]=count_race(dentist_in_WI_of_interest1 %>% filter(ages>=70))
 rownames(age_groups_count)=age_groups; 
 colnames(age_groups_count)=races 
 
 age_groups_count %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
 
 
 chisq.test(age_groups_count)
 stopifnot(sum(age_groups_count)==nrow(Dentist_in_WI))
 
 
```

* small p value indicates significant association between ages and races  


```{r, message=F, warning=F}

data.frame(age_groups_count[,-c(2,4, 6,8)]) %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(age_groups_count[,-c(2,4, 6,8)])



prop=c(age_groups_count[,-c(2,4, 6,8)][,1]/(sum(age_groups_count[,-c(2,4, 6,8)][,1])), 
       age_groups_count[,-c(2,4, 6,8)][,2]/(sum(age_groups_count[,-c(2,4, 6,8)][,2])), 
       age_groups_count[,-c(2,4, 6,8)][,3]/(sum(age_groups_count[,-c(2,4, 6,8)][,3])), 
       age_groups_count[,-c(2,4, 6,8)][,4]/(sum(age_groups_count[,-c(2,4, 6,8)][,4])))
age_groups_count_subset=data.frame(races=rep(colnames(age_groups_count[,-c(2,4, 6,8)]), each=length(age_groups)), ages_group=paste(seq(1,5), rep(rownames(age_groups_count[,-c(2,4, 6,8)])), sep=":"), n=c(age_groups_count[,-c(2,4, 6,8)][,1], age_groups_count[,-c(2,4, 6,8)][,2], age_groups_count[,-c(2,4, 6,8)][,3], age_groups_count[,-c(2,4, 6,8)][,4]), prop=round(prop,2))
side_by_side_barplot3(age_groups_count_subset, title="age distrbituon by races", num_size=2.5, fill_var = "ages_group")



 chisq.test(age_groups_count[,-c(2,4, 6,8)])
```


```{r, message=F, warning=F}
library("gplots")
# 1. convert the data as a table
dt <- as.table(as.matrix(age_groups_count[,-c(2,4, 6,8)]))
colnames(dt)[1:2]=c("B/A Americ", "H/L Americ")
# 2. Graph
balloonplot(t(dt), main ="age X races", xlab ="", ylab="",
            label = FALSE, show.margins = FALSE)


library("graphics")
mosaicplot(dt, shade = TRUE, las=2,
           main = "")
```


* dot size reflects the sample sizes 

* Blue color indicates that the observed value is higher than the expected value if the data were random

* Red color specifies that the observed value is lower than the expected value if the data were random

* [reference](http://www.sthda.com/english/wiki/chi-square-test-of-independence-in-r)



###  races vs gender 

```{r, message=F, warning=F}
genders=unique(dentist_in_WI_of_interest1$`Gender Identity`)
genders_group_count=matrix(nrow=length(genders), ncol=length(races))
for (i in 1:length(genders))
 genders_group_count[i,]=count_race(dentist_in_WI_of_interest1 %>% filter(`Gender Identity` %in% genders[i]))

rownames(genders_group_count)=genders; 
 colnames(genders_group_count)=races 

genders_group_count %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


sum(genders_group_count)
chisq.test(genders_group_count)


```


* small p value indicates significant association between genders  and races  


```{r, message=F, warning=F}

data.frame(genders_group_count[1:2,-c(2,4, 6,8)]) %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(genders_group_count[1:2,-c(2,4, 6,8)])



prop=c(genders_group_count[1:2,-c(2,4, 6,8)][,1]/(sum(genders_group_count[1:2,-c(2,4, 6,8)][,1])), 
       genders_group_count[1:2,-c(2,4, 6,8)][,2]/(sum(genders_group_count[1:2,-c(2,4, 6,8)][,2])), 
       genders_group_count[1:2,-c(2,4, 6,8)][,3]/(sum(genders_group_count[1:2,-c(2,4, 6,8)][,3])), 
       genders_group_count[1:2,-c(2,4, 6,8)][,4]/(sum(genders_group_count[1:2,-c(2,4, 6,8)][,4])))
genders_group_count_subset=data.frame(races=rep(colnames(genders_group_count[,-c(2,4, 6,8)]), each=2), genders_group=rep(rownames(genders_group_count[1:2,-c(2,4, 6,8)]), 4), n=c(genders_group_count[1:2,-c(2,4, 6,8)][,1], genders_group_count[1:2,-c(2,4, 6,8)][,2], genders_group_count[1:2,-c(2,4, 6,8)][,3], genders_group_count[1:2,-c(2,4, 6,8)][,4]), prop=round(prop,2))
side_by_side_barplot3(genders_group_count_subset, title="age distrbituon by races", fill_var="genders_group", num_size=2.5)



 chisq.test(age_groups_count[,-c(2,4, 6,8)])
```



```{r, message=F, warning=F}
chisq.test(genders_group_count[1:2,c(1,3,5,7)])

dt <- as.table(as.matrix(genders_group_count[1:2,-c(2,4, 6,8)]))
colnames(dt)[1:2]=c("B/A Americ", "H/L Americ")
# 2. Graph
balloonplot(t(dt), main ="gender X races", xlab ="", ylab="",
            label = FALSE, show.margins = FALSE)


library("graphics")
mosaicplot(dt, shade = TRUE, las=2,
           main = "")

sum(genders_group_count[1:2,c(1,3,5,7)])
```






## Gender Identity

```{r, message=F, warning=F, eval=T}
gender=dentist_in_WI_of_interest1 %>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(dentist_in_WI_of_interest1),4))

fig=plot_function("Gender Identity", gender, legend_rows = 2, var_name = "Gender Identity", num_size = 4, legend_text_size = 13)
fig



gender%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(gender$n)
```




## Dental Specialties Board Certified


```{r, message=F, warning=F, eval=T}
specialty=dentist_in_WI_of_interest1 %>% dplyr::count(`Dental Specialties Board Certified`) %>% mutate(prop=round(n/nrow(dentist_in_WI_of_interest1),4))

specialty2=specialty %>% filter(n>10)  %>% add_row(`Dental Specialties Board Certified`="other", n=specialty %>% filter(n<=10) %>% select(n) %>% sum(), prop=specialty %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 

fig=plot_function("Dental Specialties Board Certified", specialty2, legend_rows = 3, var_name = "Dental Specialties Board Certified", legend_text_size = 12)
fig



specialty2%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(specialty2$n)
```


* `other` aggregates categories with less than 10 responses, such as `General dentistry; Oral surgery`




## Best Describes This Practice Setting


```{r, message=F, warning=F, eval=T}
practice_setting=dentist_in_WI_of_interest1 %>% dplyr::count(`Best Describes This Practice Setting`) %>% mutate(prop=round(n/nrow(dentist_in_WI_of_interest1),4))

threshold=20
practice_setting2=practice_setting %>% filter(n>threshold)  %>% add_row(`Best Describes This Practice Setting`="other", n=practice_setting %>% filter(n<=threshold) %>% select(n) %>% sum(), prop=practice_setting %>% filter(n<=threshold) %>% select(prop) %>% sum()) # aggregate categories with n<=10 
fig=plot_function("Best Describes This Practice Setting", practice_setting2, legend_rows = 4, var_name = "Best Describes This Practice Setting")
fig


practice_setting2%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(practice_setting2$n)
```

`other` aggregates categories with responses less than 20. 



## practice setting distribution 


```{r, echo=F, message=F, warning=F, eval=T}
side_by_side_barplot2=function(data, angle=0, num_size=3, x_text_size=10, legend_text_size=10, title, legend_rows=1)
{
  y_limit=max(data$n)*1.1
  g=ggplot(data, aes(x=gender, y=n, fill=class)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, y_limit))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom", legend.text = element_text(size=legend_text_size))+
  theme(axis.text.x = element_text(angle = angle, vjust = 0.5, size=x_text_size))+
  #geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25, size=num_size)+  # add numbers over bars
  geom_text(label = with(data, paste(n, paste0("(", prop*100, "%", ")"))),  position=position_dodge(width=0.9), vjust=-1, size=num_size)+
  #geom_text(label = with(gender_geo_data, paste(num, paste0('(', Percent, ')'))), vjust=-1)
  ggtitle(title)+
  theme(plot.title = element_text(hjust = 0.5, size=15))+  #center the title
    guides(fill = guide_legend(nrow = legend_rows))
 return(g)
  
}

```



```{r, message=F, warning=F, eval=T}
man_practice_setting=dentist_in_WI_of_interest1 %>% filter(`Gender Identity`=="Man") %>% dplyr::count(`Best Describes This Practice Setting`)
settings=c("Group office practice (any number of dentists >1)", "Solo office practice")
nums=sapply(settings, function(x) man_practice_setting %>% filter(`Best Describes This Practice Setting`==x) %>% select(n) %>%  pull())
nums[4]=man_practice_setting$n[is.na(man_practice_setting$`Best Describes This Practice Setting`)]
nums[3]=sum(man_practice_setting$n)-sum(nums[1:2])-nums[4]
man_practice_setting2=data.frame(class=c(settings, "others", "NA"), n=nums) %>% mutate(prop=round(n/sum(nums),4))

woman_practice_setting=dentist_in_WI_of_interest1 %>% filter(`Gender Identity`=="Woman") %>% dplyr::count(`Best Describes This Practice Setting`)
nums=sapply(settings, function(x) woman_practice_setting %>% filter(`Best Describes This Practice Setting`==x) %>% select(n) %>%  pull())
nums[4]=woman_practice_setting$n[is.na(woman_practice_setting$`Best Describes This Practice Setting`)]
nums[3]=sum(woman_practice_setting$n)-sum(nums[1:2])-nums[4]
woman_practice_setting2=data.frame(class=c(settings, "others", "NA"), n=nums) %>% mutate(prop=round(n/sum(nums),4))

practice_setting_combine=data.frame(class=rep(c(settings, "others", "NA"), 2), n=c(man_practice_setting2$n, woman_practice_setting2$n), prop=c(man_practice_setting2$prop, woman_practice_setting2$prop), gender=rep(c("man", "women"), each=4))


side_by_side_barplot2(practice_setting_combine, title="practice setting", legend_rows = 2)
```


```{r, message=F, warning=F, eval=T}
white_practice_setting=dentist_in_WI_of_interest1 %>% filter(`Describe Your Race or Ethnicity`=="White") %>% dplyr::count(`Best Describes This Practice Setting`)
settings=c("Group office practice (any number of dentists >1)", "Solo office practice")
nums=sapply(settings, function(x) white_practice_setting %>% filter(`Best Describes This Practice Setting`==x) %>% select(n) %>%  pull())
nums[4]=white_practice_setting$n[is.na(white_practice_setting$`Best Describes This Practice Setting`)]
nums[3]=sum(white_practice_setting$n)-sum(nums[1:2])-nums[4]
white_practice_setting2=data.frame(class=c(settings, "others", "NA"), n=nums) %>% mutate(prop=round(n/sum(nums),4))

asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries
asia_practice_setting=dentist_in_WI_of_interest1 %>% filter(`Describe Your Race or Ethnicity`%in% asia) %>% dplyr::count(`Best Describes This Practice Setting`)
nums=sapply(settings, function(x) asia_practice_setting %>% filter(`Best Describes This Practice Setting`==x) %>% select(n) %>%  pull())
nums[4]=asia_practice_setting$n[is.na(asia_practice_setting$`Best Describes This Practice Setting`)]
nums[3]=sum(asia_practice_setting$n)-sum(nums[1:2])-nums[4]
asia_practice_setting2=data.frame(class=c(settings, "others", "NA"), n=nums) %>% mutate(prop=round(n/sum(nums),4))

practice_setting_combine=data.frame(class=rep(c(settings, "others", "NA"), 2), n=c(white_practice_setting2$n, asia_practice_setting2$n), prop=c(white_practice_setting2$prop, asia_practice_setting2$prop), gender=rep(c("White", "Asia"), each=4))


side_by_side_barplot2(practice_setting_combine, title="practice setting", legend_rows = 2)
```




## group office practice 





```{r, message=F, warning=F, eval=F}
group_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Group office practice (any number of dentists >1)") 

group_practice2=group_practice%>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(group_practice),4))

fig=plot_function(title="Group office practice (any number of dentists >1)", group_practice2,1, var_name="Gender Identity", num_size=4, legend_text_size = 13)
fig

group_practice2%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(group_practice2$n)
```



```{r, message=F, warning=F, eval=T}
group_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Group office practice (any number of dentists >1)") 

group_practice2=group_practice%>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(group_practice),4))

threshold=10
group_practice3=group_practice2 %>% filter(n>threshold)  %>% add_row(`Describe Your Race or Ethnicity`="other", n=group_practice2 %>% filter(n<=threshold) %>% select(n) %>% sum(), prop=group_practice2 %>% filter(n<=threshold) %>% select(prop) %>% sum()) # aggregate categories with n<=threshold 


fig=plot_function(title="Group office practice (any number of dentists >1)", group_practice3,2, var_name="Describe Your Race or Ethnicity", num_size = 4)
fig

group_practice3%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(group_practice3$n)
```




```{r, message=F, warning=F, eval=T}
group_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Group office practice (any number of dentists >1)") 

group_practice2=group_practice%>% dplyr::count(`Dental Specialties Board Certified`) %>% mutate(prop=round(n/nrow(group_practice),4))

threshold=10
group_practice3=group_practice2 %>% filter(n>threshold)  %>% add_row(`Dental Specialties Board Certified`="other", n=group_practice2 %>% filter(n<=threshold) %>% select(n) %>% sum(), prop=group_practice2 %>% filter(n<=threshold) %>% select(prop) %>% sum()) # aggregate categories with n<=threshold 


fig=plot_function(title="Group office practice (any number of dentists >1)", group_practice3,2, var_name="Dental Specialties Board Certified", num_size = 4)
fig

group_practice3%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(group_practice3$n)
```




## solo office practice 



```{r, message=F, warning=F, eval=T}
solo_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Solo office practice") 

solo_practice2=solo_practice%>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(solo_practice),4))

fig=plot_function(title="Solo office practice", solo_practice2,1, var_name="Gender Identity", num_size = 4, legend_text_size = 13)
fig

solo_practice2%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(solo_practice2$n)
```



```{r, message=F, warning=F, eval=T}
solo_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Solo office practice") 

solo_practice2=solo_practice%>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(solo_practice),4))
threshold=10
solo_practice3=solo_practice2 %>% filter(n>threshold)  %>% add_row(`Describe Your Race or Ethnicity`="other", n=solo_practice2 %>% filter(n<=threshold) %>% select(n) %>% sum(), prop=solo_practice2 %>% filter(n<=threshold) %>% select(prop) %>% sum()) # aggregate categories with n<=threshold 


fig=plot_function(title="Solo office practice", solo_practice3,2, var_name="Describe Your Race or Ethnicity", num_size = 4)
fig

solo_practice3%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(solo_practice3$n)
```


```{r, message=F, warning=F, eval=T}
solo_practice=dentist_in_WI_of_interest1 %>% dplyr::filter(`Best Describes This Practice Setting`=="Solo office practice") 

solo_practice2=solo_practice%>% dplyr::count(`Dental Specialties Board Certified`) %>% mutate(prop=round(n/nrow(solo_practice),4))
threshold=10
solo_practice3=solo_practice2 %>% filter(n>threshold)  %>% add_row(`Dental Specialties Board Certified`="other", n=solo_practice2 %>% filter(n<=threshold) %>% select(n) %>% sum(), prop=solo_practice2 %>% filter(n<=threshold) %>% select(prop) %>% sum()) # aggregate categories with n<=threshold 


fig=plot_function(title="Solo office practice", solo_practice3,1, var_name="Dental Specialties Board Certified", num_size = 4, legend_text_size = 12)
fig

solo_practice3%>% arrange(desc(n))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(solo_practice3$n)
```




## geographical distribution 

```{r, message=F, warning=F, results=F}
wisconsin_urban_rural_zip=multiplesheets("C:\\Shengtong\\Research\\OralPublicHealth\\Dental_Emergency_visit\\Wisconsin-Urban-Rural-zip.xlsx")
```


* [Wisconsin state urban rural code](https://marq-my.sharepoint.com/:x:/g/personal/shengtong_han_marquette_edu/ETU5WgJJl9BIoNsBBNhPqocBR3DcuAN3q1H65LThX3eeuQ?e=Ozruo2)



```{r, message=F, warning=F}
region_code=unique(wisconsin_urban_rural_zip$`Table 1`$`2014 ZCTA-based WURC Code`)
all_code=wisconsin_urban_rural_zip$`Table 1`$`2014 ZCTA-based WURC Code`
all_code[which(all_code=="R2/R1")]="R2"   # rename regions 
all_code[which(all_code=="Urban/R1")]="Urban"
all_code[which(all_code=="Metro W-O-W/R1")]="Metro W-O-W"
all_code[which(all_code=="R3/R1")]="R3"
all_code[which(all_code=="R3/R2/R1")]="R3"
all_code[which(all_code=="Urban/R2")]="Urban"
all_code[which(all_code=="R1/Urban")]="R1"
wisconsin_urban_rural_zip_data=wisconsin_urban_rural_zip$`Table 1` %>% mutate(new_region_code=all_code)
region_code_update=unique(all_code)
```


```{r, message=F, warning=F, eval=T}
region_code_zip=sapply(region_code_update, function(x) wisconsin_urban_rural_zip_data %>% filter(new_region_code==x) %>% select(`ZCTA/\r\nZIPCode`)) # extract zip codes 


#zip_in_hygie_only=setdiff(hygienist_zip, unlist(region_code_zip)) #### zip codes in the survey, but not in wisconsin urban rural zip data 
# Dental_Hygienist$`Dental H` %>% filter(`5-digit Zip code` %in% zip_in_hygie_only)%>% filter(`Gender Identity`=="Man" | `Gender Identity`=="Woman") %>% nrow() these man/woman in the survey, but missed in wisconsin urban/rural data 


dentist_zip=unique(dentist_in_WI_of_interest1 %>% select(`5-digit Zip code` ) %>% pull)
#sum(is.na(Dentist_Survey_zipcode)==T) 893 zip codes are missing 


zip_in_dentist_only=setdiff(dentist_zip, unlist(region_code_zip)) #### zip codes in the survey, but not in Wisconsin urban rural zip data 
dentist_in_WI_of_interest1 %>% filter(`5-digit Zip code` %in% zip_in_dentist_only)%>% filter(`Gender Identity`=="Man" | `Gender Identity`=="Woman") %>% nrow() # these 886 man/woman in the survey, but missed in wisconsin urban/rural data

data.frame(zip_in_dentist_only)%>%
datatable(extensions = 'Buttons',
          caption = " Zip codes in the survey, but not in Wisconsin zip code list",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



* among  77 zip codes missing, i.e. not in Wisconsin zip code list,  some code (46/77=59.7%) have sub-code like `53574-8881`, but Wisconsin zip code don't have sub-code.  




```{r, message=F, warning=F, eval=T}
region_code_zip=sapply(region_code_update, function(x) wisconsin_urban_rural_zip_data %>% filter(new_region_code==x) %>% select(`ZCTA/\r\nZIPCode`)) # extract zip codes 


#zip_in_hygie_only=setdiff(hygienist_zip, unlist(region_code_zip)) #### zip codes in the survey, but not in wisconsin urban rural zip data 
# Dental_Hygienist$`Dental H` %>% filter(`5-digit Zip code` %in% zip_in_hygie_only)%>% filter(`Gender Identity`=="Man" | `Gender Identity`=="Woman") %>% nrow() these man/woman in the survey, but missed in wisconsin urban/rural data 


dentist_zip_raw=unique(dentist_in_WI_of_interest1 %>% select(`5-digit Zip code` ) %>% pull)
dentist_zip=str_sub(dentist_zip_raw, 1, 5)

zip_in_dentist_only=setdiff(dentist_zip, unlist(region_code_zip)) #### zip codes in the survey, but not in Wisconsin urban rural zip data 
Dentist_Survey_zipcode=dentist_in_WI_of_interest1 %>% select(`5-digit Zip code`) %>% pull()


dentist_in_WI_of_interest1 %>% filter(`5-digit Zip code` %in% zip_in_dentist_only)%>% filter(`Gender Identity`=="Man" | `Gender Identity`=="Woman") %>% nrow() # these 886 man/woman in the survey, but missed in wisconsin urban/rural data

data.frame(zip_in_dentist_only)%>%
datatable(extensions = 'Buttons',
          caption = " Zip codes in the survey, but not in Wisconsin zip code list",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))



dentist_zip_in_dentist_only=sapply(zip_in_dentist_only, function(x) Dentist_Survey$`Dentist Survey` %>% filter(`5-digit Zip code` %in% x)%>% filter(`Gender Identity`=="Man" | `Gender Identity`=="Woman") %>% nrow())

```



### Gender Identity


```{r, echo=F, message=F, warning=F}
side_by_side_barplot=function(data, angle=0, num_size=3, x_text_size=10, legend_text_size=10, title)
{
  y_limit=max(data$num)*1.1
  g=ggplot(data, aes(x=geo, y=num, fill=gender)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, y_limit))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom", legend.text = element_text(size=legend_text_size))+
  theme(axis.text.x = element_text(angle = angle, vjust = 0.5, size=x_text_size))+
  #geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=num_size)+  # add numbers over bars
  geom_text(label = with(gender_geo_data, paste(num, paste0('(', prop*100, "%", ')'))), position=position_dodge(width=0.9), vjust=-1, size=num_size)+
  ggtitle(title)+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
 return(g)
  
}
```








```{r, message=F, warning=F, eval=T}
gender_geo=sapply(region_code_zip, function(x) dentist_in_WI_of_interest1 %>% filter(`5-digit Zip code` %in% x) %>% select(`Gender Identity`))
gender_prop=sapply(gender_geo, function(x) c(sum(x=="Man", na.rm=T), sum(x=="Woman", na.rm=T))) 
gender_geo_data=data.frame(geo=rep(region_code_update,each=2), num=as.vector(gender_prop), gender=rep(c("Man", "Woman"), length(region_code_update))) %>% drop_na()


man_total=sum(gender_geo_data %>% filter(gender=="Man") %>% select(num) %>% pull())
woman_total=sum(gender_geo_data %>% filter(gender=="Woman") %>% select(num) %>% pull())
prop=numeric()
prop[seq(1,11,by=2)]=gender_geo_data$num[seq(1,11,by=2)]/man_total
prop[seq(2,12,by=2)]=gender_geo_data$num[seq(2,12,by=2)]/woman_total
gender_geo_data=gender_geo_data %>% mutate(prop=round(prop,4))

fig=side_by_side_barplot(gender_geo_data, angle=30, num_size = 2.5, x_text_size=12, legend_text_size=12, title="Dentist_Survey")
fig


gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "Dentist",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(gender_geo_data$num)
```



### specialty distribution 





```{r, message=F, warning=F, eval=T}
specialty=c("General dentistry", "Endodontics", "Orthodontics","Periodontics",  "Prosthodontics", "Pediatric dentistry", "Oral surgery")
specialty_geo=sapply(region_code_zip, function(x) dentist_in_WI_of_interest1 %>% filter(`5-digit Zip code` %in% x) %>% filter(`Dental Specialties Board Certified` %in% specialty) %>% select(`Dental Specialties Board Certified`))
specialty_prop=sapply(specialty_geo, function(x) c(sum(x=="General dentistry"), sum(x=="Endodontics"), sum(x=="Orthodontics"), sum(x=="Periodontics"), sum(x=="Prosthodontics"), sum(x=="Pediatric dentistry"), sum(x=="Oral surgery"))) 
specialty_geo_data=data.frame(geo=rep(region_code_update,each=length(specialty)), num=as.vector(specialty_prop), spect=rep(specialty, length(region_code_update))) %>% drop_na()

figures=list()
pie_chart=list()
for (i in 1:length(region_code_update))
  
{
   figures[[i]]=ggplot(specialty_geo_data %>% filter(geo %in% region_code_update[i]), aes(x=spect, y=num, fill=spect)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, max(specialty_geo_data %>% filter(geo %in% region_code_update[i]) %>% select(num)%>% pull())+10))+
 # facet_grid("geo")+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle(region_code_update[i])+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
  
  pie_data=specialty_geo_data %>% filter(geo %in% region_code_update[i])
  pie_data <- pie_data %>% 
  mutate(per=`num`/sum(`num`)) %>% 
  arrange(desc(spect))
pie_data$label <- scales::percent(pie_data$per)
pie_chart[[i]]=ggplot(data=pie_data)+
  geom_bar(aes(x="", y=per, fill=spect), stat="identity", width = 1)+
  coord_polar("y", start=0)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(per) - per/2, label=label))
   
   
}
  
ggarrange(figures[[1]], figures[[2]], figures[[3]], figures[[4]], figures[[5]], figures[[6]], ncol=2)






gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
sum(gender_geo_data$num)
```

