---
title: "07/31/2024"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---



```{r, echo=F, message=F, warning=F, results=F}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
changeCellColor <- function(row, col){
  c(
    "function(row, data, num, index){",
    sprintf("  if(index == %d){", row-1),
    sprintf("    $('td:eq(' + %d + ')', row)", col),
    "    .css({'background-color': 'orange'});",
    "  }",
    "}"  
  )
}
```




```{r, echo=F, message=F, warning=F, results=F}
Dental_Hygienist=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\state_survey\\Dental Hygienist.xlsx")
Dentist_Survey=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\state_survey\\Dentist Survey.xlsx")
```


## Dental_Hygienist

```{r, message=F, warning=F}
dim(Dental_Hygienist$`Dental H`)
variables=colnames(Dental_Hygienist$`Dental H`)
variables
```

### Race or Ethnicity

```{r, message=F, warning=F}
race=Dental_Hygienist$`Dental H` %>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(Dental_Hygienist$`Dental H`),4))
south_east_asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries 
south_east_asia_race= race %>% filter(`Describe Your Race or Ethnicity` %in% south_east_asia)
race_new=race %>% filter(`Describe Your Race or Ethnicity` %in% south_east_asia==F) %>% add_row(`Describe Your Race or Ethnicity`="south east asia", n=south_east_asia_race %>% select(n) %>% sum(), prop=south_east_asia_race %>% select(prop) %>% sum()) # combine south east asia countries into one unit 


ggplot(race_new, aes(x=`Describe Your Race or Ethnicity`, y=n, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(race_new, aes(x=`Describe Your Race or Ethnicity`, y=prop, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


race_new%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* `south east asia` includes "East Asian", "Filipino", "Hmong", "Laotian", "South Asian"



### Gender Identity

```{r, message=F, warning=F}
gender=Dental_Hygienist$`Dental H` %>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(Dental_Hygienist$`Dental H`),4))

ggplot(gender, aes(x=`Gender Identity`, y=n, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



## Dentist Survey

```{r, message=F, warning=F}
dim(Dentist_Survey$`Dentist Survey`)
variables=colnames(Dentist_Survey$`Dentist Survey`)
variables
```



### Race or Ethnicity

```{r, message=F, warning=F}
race=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))
south_east_asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries 
south_east_asia_race= race %>% filter(`Describe Your Race or Ethnicity` %in% south_east_asia)
race_new=race %>% filter(`Describe Your Race or Ethnicity` %in% south_east_asia==F) %>% add_row(`Describe Your Race or Ethnicity`="south east asia", n=south_east_asia_race %>% select(n) %>% sum(), prop=south_east_asia_race %>% select(prop) %>% sum()) # combine south east asia countries into one unit 

race_new2=race_new %>% filter(n>10)  %>% add_row(`Describe Your Race or Ethnicity`="other", n=race_new %>% filter(n<=10) %>% select(n) %>% sum(), prop=race_new %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 

ggplot(race_new2, aes(x=`Describe Your Race or Ethnicity`, y=n, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new2$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(race_new2, aes(x=`Describe Your Race or Ethnicity`, y=prop, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new2$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


race_new2%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* `south east asia` includes "East Asian", "Filipino", "Hmong", "Laotian", "South Asian"

* `other` aggregates categories with less than 10 responses. 



### Gender Identity

```{r, message=F, warning=F}
gender=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))

ggplot(gender, aes(x=`Gender Identity`, y=n, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




### Dental Specialties Board Certified


```{r, message=F, warning=F}
specialty=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Dental Specialties Board Certified`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))

specialty2=specialty %>% filter(n>10)  %>% add_row(`Dental Specialties Board Certified`="other", n=specialty %>% filter(n<=10) %>% select(n) %>% sum(), prop=specialty %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 



ggplot(specialty2, aes(x=`Dental Specialties Board Certified`, y=n, fill=`Dental Specialties Board Certified`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=specialty2$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(specialty2, aes(x=`Dental Specialties Board Certified`, y=prop, fill=`Dental Specialties Board Certified`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=specialty2$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


specialty2%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


* `other` aggregates categories with less than 10 responses, such as `General dentistry; Oral surgery`





## geographical distribution 

```{r, message=F, warning=F, results=F}
wisconsin_urban_rural_zip=multiplesheets("C:\\Shengtong\\Research\\OralPublicHealth\\Dental_Emergency_visit\\Wisconsin-Urban-Rural-zip.xlsx")
```


```{r, message=F, warning=F}
region_code=unique(wisconsin_urban_rural_zip$`Table 1`$`2014 ZCTA-based WURC Code`)
```


```{r, message=F, warning=F}
region_code_zip=sapply(region_code, function(x) wisconsin_urban_rural_zip$`Table 1` %>% filter(`2014 ZCTA-based WURC Code`==x) %>% select(`ZCTA/\r\nZIPCode`))

```

### Gender Identity

```{r, message=F, warning=F}
gender_geo=sapply(region_code_zip, function(x) Dental_Hygienist$`Dental H` %>% filter(`5-digit Zip code` %in% x) %>% select(`Gender Identity`))
gender_prop=sapply(gender_geo, function(x) c(sum(x=="Man"), sum(x=="Woman"))) 
gender_geo_data=data.frame(geo=rep(region_code,each=2), num=as.vector(gender_prop), gender=rep(c("Man", "Woman"), length(region_code))) %>% drop_na()


ggplot(gender_geo_data, aes(x=geo, y=num, fill=gender)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

#ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
#  ylab("%")+xlab("")+
#  theme(legend.position="")+
#  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
#  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
#  ggtitle("Hygienist ")+
#  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
* only keep `Man` and `Woman` and ignore other reponses 




```{r, message=F, warning=F}
gender_geo=sapply(region_code_zip, function(x) Dentist_Survey$`Dentist Survey` %>% filter(`5-digit Zip code` %in% x) %>% select(`Gender Identity`))
gender_prop=sapply(gender_geo, function(x) c(sum(x=="Man"), sum(x=="Woman"))) 
gender_geo_data=data.frame(geo=rep(region_code,each=2), num=as.vector(gender_prop), gender=rep(c("Man", "Woman"), length(region_code))) %>% drop_na()


ggplot(gender_geo_data, aes(x=geo, y=num, fill=gender)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist_Survey")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

#ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
#  ylab("%")+xlab("")+
#  theme(legend.position="")+
#  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
#  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
#  ggtitle("Hygienist ")+
#  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### specialty distribution 


```{r, message=F, warning=F}
specialty=c("General dentistry", "Endodontics", "Orthodontics", "Periodontics", "Prosthodontics", "Pediatric dentistry", "Oral surgery")
specialty_geo=sapply(region_code_zip, function(x) Dentist_Survey$`Dentist Survey` %>% filter(`5-digit Zip code` %in% x) %>% filter(`Dental Specialties Board Certified` %in% specialty) %>% select(`Dental Specialties Board Certified`))
specialty_prop=sapply(specialty_geo, function(x) c(sum(x=="General dentistry"), sum(x=="Endodontics"), sum(x=="Orthodontics"), sum(x=="Periodontics"), sum(x=="Prosthodontics"), sum(x=="Pediatric dentistry"), sum(x=="Oral surgery"))) 
specialty_geo_data=data.frame(geo=rep(region_code,each=length(specialty)), num=as.vector(specialty_prop), spect=rep(specialty, length(region_code))) %>% drop_na()


ggplot(specialty_geo_data, aes(x=geo, y=num, fill=spect)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist_Survey")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

#ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
#  ylab("%")+xlab("")+
#  theme(legend.position="")+
#  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
#  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
#  ggtitle("Hygienist ")+
#  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```