---
title: "Coronal movement"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2025-10-07"
---



```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()
```


```{r, message=F, warning=F, results=F}
#data_raw=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202410\\Neal\\CBCT Thesis data FINAL VK011525.xlsx")
coronal_movement=as_tibble(read.csv(file.path(root,"..\\2024\\202410\\Neal\\6 FINAL CBCT Thesis data (09-11-25)_Coronal_Movement.csv")))

#finalized_with_omitted_data=data_raw$`Finalized with Omitted data`
#coding=data_raw$`Coding`
#save(finalized_with_omitted_data, finalized_data, coding, file="C:\\Shengtong\\Research\\AllCollaboration\\2024\\202410\\Neal\\data.RData")
#load("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202410\\Neal\\data.RData")


#colnames(finalized_data)
```



## home 

[Home](2024_1002_Neal.html)





```{r, message=F, warning=F}
both_tooth_yes=coronal_movement %>% filter(`Coronal_Movement_both_Teeth..y.n.`=="Y") %>% nrow()
both_tooth_all=coronal_movement %>% filter(`Coronal_Movement_both_Teeth..y.n.`=="Y" | `Coronal_Movement_both_Teeth..y.n.`=="N") %>% nrow()

both_tooth_yes/both_tooth_all

m_tooth_yes=coronal_movement %>% filter(M_Tooth_Coronal_Migration=="Y") %>% nrow()
m_tooth_all=coronal_movement %>% filter(M_Tooth_Coronal_Migration=="Y" | M_Tooth_Coronal_Migration=="N") %>% nrow()

m_tooth_yes/m_tooth_all

d_tooth_yes=coronal_movement %>% filter(D_Tooth_Coronal_Migration=="Y") %>% nrow()
d_tooth_all=coronal_movement %>% filter(D_Tooth_Coronal_Migration=="Y" | D_Tooth_Coronal_Migration=="N") %>% nrow()

d_tooth_yes/d_tooth_all

```



* frequency: ` coronal_movement_both_teeth`: 3.17%; `M_tooth_coronal_migration`: 1.98%; `D_tooth_coronal_migration`: 1.59%. 





```{r, message=F, warning=F}
prop.test(x=c(both_tooth_yes, m_tooth_yes), n=c(both_tooth_all, m_tooth_all))

prop.test(x=c(both_tooth_yes, d_tooth_yes), n=c(both_tooth_all, d_tooth_all))

prop.test(x=c(m_tooth_yes, d_tooth_yes), n=c(m_tooth_all, d_tooth_all))
```






* `coronal_movement_both_teeth`  vs `M_tooth_coronal_migration`: p value 0.5741; 

* `coronal_movement_both_teeth`  vs `D_tooth_coronal_migration`: p value 0.3807;

* `M_tooth_coronal_migration`  vs `D_tooth_coronal_migration`: p value 1.000;


* in summary, all three are not different from one another. 

* two sample proportion test was used 