---
title: "07/31/2024"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
---



```{r, echo=F, message=F, warning=F, results=F}
source("C:/Shengtong/Research/AllCollaboration/Collaborations/analysis/Rfunctions.R")
changeCellColor <- function(row, col){
  c(
    "function(row, data, num, index){",
    sprintf("  if(index == %d){", row-1),
    sprintf("    $('td:eq(' + %d + ')', row)", col),
    "    .css({'background-color': 'orange'});",
    "  }",
    "}"  
  )
}
```




```{r, echo=F, message=F, warning=F, results=F}
Dental_Hygienist=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\state_survey\\Dental Hygienist.xlsx")
Dentist_Survey=multiplesheets("C:\\Shengtong\\Research\\AllCollaboration\\2024\\202407\\state_survey\\Dentist Survey.xlsx")
```


## Dental_Hygienist

```{r, message=F, warning=F}
#dim(Dental_Hygienist$`Dental H`)
variables=colnames(Dental_Hygienist$`Dental H`)
data.frame(questions=variables)%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* in total 3991 responses and 46 questions 




### Race or Ethnicity

```{r, message=F, warning=F}
race=Dental_Hygienist$`Dental H` %>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(Dental_Hygienist$`Dental H`),4))
asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries 
asia_race= race %>% filter(`Describe Your Race or Ethnicity` %in% asia)
race_new=race %>% filter(`Describe Your Race or Ethnicity` %in% asia==F) %>% add_row(`Describe Your Race or Ethnicity`="asia", n=asia_race %>% select(n) %>% sum(), prop=asia_race %>% select(prop) %>% sum()) # combine south east asia countries into one unit 


ggplot(race_new, aes(x=`Describe Your Race or Ethnicity`, y=n, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(race_new, aes(x=`Describe Your Race or Ethnicity`, y=prop, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


race_new%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* `asia` includes "East Asian", "Filipino", "Hmong", "Laotian", "South Asian"



### Gender Identity

```{r, message=F, warning=F}
gender=Dental_Hygienist$`Dental H` %>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(Dental_Hygienist$`Dental H`),4))

ggplot(gender, aes(x=`Gender Identity`, y=n, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



## Dentist Survey

```{r, message=F, warning=F}
#dim(Dentist_Survey$`Dentist Survey`)
variables=colnames(Dentist_Survey$`Dentist Survey`)
data.frame(questions=variables)%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* in total 2957 responses and 40 questions 


### Race or Ethnicity

```{r, message=F, warning=F}
race=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Describe Your Race or Ethnicity`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))
asia=c("East Asian", "Filipino", "Hmong", "Laotian", "South Asian") # define south east asia countries 
asia_race= race %>% filter(`Describe Your Race or Ethnicity` %in% asia)
race_new=race %>% filter(`Describe Your Race or Ethnicity` %in% asia==F) %>% add_row(`Describe Your Race or Ethnicity`="asia", n=asia_race %>% select(n) %>% sum(), prop=asia_race %>% select(prop) %>% sum()) # combine south east asia countries into one unit 

race_new2=race_new %>% filter(n>10)  %>% add_row(`Describe Your Race or Ethnicity`="other", n=race_new %>% filter(n<=10) %>% select(n) %>% sum(), prop=race_new %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 

ggplot(race_new2, aes(x=`Describe Your Race or Ethnicity`, y=n, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new2$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(race_new2, aes(x=`Describe Your Race or Ethnicity`, y=prop, fill=`Describe Your Race or Ethnicity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=8))+
  geom_text(aes(label=race_new2$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


race_new2%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

* `asia` includes "East Asian", "Filipino", "Hmong", "Laotian", "South Asian"

* `other` aggregates categories with less than 10 responses. 



### Gender Identity

```{r, message=F, warning=F}
gender=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Gender Identity`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))

ggplot(gender, aes(x=`Gender Identity`, y=n, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(gender, aes(x=`Gender Identity`, y=prop, fill=`Gender Identity`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=gender$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




### Dental Specialties Board Certified


```{r, message=F, warning=F}
specialty=Dentist_Survey$`Dentist Survey` %>% dplyr::count(`Dental Specialties Board Certified`) %>% mutate(prop=round(n/nrow(Dentist_Survey$`Dentist Survey`),4))

specialty2=specialty %>% filter(n>10)  %>% add_row(`Dental Specialties Board Certified`="other", n=specialty %>% filter(n<=10) %>% select(n) %>% sum(), prop=specialty %>% filter(n<=10) %>% select(prop) %>% sum()) # aggregate categories with n<=10 



ggplot(specialty2, aes(x=`Dental Specialties Board Certified`, y=n, fill=`Dental Specialties Board Certified`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=specialty2$n), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title

ggplot(specialty2, aes(x=`Dental Specialties Board Certified`, y=prop, fill=`Dental Specialties Board Certified`)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("%")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=13))+
  geom_text(aes(label=specialty2$prop*100), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


specialty2%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


* `other` aggregates categories with less than 10 responses, such as `General dentistry; Oral surgery`





## geographical distribution 

```{r, message=F, warning=F, results=F}
wisconsin_urban_rural_zip=multiplesheets("C:\\Shengtong\\Research\\OralPublicHealth\\Dental_Emergency_visit\\Wisconsin-Urban-Rural-zip.xlsx")
```


* [Wisconsin state urban rural code](https://marq-my.sharepoint.com/:x:/g/personal/shengtong_han_marquette_edu/ETU5WgJJl9BIoNsBBNhPqocBR3DcuAN3q1H65LThX3eeuQ?e=Ozruo2)



```{r, message=F, warning=F}
region_code=unique(wisconsin_urban_rural_zip$`Table 1`$`2014 ZCTA-based WURC Code`)
all_code=wisconsin_urban_rural_zip$`Table 1`$`2014 ZCTA-based WURC Code`
all_code[which(all_code=="R2/R1")]="R2"   # raname regions 
all_code[which(all_code=="Urban/R1")]="Urban"
all_code[which(all_code=="Metro W-O-W/R1")]="Metro W-O-W"
all_code[which(all_code=="R3/R1")]="R3"
all_code[which(all_code=="R3/R2/R1")]="R3"
all_code[which(all_code=="Urban/R2")]="Urban"
all_code[which(all_code=="R1/Urban")]="R1"
wisconsin_urban_rural_zip_data=wisconsin_urban_rural_zip$`Table 1` %>% mutate(new_region_code=all_code)
region_code_update=unique(all_code)
```


```{r, message=F, warning=F}
region_code_zip=sapply(region_code_update, function(x) wisconsin_urban_rural_zip_data %>% filter(new_region_code==x) %>% select(`ZCTA/\r\nZIPCode`)) # extract zip codes 

```

### Gender Identity

```{r, message=F, warning=F}
gender_geo=sapply(region_code_zip, function(x) Dental_Hygienist$`Dental H` %>% filter(`5-digit Zip code` %in% x) %>% select(`Gender Identity`))
gender_prop=sapply(gender_geo, function(x) c(sum(x=="Man", na.rm = T), sum(x=="Woman", na.rm = T))) 
gender_geo_data=data.frame(geo=rep(region_code_update,each=2), num=as.vector(gender_prop), gender=rep(c("Man", "Woman"), length(region_code_update))) %>% drop_na()


ggplot(gender_geo_data, aes(x=geo, y=num, fill=gender)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Hygienist ")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title



gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```
* only keep `Man` and `Woman` and ignore other responses 




```{r, message=F, warning=F}
gender_geo=sapply(region_code_zip, function(x) Dentist_Survey$`Dentist Survey` %>% filter(`5-digit Zip code` %in% x) %>% select(`Gender Identity`))
gender_prop=sapply(gender_geo, function(x) c(sum(x=="Man", na.rm=T), sum(x=="Woman", na.rm=T))) 
gender_geo_data=data.frame(geo=rep(region_code_update,each=2), num=as.vector(gender_prop), gender=rep(c("Man", "Woman"), length(region_code_update))) %>% drop_na()


ggplot(gender_geo_data, aes(x=geo, y=num, fill=gender)) +geom_bar(position = "dodge", stat="identity")+
 # ylim(c(0, 0.7))+
  ylab("n")+xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist_Survey")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title


gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### specialty distribution 


```{r, message=F, warning=F}
specialty=c("General dentistry", "Endodontics", "Orthodontics", "Periodontics", "Prosthodontics", "Pediatric dentistry", "Oral surgery")
specialty_geo=sapply(region_code_zip, function(x) Dentist_Survey$`Dentist Survey` %>% filter(`5-digit Zip code` %in% x) %>% filter(`Dental Specialties Board Certified` %in% specialty) %>% select(`Dental Specialties Board Certified`))
specialty_prop=sapply(specialty_geo, function(x) c(sum(x=="General dentistry"), sum(x=="Endodontics"), sum(x=="Orthodontics"), sum(x=="Periodontics"), sum(x=="Prosthodontics"), sum(x=="Pediatric dentistry"), sum(x=="Oral surgery"))) 
specialty_geo_data=data.frame(geo=rep(region_code_update,each=length(specialty)), num=as.vector(specialty_prop), spect=rep(specialty, length(region_code_update))) %>% drop_na()

figures=list()
for (i in 1:length(region_code_update))
  
{
   figures[[i]]=ggplot(specialty_geo_data %>% filter(geo %in% region_code_update[i]), aes(x=spect, y=num, fill=spect)) +geom_bar(position = "dodge", stat="identity")+
  ylim(c(0, max(specialty_geo_data %>% filter(geo %in% region_code_update[i]) %>% select(num)%>% pull())+10))+
  facet_grid("geo")+
  ylab("n")+xlab("")+
  theme(legend.position="")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size=10))+
  geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25, size=3)+  # add numbers over bars
  ggtitle("Dentist_Survey")+
  theme(plot.title = element_text(hjust = 0.5, size=15))  #center the title
  
  
}
  
ggarrange(figures[[1]], figures[[2]], figures[[3]], figures[[4]], figures[[5]], figures[[6]], ncol=2)




gender_geo_data%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```