---
title: "04/25 2025"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2025-04-25"
---




```{r, echo=F, message=F, warning=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()
```




```{r, message=F, warning=F, results=F}
SDF=multiplesheets((file.path(root, "..\\2025\\202504\\Matina\\SDF.xlsx")))
SDF_data=SDF$Sheet1



# Define the follow-up columns
followup_cols <- c("3m", "6m", "9m", "12m", "15m", "18m", "24m")

# Define success values
success_vals <- c(1, NA, 4)

# Function to calculate survival time
get_survival_time <- function(row) {
  months <- c(3, 6, 9, 12, 15, 18, 24)
  values <- as.numeric(row[c("3m", "6m", "9m", "12m", "15m", "18m", "24m")])
  
  # Loop through each time point and find when the first failure occurs
  for (i in seq_along(values)) {
    if (!is.na(values[i]) && !(values[i] %in% success_vals)) {
      return(months[i - 1 ])  # Return survival time just before failure
    }
  }

  # If no failure found, return the last time point with a non-NA value
  last_success_index <- max(which(is.na(values) | values %in% success_vals), na.rm = TRUE)
  return(months[last_success_index])
}

# Apply function row-wise
SDF_data$Time <- apply(SDF_data, 1, get_survival_time)

SDF_data


```



## overall success rate 

```{r, message=F, warning=F}
# Define values considered immediate successes
success_vals <- c(1, 4)

# Time point columns
time_points <- c("3m", "6m", "9m", "12m", "15m", "18m", "24m")

# Function to compute per-row success with correct rule
check_success_corrected <- function(values) {
  status <- logical(length(values))
  had_success <- FALSE
  failed <- FALSE
  
  for (i in seq_along(values)) {
    val <- values[i]
    
    if (failed) {
      status[i] <- FALSE  # All after a failure are failures
    } else if (!is.na(val) && val %in% success_vals) {
      status[i] <- TRUE
      had_success <- TRUE
    } else if (is.na(val) && had_success) {
      status[i] <- TRUE
    } else {
      status[i] <- FALSE
      failed <- TRUE
    }
  }
  
  return(status)
}

# Apply to each row in the dataset
success_matrix <- t(apply(SDF_data[, time_points], 1, check_success_corrected))

# Calculate survival rate: proportion of successes at each time point
survival_rate <- colSums(success_matrix, na.rm = TRUE) / nrow(SDF_data)

# Create survival rate data frame
survival_df <- data.frame(
  Time = time_points,
  SurvivalRate = round(survival_rate, 3)
)

survival_df%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




```{r, message=F, warning=F}
# Ensure 'Time' is treated as a factor with the correct order
survival_df$Time <- factor(survival_df$Time, levels = c("3m", "6m", "9m", "12m", "15m", "18m", "24m"))

# Convert rate to percent
survival_df$SurvivalPercent <- survival_df$SurvivalRate * 100

# Plot with distinct colors for each bar
ggplot(survival_df, aes(x = Time, y = SurvivalPercent, fill = Time)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(SurvivalPercent, 1), "%")),
            vjust = -0.5, size = 4) +
  scale_fill_brewer(palette = "Set3") +  # Nice, distinguishable colors
  labs(title = "",
       x = "Time Point",
       y = "Survival Rate (%)") +
  ylim(0,110)+
  #theme_minimal() +
  theme(legend.position = "none")  # Remove legend since colors match x-axis

```




```{r, message=F, warning=F}
# Load required libraries
library(survival)
library(survminer)

# Create event indicator: 1 for success, 0 otherwise
SDF_data$Event <- ifelse(SDF_data$outcome == 1, 0, 1)

# Create a Surv object (time and event)
surv_obj <- Surv(time = SDF_data$Time, event = SDF_data$Event)

# Fit Kaplan-Meier model using the data argument
km_fit <- survfit(surv_obj ~ 1, data = SDF_data)



ggsurvplot(
  km_fit,
  data = SDF_data,
  conf.int = TRUE,
  risk.table = TRUE,
  xlab = "Time (months)",
  ylab = "Success Probability",
  title = "Kaplan-Meier Curve of Treatment Success",
  palette = "red",
  break.time.by = 3,                            # Tick marks at 0, 3, 6, ..., 24
  xlim = c(0, 24),                              # Include 0-month baseline
  risk.table.breaks = seq(0, 24, 3),            # Risk table also starts from 0
  risk.table.y.text.col = TRUE,
  risk.table.height = 0.25
)
```

* for outcome, treat `1` as success and failure otherwise, but in survival data, that's the opposite,  `1` denotes failure and `0` no failure 



## survival by tooth types 

```{r, message=F, warning=F}
SDF_data_tooth_type=SDF_data %>%
  mutate(
    Tooth_Type = case_when(
      Tooth %in% c(51, 52, 61, 62, 73)        ~ "anterior",
      Tooth %in% c(74, 84)                    ~ "lower 1st molar",
      Tooth %in% c(75, 85)                    ~ "lower 2nd molar",
      Tooth %in% c(64, 54)                    ~ "upper 1st molar",
      Tooth %in% c(65, 55)                    ~ "upper 2nd molar",
      TRUE                                    ~ "other"
    )
  )
table(SDF_data_tooth_type$Tooth_Type)
```


```{r, message=F, warning=F}
# Step 1: Create the survival object
surv_obj <- Surv(time = SDF_data_tooth_type$Time, event = SDF_data_tooth_type$Event)

# Step 2: Fit the survival curves by Tooth_Type
fit <- survfit(surv_obj ~ Tooth_Type, data = SDF_data_tooth_type)

# Step 3: Plot with smaller font size in risk table
ggsurvplot(fit, data = SDF_data_tooth_type,
           pval = TRUE,
           risk.table = TRUE,
           risk.table.fontsize = 2,  # <-- adjust this number (default is ~4.5)
           legend.title = "Tooth Type",
           legend.labs = levels(factor(SDF_data_tooth_type$Tooth_Type)),
           xlab = "Time (months)",
           ylab = "Survival probability",
           ggtheme = theme_minimal())
```
* p value of 0.0054 indicates significant difference across tooth types 


### cox proportional hazard models 

```{r, message=F, warning=F}
cox_model <- coxph(Surv(Time, Event) ~ Tooth_Type, data = SDF_data_tooth_type)
summary(cox_model)
```
*  All molar types have significantly longer survival than anterior teeth. The hazard of failure is much lower for molars.

* Hazard Ratios (`exp(coef)`) < 1 mean better survival

* `Score (logrank) test = 12.5  on 4 df,   p=0.01` survival curves differ significantly across teeth types. 

*  Compared to anterior teeth, all molar types (lower 1st, lower 2nd, upper 1st, upper 2nd) show significantly better survival, with hazard ratios ranging from 0.22 to 0.35. This means molars have a 65–78% lower risk of failure over time compared to anterior teeth. 


## full model, including all covariates 


```{r, message=F, warning=F}
coxph(Surv(Time, Event) ~ Tooth_Type + Age + Sex + SSC, data = SDF_data_tooth_type)
```


Interpretation of Coefficients

* Tooth_Type (Reference: anterior)

Compared to anterior teeth:

Lower 1st molar: HR = 0.093 (p < 0.001)
→ 91% lower hazard; significantly better survival.

Lower 2nd molar: HR = 0.101 (p < 0.001)
→ 90% lower hazard; significantly better survival.

Upper 1st molar: HR = 0.153 (p < 0.001)
→ 85% lower hazard; significantly better survival.

Upper 2nd molar: HR = 0.083 (p < 0.001)
→ 92% lower hazard; significantly better survival.

* Age: HR = 1.18 (p = 0.0015)
→ For every one-month increase in age, the hazard increases by 18%. Older patients tend to have worse survival.

* Sex: HR = 1.18 (p = 0.37)
→ Not statistically significant. There is no strong evidence that survival differs by sex.

* SSC (Reference: 0 = No SSC): HR = 1.72 (p = 0.039)
→ Teeth with SSC have a 72% higher hazard, indicating worse survival, and the result is statistically significant.

* Model Fit Statistics
Likelihood ratio test: p = 0.0039

Wald test: p = 0.0039

Number of observations: 159

Number of events: 119

The model fit is statistically significant, suggesting that at least one predictor is significantly associated with survival.