---
title: "03/05 2025"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2025-03-05"
---




```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()
```


```{r, message=F, warning=F, results=F}
MBSE_23=multiplesheets_without_headers((file.path(root, "../2025/202503/Zainab/23 Tablet grades seperated by exam 20250509.xlsx")))
MBSE_24=multiplesheets_without_headers((file.path(root, "..\\2025\\202503\\Zainab\\OT Research - 24 MBSE.xlsx")))
```

`
Probe only
23 Probe has 28 questions in one line

24 Probe has 4 lines per person 

Columns C - I
1st row for each person is 1 - 7
2nd row per person is 8 - 14
3rd row per person is 15 - 21
4th row per person is 22 - 28

Explorer, sickle, universal, area specific is set up as the 24 probe with 4 lines per person 
Cumulative was not evaluated the same and should not be considered in the analysis
`


```{r, message=F, warning=F}
side_by_side_bar_plot <- function(combined_data, variable = "probe") {
  # Reshape the data from wide to long format
  long_data <- combined_data %>%
    pivot_longer(
      cols = starts_with(paste0(variable, "_")),
      names_to = "var_name",
      values_to = "value"
    ) %>%
    filter(!is.na(value))

  # Create an ordered factor for correct x-axis ordering
  num_vars <- ncol(combined_data) - 1  # adjust if 'year' is always last
  long_data <- long_data %>%
    mutate(
      var_name = factor(var_name, levels = paste0(variable, "_", 1:num_vars))
    )

  # Summarize data
  summary_data <- long_data %>%
    group_by(year, var_name) %>%
    summarise(
      mean = mean(value, na.rm = TRUE),
      se = sd(value, na.rm = TRUE) / sqrt(n()),
      .groups = 'drop'
    )

  # Plot
  fig <- ggplot(summary_data, aes(x = var_name, y = mean, fill = factor(year))) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                  position = position_dodge(width = 0.9), width = 0.2) +
    labs(
      title = "",
      x = "",
      y = "Average score",
      fill = "Year"
    ) +
    theme(axis.text.x = element_text(angle = 60, vjust = 0.5))

  return(fig)
}

data_clean=function(data)
{
  student_names=unique(data$...1)
  data_clean <- data %>% filter(`...1` %in% student_names) %>%
  arrange(factor(`...1`, levels = student_names)) %>%
  select(3:9) %>%
  as.matrix() %>%
  t() %>%
  as.vector() %>%
  matrix(nrow = length(student_names), byrow = TRUE)  

  return(data_clean)
  
}

compute_pvalue=function(data1, data2, variable)
{
  pvalue=numeric(); pvalue2=numeric(); pvalue3=numeric()
for (i in 1:ncol(data1))
{
  if (sum(!is.na(data1[, i])) > 1 && sum(!is.na(data2[, i])) > 1) {
  pvalue[i]=t.test(data1[, i], data2[, i])$p.value
  pvalue2[i]=t.test(data1[, i], data2[, i], alternative ="less" )$p.value
  pvalue3[i]=t.test(data1[, i], data2[, i], alternative ="greater" )$p.value
} else {
  pvalue[i]="NA"
  pvalue2[i]="NA"
  pvalue3[i]="NA"
  
}
  
}
  output=data.frame(questions=paste(variable, seq(1:ncol(data_23_clean)), sep="_"), pvalue=pvalue_adjust(pvalue), pvalue2=pvalue_adjust(pvalue2), pvalue3=pvalue_adjust(pvalue3))
  return(output)
  
}

```








## probe 

```{r, message=F, warning=F}
data_23=MBSE_23$`23 Probe`
data_24=MBSE_24$`24 Probe`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
sum(num_rows==4)==length(num_rows)  # ensure all students have 4 rows 
```


```{r, message=F, warning=F}
data_23_clean=data_23[,5:32]
data_24_clean=data_clean(data_24)
compute_pvalue(data_23_clean, data_24_clean, "probe") %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




* two sample t test was used
* small `pvalue` indicates strong evidence of year 23 not equal year 24; small `pvalue2` suggests year 24 greater than year 23; small `pvalue3` suggests year 24 smaller than year 23.  


```{r, message=F, warning=F, eval=T}
parameter="probe"
data_23_clean=data.frame(data_23[,5:32])
data_24_clean=data.frame(data_clean(data_24))

# Step 1: Add group labels
data_23_clean$year <- "2023"
data_24_clean$year <- "2024"
colnames(data_23_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")
colnames(data_24_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")

# Step 2: Combine the datasets
combined_data <- bind_rows(data_23_clean, data_24_clean)
colnames(combined_data)[ncol(combined_data)]="year"

fig=side_by_side_bar_plot(combined_data, variable=parameter)
fig
```







## Explorer 

```{r, message=F, warning=F}
data_23=MBSE_23$`23 Explorer`
data_24=MBSE_24$`24 Explorer`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else which(num_rows != 4)

student_names_23=unique(data_23$...1)
num_rows=sapply(student_names_23, function(x) (data_23 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names_23[which(num_rows != 4)] # ensure all students have 4 rows 
  
```


```{r, message=F, warning=F, eval=T}
data_23_clean=data_clean(data_23) 
data_24_clean=data_clean(data_24) 

ncol(data_23_clean)==ncol(data_24_clean)

compute_pvalue(data_23_clean, data_24_clean, "Explorer") %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
  
 
```



```{r, message=F, warning=F, eval=T}
parameter="Explorer"
data_23_clean=data.frame(data_clean(data_23))
data_24_clean=data.frame(data_clean(data_24))

# Step 1: Add group labels
data_23_clean$year <- "2023"
data_24_clean$year <- "2024"
colnames(data_23_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")
colnames(data_24_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")

# Step 2: Combine the datasets
combined_data <- bind_rows(data_23_clean, data_24_clean)
colnames(combined_data)[ncol(combined_data)]="year"

fig=side_by_side_bar_plot(combined_data, variable=parameter)
fig
```











## Sickle 

```{r, message=F, warning=F}
data_23=MBSE_23$`23 Sickle`
data_24=MBSE_24$`24 Sickle`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names[which(num_rows != 4)] # ensure all students have 4 rows

student_names_23=unique(data_23$...1)
num_rows=sapply(student_names_23, function(x) (data_23 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names_23[which(num_rows != 4)] # ensure all students have 4 rows 
  
```


```{r, message=F, warning=F}
data_23_clean=data_clean(data_23) 
data_24_clean=data_clean(data_24) 

ncol(data_23_clean)==ncol(data_24_clean)

compute_pvalue(data_23_clean, data_24_clean, "Sickle") %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



```{r, message=F, warning=F, eval=T}
parameter="Sickler"
data_23_clean=data.frame(data_clean(data_23))
data_24_clean=data.frame(data_clean(data_24))

# Step 1: Add group labels
data_23_clean$year <- "2023"
data_24_clean$year <- "2024"
colnames(data_23_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")
colnames(data_24_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")

# Step 2: Combine the datasets
combined_data <- bind_rows(data_23_clean, data_24_clean)
colnames(combined_data)[ncol(combined_data)]="year"

fig=side_by_side_bar_plot(combined_data, variable=parameter)
fig
```


## Universal 

```{r, message=F, warning=F}
data_23=MBSE_23$`23 Universal`
data_24=MBSE_24$`24 Universal`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names[which(num_rows != 4)] # ensure all students have 4 rows

student_names_23=unique(data_23$...1)
num_rows=sapply(student_names_23, function(x) (data_23 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names_23[which(num_rows != 4)] # ensure all students have 4 rows 
   
```


```{r, message=F, warning=F, eval=T}

data_23_clean=data_clean(data_23) 
data_24_clean=data_clean(data_24) 

ncol(data_23_clean)==ncol(data_24_clean)

compute_pvalue(data_23_clean, data_24_clean, "Universal") %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


```{r, message=F, warning=F, eval=T}
parameter="Universal"
data_23_clean=data.frame(data_clean(data_23))
data_24_clean=data.frame(data_clean(data_24))

# Step 1: Add group labels
data_23_clean$year <- "2023"
data_24_clean$year <- "2024"
colnames(data_23_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")
colnames(data_24_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")

# Step 2: Combine the datasets
combined_data <- bind_rows(data_23_clean, data_24_clean)
colnames(combined_data)[ncol(combined_data)]="year"

fig=side_by_side_bar_plot(combined_data, variable=parameter)
fig
```


## Area Specific 

```{r, message=F, warning=F}
data_23=MBSE_23$`23 Area Specific`
data_24=MBSE_24$`24 Area Specific`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names[which(num_rows != 4)] # ensure all students have 4 rows

student_names_23=unique(data_23$...1)
num_rows=sapply(student_names_23, function(x) (data_23 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 4)) print("Correct") else student_names_23[which(num_rows != 4)] # ensure all students have 4 rows 
  
```


```{r, message=F, warning=F, eval=T}

data_23_clean=data_clean(data_23) 
data_24_clean=data_clean(data_24) 

ncol(data_23_clean)==ncol(data_24_clean)

compute_pvalue(data_23_clean, data_24_clean, "Area_Specific") %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




```{r, message=F, warning=F, eval=T}
parameter="Area_Specific"
data_23_clean=data.frame(data_clean(data_23))
data_24_clean=data.frame(data_clean(data_24))

# Step 1: Add group labels
data_23_clean$year <- "2023"
data_24_clean$year <- "2024"
colnames(data_23_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")
colnames(data_24_clean)=paste(parameter, seq(1:ncol(data_23_clean)), sep="_")

# Step 2: Combine the datasets
combined_data <- bind_rows(data_23_clean, data_24_clean)
colnames(combined_data)[ncol(combined_data)]="year"

fig=side_by_side_bar_plot(combined_data, variable=parameter)
fig
```


## Cumulative


```{r, message=F, warning=F}
data_23=MBSE_23$`23 Cumulative`
data_24=MBSE_24$`24 Cumulative`
```




```{r, message=F, warning=F}
# check if each student has the same 4 lines 
student_names=unique(data_24$...1)
num_rows=sapply(student_names, function(x) (data_24 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 5)) print("Correct") else student_names[which(num_rows != 5)] # ensure all students have 4 rows

student_names_23=unique(data_23$...1)
num_rows=sapply(student_names_23, function(x) (data_23 %>% filter(`...1`==x) %>% nrow()))
if (all(num_rows == 5)) print("Correct") else student_names_23[which(num_rows != 5)] # ensure all students have 4 rows 
  
```


```{r, message=F, warning=F, eval=F}

data_24_clean <- data_24 %>%
  filter(`...1` %in% student_names) %>%
  arrange(factor(`...1`, levels = student_names)) %>%
  select(3:9) %>%
  as.matrix() %>%
  t() %>%
  as.vector() %>%
  matrix(nrow = length(student_names), byrow = TRUE)  

pvalue=numeric()
for (i in 1:ncol(data_23_clean))
{
  if (sum(!is.na(data_23_clean[, i])) > 1 && sum(!is.na(data_24_clean[, i])) > 1) {
  pvalue[i]=t.test(data_23_clean[, i], data_24_clean[, i])$p.value
} else {
  pvalue[i]="NA"
}
  
}
  data.frame(questions=paste("Area Specific", seq(1:ncol(data_23_clean)), sep="_"), pvalue=pvalue_adjust(pvalue))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


## Perio Community of Practice


```{r, message=F, warning=F}
perio_community=read_xlsx((file.path(root, "..\\2025\\202503\\Zainab\\Perio Community of Practice_March 4, 2025_14.27 updated manual_cleaned.xlsx")))
```



```{r, message=F, warning=F}
library(rstatix)

# -------------------------------
# 1. Reshape data into long format
# -------------------------------
df_long <- perio_community %>%
  pivot_longer(
    cols = starts_with("Q"),
    names_to = "question",
    values_to = "response"
  )

# -------------------------------
# 2. Counts for bar plots
# -------------------------------
counts <- df_long %>%
  group_by(question, time, response) %>%
  summarise(n = n(), .groups = "drop")

# -------------------------------
# 3. Bar plots (pre vs post)
# -------------------------------
#ggplot(counts, aes(x = response, y = n, fill = time)) +
#  geom_bar(stat = "identity", position = "dodge") +
#  facet_wrap(~ question, scales = "free_x") +
#  theme_bw() +
#  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#  labs(x = "Response", y = "Count", title = "Pre vs Post Responses")
counts %>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### pre vs post 

```{r, message=F, warning=F}

# -------------------------------
# 4a. McNemar test (binary collapse)
# -------------------------------
df_long <- df_long %>%
  mutate(question = sub(":.*", "", question)) %>% filter(response != "N/A")

questions=unique(df_long$question)
pvalue=numeric(); k=0
variable=c()
for (i in 1:length(questions))
{
  count=df_long %>% filter(question==questions[i])
  if (length(unique(count$time))==2)
  { 
    common_response=intersect(count %>% filter(time=="pre") %>% select(response) %>% pull(), count %>% filter(time=="post") %>% select(response) %>% pull())
  for (j in 1:length(common_response))
  {
    sub_count=c(count %>% filter(time=="pre" & response ==common_response[j]) %>% nrow(), count %>% filter(time=="post" & response ==common_response[j]) %>% nrow())
    k=k+1
    pvalue[k]=binom.test(sub_count)$p.val
    variable[k]=paste0(questions[i], ":", common_response[j])
  }
  }
}
data.frame(variable, pvalue=pvalue_adjust(pvalue))%>%
datatable(extensions = 'Buttons',
          caption = "",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```

