---
title: "1/14 2025"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2025-01-14"
---

## sample size calculation 


The following factors influences the sample size 


* Power: the desired probability we correctly reject the null hypothesis of no treatment effect assuming the experimental treatment really is efficacious. 

* Significance level: the type I error we’re willing to assume.

* Marginal probabilities: the probability that a subject will be in a response level, averaged over the two treatment groups.

* Reference improvement: the odds ratio that expresses the improvement of experimental treatment over control.

* Fraction: the fraction of subjects allocated to the control group.


```{r, message=F, warning=F}
#install.packages("Hmisc")
library(Hmisc)
marg_probs=c(0.2, 0.2, 0.2, 0.2, 0.2) # equal probability 
OR=2
posamsize(p = marg_probs, odds.ratio = OR, fraction = 0.5, 
          alpha = 0.05, power = 0.8)

```

```{r, message=F, warning=F}
#install.packages("Hmisc")
library(Hmisc)
marg_probs=c(0.2, 0.2, 0.2, 0.2, 0.2) # equal probability 
OR=2
posamsize(p = marg_probs, odds.ratio = OR, fraction = 0.5, 
          alpha = 0.05, power = 0.9)

```



* [reference](https://library.virginia.edu/data/articles/power-and-sample-size-calculations-ordered-categorical-data)

