---
title: "8/17 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-08-17"
---

```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()

library(irr)
library(dplyr)
library(purrr)
library(tidyr)

```



```{r, message=F, warning=F}
#nsduh_data=as_tibble(read_excel((file.path(root, "../2026/202608/LeeZa/NSDUH data 12 to 17 years old for analysis.xlsx"))))
nsduh_data=as_tibble(read.csv((file.path(root, "../2026/202608/LeeZa/NSDUH data 12 to 17 years old for analysis(Sheet1).csv"))))

```


```{r, message=F, warning=F}
table(nsduh_data$PrevDent_24)
nsduh_data =nsduh_data %>% filter(PrevDent_24!=99)
table(nsduh_data$PrevDent_24)
```




## chi square test 


### Child and Family Demographic



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$SC_SEX, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)


```

* 	1 = Male; 2 = Female; 99 = missing

```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$race7_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1 = Hispanic; 2=White, non Hispanic; 3 = Black; 4 = Asian; 5 = American Indian; 6 = Native Hawaiian/Pacific Islander; 7 = Multi-race. 



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$povSCHIP_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1= 0 – 199%; 2 = 200 – 299%; 3 = 300 – 399%; 4 = 400% or more of poverty level




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$PrntNativity_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = all parents born in the US “3rd gen or higher; 2 = Any parent born outside of the US “1st and 2nd gen”; 3 = other “child born in the US, parents are not listed”; 99 = missing value




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$AdultEduc_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 	1 = less than high school; 2 = high school/GED; 3 = some college/technical school; 4 = college degree or higher; 99 = missing


### Child-level covariates


```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$OralProb_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = Yes; 2 = No; 95 = less than 1 year old; 99 = missing



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$ACE2more_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```



* 1 = no ACE; 2 = experienced 1 ACE; 3 = experienced 2 or more ACE; 99 = missing





## logistic regression 

```{r, message=F, warning=F}

library(tidyverse)
library(gtsummary)
library(logistf)

# 1. Select the exact variables from the dataset
covariates <- c(
  "MEDB10ScrQ5_24", "SC_AGE_YEARS", "SC_SEX", "race7_24", 
  "PrntNativity_24", "povSCHIP_24", "AdultEduc_24", "OralProb_24", 
  "ACE2more_24", "MedDentCare_24", "FamResilience_24", 
  "NbhdSafe_24", "frustrated_24"
)

formula_logit <- as.formula(
  paste("PrevDent_24 ~", paste(covariates, collapse = " + "))
)

# 2. Data Preparation
# Convert binary variable levels (In NSCH: 1 = Yes, 2 = No; recode to 0 = No, 1 = Yes for logit modeling)
nsduh_clean <- nsduh_data %>%
  select(all_of(c("PrevDent_24", covariates))) %>%
  drop_na() %>%
  mutate(
    # Recode outcome: 1 = Yes, 2 = No -> 1 = Yes, 0 = No
    PrevDent_24 = ifelse(PrevDent_24 == 1, 1, 0),
    PrevDent_24 = factor(PrevDent_24, levels = c(0, 1), labels = c("No", "Yes")),
    
    # Ensure categorical survey indicators are treated as factors
    SC_SEX = factor(SC_SEX),
    race7_24 = factor(race7_24),
    PrntNativity_24 = factor(PrntNativity_24),
    povSCHIP_24 = factor(povSCHIP_24),
    AdultEduc_24 = factor(AdultEduc_24),
    OralProb_24 = factor(OralProb_24),
    ACE2more_24 = factor(ACE2more_24),
    MedDentCare_24 = factor(MedDentCare_24),
    FamResilience_24 = factor(FamResilience_24),
    NbhdSafe_24 = factor(NbhdSafe_24),
    frustrated_24 = factor(frustrated_24)
  )

# 3. Fit Standard Logistic Regression (GLM)
logit_model <- glm(
  formula = formula_logit,
  data = nsduh_clean,
  family = binomial(link = "logit")
)

coef_mat <- summary(logit_model)$coefficients
ci_mat <- suppressMessages(confint(logit_model))

# 2. Identify common terms (drops MEDB10ScrQ5_24 automatically)
common_terms <- intersect(rownames(coef_mat), rownames(ci_mat))

# 3. Build data frame using aligned terms
clean_table <- data.frame(
  Variable = common_terms,
  OR       = exp(coef_mat[common_terms, "Estimate"]),
  CI_2.5   = exp(ci_mat[common_terms, 1]),
  CI_97.5  = exp(ci_mat[common_terms, 2]),
  p_value  = coef_mat[common_terms, "Pr(>|z|)"]
)

# 4. Format numbers for reporting
clean_table[, 2:5] <- round(clean_table[, 2:5], 4)

clean_table%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))




```





```{r, message=F, warning=F}
library(tidyverse)

# 1. Read in the model estimates
clean_table <- data.frame(
  Variable = c("(Intercept)", "SC_AGE_YEARS", "SC_SEX2", "race7_242", "race7_243", 
               "race7_244", "race7_245", "race7_246", "race7_247", "PrntNativity_242", 
               "PrntNativity_243", "PrntNativity_2499", "povSCHIP_242", "povSCHIP_243", 
               "povSCHIP_244", "AdultEduc_242", "AdultEduc_243", "AdultEduc_244", 
               "OralProb_242", "OralProb_2499", "ACE2more_242", "ACE2more_243", 
               "ACE2more_2499", "MedDentCare_242", "MedDentCare_2499", "FamResilience_242", 
               "FamResilience_243", "FamResilience_2499", "NbhdSafe_242", "NbhdSafe_243", 
               "NbhdSafe_2499", "frustrated_242", "frustrated_243", "frustrated_2499"),
  OR = c(1.56e12, 1.0782, 1.154, 0.656, 0.6367, 0.5742, 0.9277, 0, 0.6004, 0.911, 
         1.2417, 0.5465, 1.0337, 1.4418, 1.774, 1.0378, 1.1254, 1.419, 0.8364, 
         0.3409, 0.8214, 0.6744, 1.4782, 0, 0, 1.0297, 1.1411, 0.8428, 1.024, 
         0.8498, 0.6654, 0.7208, 0.581, 0.5045),
  CI_2.5 = c(6.07e204, 1.058, 0.9888, 0.5189, 0.4564, 0.3476, 0.35, 0, 0.4243, 0.7077, 
            0.92, 0.2767, 0.8311, 1.1112, 1.4251, 0.7036, 0.766, 0.9603, 0.6893, 
            0.0867, 0.6687, 0.5506, 0.6454, 0.0, 0.0, 0.755, 0.8867, 0.3992, 0.862, 
            0.6068, 0.3057, 0.6057, 0.4485, 0.1949),
  CI_97.5 = c(1.22e234, 1.099, 1.347, 0.8283, 0.8862, 0.9441, 2.5365, 0, 0.8474, 1.1726, 
             1.6764, 1.0436, 1.2849, 1.8719, 2.2103, 1.5376, 1.6611, 2.1064, 1.0145, 
             1.1136, 1.0087, 0.8255, 3.4437, 0, 0, 1.4049, 1.4703, 1.7664, 1.2168, 
             1.1843, 1.4402, 0.8574, 0.7504, 1.2254),
  p_value = c(0.9583, 0.0000, 0.0694, 0.0004, 0.0076, 0.0292, 0.8802, 0.9709, 0.0038, 
              0.4690, 0.1569, 0.0727, 0.7657, 0.0059, 0.0000, 0.8520, 0.5491, 0.0803, 
              0.0699, 0.0908, 0.0606, 0.0001, 0.3587, 0.9574, 0.9584, 0.8534, 0.3060, 
              0.6507, 0.7870, 0.3394, 0.3003, 0.0002, 0.0000, 0.1407)
)

# 2. Prepare data for plotting (Original linear scale)
plot_data <- clean_table %>%
  filter(Variable != "(Intercept)", OR > 0) %>%
  mutate(
    Variable = factor(Variable, levels = rev(Variable)),
    Significance = ifelse(p_value < 0.05, "p < 0.05", "p ≥ 0.05")
  )

# 3. Draw Forest Plot on Original Scale
forest_linear <- ggplot(plot_data, aes(x = OR, y = Variable, color = Significance)) +
  # Null reference line at OR = 1.0
  geom_vline(xintercept = 1.0, linetype = "dashed", color = "black", linewidth = 0.6) +
  # Error bars for 95% CIs
  geom_errorbarh(aes(xmin = CI_2.5, xmax = CI_97.5), height = 0.2, linewidth = 0.8) +
  # Square markers for Odds Ratios
  geom_point(shape = 15, size = 2.8) +
  # Linear X-axis scale (0 to 3.5)
  scale_x_continuous(
    limits = c(0, 4.6), 
    breaks = seq(0, 3.5, by = 0.5),
    expand = c(0, 0)
  ) +
  # Palette matching publication standards
  scale_color_manual(values = c("p < 0.05" = "#d95f02", "p ≥ 0.05" = "#2b83ba")) +
  # Annotate Odds Ratio & 95% CI text on the right side
  geom_text(
    aes(x = 4.2, label = sprintf("%.2f (%.2f, %.2f)", OR, CI_2.5, CI_97.5)),
    hjust = 1, size = 3, color = "black", fontface = "plain"
  ) +
  labs(
    title = "FOREST PLOT: MULTIVARIABLE LOGISTIC REGRESSION OUTCOMES",
    subtitle = "Odds Ratios (95% CI) Presented on Original Scale",
    x = "Odds Ratio (OR)",
    y = NULL,
    color = NULL
  ) +
  theme_classic(base_size = 11) +
  theme(
    legend.position = "top",
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, face = "italic"),
    axis.text.y = element_text(face = "bold", color = "black"),
    axis.line = element_line(color = "black")
  )

print(forest_linear)
```
