---
title: "03/03 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-03-03"
---


```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()

```



```{r, message=F, warning=F, results=F}
#data=multiplesheets((file.path(root, "../2026/202603/Abdulaziz/Color Change Averages.xlsx")))
#saveRDS(data$cleaned_data, file=file.path(root, "../2026/202603/Abdulaziz/cleaned_data.RDs"))

cleaned_data=readRDS(file.path(root, "../2026/202603/Abdulaziz/cleaned_data.RDs"))
```


```{r, message=F, warning=F}
time_intervals=unique(cleaned_data$time_interval)
solutions=unique(cleaned_data$solution)
materials=unique(cleaned_data$material)
methods=unique(cleaned_data$...4)
```


```{r, message=F, warning=F}
analyze_dental_color <- function(data, target_type, target_material) {
  
  # 1. Filter and Prepare Data
  analysis_df <- data %>%
    filter(`...4` == target_type & material == target_material) %>%
    mutate(specimen_id = str_extract(...1, "\\d$"))
  
  # 2. Repeated Measures ANOVA
  anova_table <- analysis_df %>%
    group_by(solution) %>%
    anova_test(dv = DeltaE, wid = specimen_id, within = time_interval) %>%
    get_anova_table()
  
  # 3. Pairwise Comparisons
  pairwise_table <- analysis_df %>%
    group_by(solution) %>%
    pairwise_t_test(
      DeltaE ~ time_interval, 
      paired = TRUE, 
      p.adjust.method = "bonferroni",
      conf.level = 0.95,
      detailed = TRUE
    ) %>%
    rename(mean_diff = estimate) %>%
    select(solution, group1, group2, n1, mean_diff, conf.low, conf.high, p.adj, p.adj.signif) %>%
    # Rounding the numerical columns
    mutate(
      mean_diff = round(mean_diff, 4),
      conf.low = round(conf.low, 4),
      conf.high = round(conf.high, 4)
    )
  
  # Return both tables as a list
  return(list(anova = anova_table, pairwise = pairwise_table))
}
```




```{r, message=F, warning=F}
compare_all_scenarios <- function(data, target_type, mat1, mat2) {
  
  # 1. Filter for the two materials and the specific measurement type (SCI/SCE)
  comparison_df <- data %>%
    filter(`...4` == target_type) %>%
    filter(material %in% c(mat1, mat2))
  
  # 2. Group by solution and interval, then run independent t-tests
  results_table <- comparison_df %>%
    group_by(solution, time_interval) %>%
    t_test(
      DeltaE ~ material, 
      paired = FALSE,         # Materials are separate specimens
      detailed = TRUE,
      conf.level = 0.95
    ) %>%
    # 3. Add significance thresholds
    add_significance(
      p.col = "p",
      cutpoints = c(0, 0.001, 0.01, 0.05, 1),
      symbols = c("***", "**", "*", "ns")
    ) %>%
    # 4. Clean up, rename, and format
    rename(mean_diff = estimate) %>%
    mutate(
      across(c(mean_diff, conf.low, conf.high), ~ round(.x, 4)),
      p = format.pval(p, digits = 4, eps = 0.001)
    ) %>%
    # 5. Select key columns for comparison
    select(solution, time_interval, group1, group2, n1, n2, mean_diff, conf.low, conf.high, p, p.signif)
  
  return(results_table)
}
```



## SCI 


### Rodin 




```{r, message=F, warning=F}
SCI_rodin=analyze_dental_color(cleaned_data, "SCI", "Rodin")

SCI_rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

SCI_rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



***: $p < 0.001$

**: $p < 0.01$

*: $p < 0.05$

ns: $p \geq 0.05$


### Varseosmile

```{r, message=F, warning=F}
SCI_rodin=analyze_dental_color(cleaned_data, "SCI", "Varseosmile")

SCI_rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

SCI_rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### Sprintray

```{r, message=F, warning=F}
SCI_rodin=analyze_dental_color(cleaned_data, "SCI", "Sprintray")

SCI_rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

SCI_rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```





### Rodin vs Varseosmile


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCI", "Rodin", "Varseosmile")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### Rodin vs Sprintray


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCI", "Rodin", "Sprintray")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


### Varseosmile vs Sprintray


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCI", "Varseosmile", "Sprintray")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```




## SCE 


### Rodin 




```{r, message=F, warning=F}
rodin=analyze_dental_color(cleaned_data, "SCE", "Rodin")

rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



***: $p < 0.001$

**: $p < 0.01$

*: $p < 0.05$

ns: $p \geq 0.05$


### Varseosmile

```{r, message=F, warning=F}
rodin=analyze_dental_color(cleaned_data, "SCE", "Varseosmile")

rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### Sprintray

```{r, message=F, warning=F}
rodin=analyze_dental_color(cleaned_data, "SCE", "Sprintray")

rodin$anova%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

rodin$pairwise%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```





### Rodin vs Varseosmile


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCE", "Rodin", "Varseosmile")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```



### Rodin vs Sprintray


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCE", "Rodin", "Sprintray")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


### Varseosmile vs Sprintray


```{r, message=F, warning=F}
full_report <- compare_all_scenarios(cleaned_data, "SCE", "Varseosmile", "Sprintray")
full_report%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
```


## statistical analysis

```{r, message=F, warning=F}
R.version
```

R version 4.3.2 was used for all analysis. Statistical significance was determined if p values is less than 5\%. Repeated-measure annova was conducted across all different time intervals, Paired two sample t test was used between time intervals for specific materials with a specific solution and independent t test was used between different materials with the same solution and time period.    
