---
title: "8/17 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-08-17"
---

```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()

library(irr)
library(dplyr)
library(purrr)
library(tidyr)

```



```{r, message=F, warning=F}
#nsduh_data=as_tibble(read_excel((file.path(root, "../2026/202608/LeeZa/NSDUH data 12 to 17 years old for analysis.xlsx"))))
nsduh_data=as_tibble(read.csv((file.path(root, "../2026/202608/LeeZa/NSDUH data 12 to 17 years old for analysis(Sheet1)_20260928.csv"))))

```


```{r, message=F, warning=F}
table(nsduh_data$PrevDent_24)
nsduh_data =nsduh_data %>% filter(PrevDent_24!=99)
table(nsduh_data$PrevDent_24)
```




## chi square test 


### Child and Family Demographic



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$SC_SEX, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)


```

* 	1 = Male; 2 = Female;

* small p values suggests there is a gender bias for outcome variable. 


```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$race7_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1 = Hispanic; 2=White, non Hispanic; 3 = Black; 4 = Asian; 5 = American Indian; 6 = Native Hawaiian/Pacific Islander; 7 = Multi-race. 



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$povSCHIP_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1= 0 – 199%; 2 = 200 – 299%; 3 = 300 – 399%; 4 = 400% or more of poverty level




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$PrntNativity_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = all parents born in the US “3rd gen or higher; 2 = Any parent born outside of the US “1st and 2nd gen”; 3 = other “child born in the US, parents are not listed”; 99 = missing value




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$AdultEduc_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 	1 = less than high school; 2 = high school/GED; 3 = some college/technical school; 4 = college degree or higher; 99 = missing


### Child-level covariates


```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$OralProb_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = Yes; 2 = No; 95 = less than 1 year old; 99 = missing



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevDent_24, 
  nsduh_data$ACE2more_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```



* 1 = no ACE; 2 = experienced 1 ACE; 3 = experienced 2 or more ACE; 99 = missing





## logistic regression 

```{r, message=F, warning=F}

library(tidyverse)
library(gtsummary)
library(logistf)

# 1. Select the exact variables from the dataset
covariates <- c(
  "MEDB10ScrQ5_24", "SC_AGE_YEARS", "SC_SEX", "race7_24", 
  "PrntNativity_24", "povSCHIP_24", "AdultEduc_24", "OralProb_24", 
  "ACE2more_24", "MedDentCare_24", "FamResilience_24", 
  "NbhdSafe_24", "frustrated_24", "EmploymentSt_24", "SpEducPln_24"
)

formula_logit <- as.formula(
  paste("PrevDent_24 ~", paste(covariates, collapse = " + "))
)

# 2. Data Preparation
# Convert binary variable levels (In NSCH: 1 = Yes, 2 = No; recode to 0 = No, 1 = Yes for logit modeling)
nsduh_clean <- nsduh_data %>%
  select(all_of(c("PrevDent_24", covariates))) %>%
  drop_na() %>%
  mutate(
    # Recode outcome: 1 = Yes, 2 = No -> 1 = Yes, 0 = No
    PrevDent_24 = ifelse(PrevDent_24 == 1, 1, 0),
    PrevDent_24 = factor(PrevDent_24, levels = c(0, 1), labels = c("No", "Yes")),
    
    # Ensure categorical survey indicators are treated as factors
    SC_SEX = factor(SC_SEX),
    race7_24 = factor(race7_24),
    PrntNativity_24 = factor(PrntNativity_24),
    povSCHIP_24 = factor(povSCHIP_24),
    AdultEduc_24 = factor(AdultEduc_24),
    OralProb_24 = factor(OralProb_24),
    ACE2more_24 = factor(ACE2more_24),
    MedDentCare_24 = factor(MedDentCare_24),
    FamResilience_24 = factor(FamResilience_24),
    NbhdSafe_24 = factor(NbhdSafe_24),
    frustrated_24 = factor(frustrated_24)
  )

# 3. Fit Standard Logistic Regression (GLM)
logit_model <- glm(
  formula = formula_logit,
  data = nsduh_clean,
  family = binomial(link = "logit")
)

coef_mat <- summary(logit_model)$coefficients

#Wald CIs: Estimate ± 1.96 * Std. Error
estimates  <- coef_mat[, "Estimate"]
std_errors <- coef_mat[, "Std. Error"]

clean_table <- data.frame(
  Variable = rownames(coef_mat),
  OR       = exp(estimates),
  CI_2.5   = exp(estimates - 1.96 * std_errors),
  CI_97.5  = exp(estimates + 1.96 * std_errors),
  p_value  = coef_mat[, "Pr(>|z|)"]
)

# 4. Format numbers for reporting
clean_table[, 2:5] <- round(clean_table[, 2:5], 4)

clean_table%>%
datatable(extensions = 'Buttons',
          caption = "", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))




```


* for continuous variable, for example `SC_AGE_YEARS`, one unit of increase will results in odds increase by 10.24% of not having outcome variable. 

* for discrete variable, such as `race7_24`, `race7_24_1` is the reference group, compared to the reference group, `race7_242` has (1-0.646)=0.354 (35.4%) decrease in odds of not having outcome variable. 





```{r, message=F, warning=F}
library(dplyr)
library(ggplot2)

# 1. Process and clean data directly from `clean_table`
plot_data <- clean_table %>%
  # Exclude intercept, zero estimates, and infinite upper confidence bounds
  filter(
    Variable != "(Intercept)",
    OR > 0,
    !is.infinite(CI_97.5),
    !is.infinite(CI_2.5)
  ) %>%
  mutate(
    # Set factor levels so variables plot in order top-to-bottom
    Variable = factor(Variable, levels = rev(Variable)),
    Significance = ifelse(p_value < 0.05, "p < 0.05", "p ≥ 0.05"),
    
    # Cap upper CI for visual error bars to keep the plot scale readable (up to 4.5)
    CI_97.5_plot = pmin(CI_97.5, 4.5),
    
    # Format actual text label for the right-hand side table column
    LabelText = sprintf("%.2f (%.2f, %.2f)", OR, CI_2.5, CI_97.5)
  )

# 2. Draw Forest Plot on Original Scale
forest_linear <- ggplot(plot_data, aes(x = OR, y = Variable, color = Significance)) +
  # Reference line at Null Effect (OR = 1.0)
  geom_vline(xintercept = 1.0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  
  # 95% Confidence Interval error bars
  geom_errorbarh(aes(xmin = CI_2.5, xmax = CI_97.5_plot), height = 0.25, linewidth = 0.8) +
  
  # Odds Ratio point estimates
  geom_point(shape = 15, size = 2.8) +
  
  # Custom X-axis scale with padding on the right for text annotations
  scale_x_continuous(
    limits = c(0, 6.2), 
    breaks = seq(0, 4.5, by = 0.5),
    expand = c(0, 0)
  ) +
  
  # Color palette matching publication standards
  scale_color_manual(values = c("p < 0.05" = "#d95f02", "p ≥ 0.05" = "#2b83ba")) +
  
  # Text annotations on the right side
  geom_text(
    aes(x = 6.0, label = LabelText),
    hjust = 1, size = 3, color = "black", fontface = "plain"
  ) +
  
  # Labels and Layout
  labs(
    title = "FOREST PLOT: MULTIVARIABLE LOGISTIC REGRESSION OUTCOMES",
    subtitle = "Odds Ratios (95% CI) Presented on Original Scale",
    x = "Odds Ratio (OR)",
    y = NULL,
    color = NULL
  ) +
  theme_classic(base_size = 11) +
  theme(
    legend.position = "top",
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, face = "italic"),
    axis.text.y = element_text(face = "bold", color = "black"),
    axis.line = element_line(color = "black")
  )

print(forest_linear)
```
