---
title: "Bland Altman analysis"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-05-06"
---

```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()

```



## home page 

[home](2026_0303_Arndt.html)


### trueness

```{r, echo=F, message=F, warning=F}
trueness=as_tibble(read.csv(file.path(root, "..\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_trueness.csv" )),header=T)
methods2=c("FGAS_LS", "FGAS_IOS", "FGAS_CBCT", "FHAS_LS", "FHAS_IOS", "FHAS_CBCT")
trueness=trueness %>% mutate(methods=rep(methods2, each=20)) # add new column with unique sample ID's 
```


```{r, message=F, warning=F}
library(tidyverse)
library(blandr)

compare_methods_ba <- function(df, method_a, method_b) {
  
  # 1. Identify numeric variables to analyze
  vars_to_analyze <- df %>% 
    select(where(is.numeric), -Implant.position) %>% 
    colnames()
  
  # 2. Create a standardized 'Match_ID' based on the trailing number
  # This turns "FGAS_LS_1" and "FGAS_IOS_1" both into "1"
  df_clean <- df %>%
    filter(methods %in% c(method_a, method_b)) %>%
    mutate(Match_ID = as.numeric(str_extract(Sample, "\\d+$")))
  
  # 3. Pivot the data using our new Match_ID
  df_wide <- df_clean %>%
    select(Match_ID, methods, all_of(vars_to_analyze)) %>%
    pivot_wider(
      names_from = methods,
      values_from = all_of(vars_to_analyze)
    ) %>%
    drop_na() # Ensures we only plot samples present in both groups
  
  # 4. Generate the plots
  for (var in vars_to_analyze) {
    col_a <- paste0(var, "_", method_a)
    col_b <- paste0(var, "_", method_b)
    
    # Using try() to ensure the loop continues if one plot fails
    try({
      p <- blandr.draw(df_wide[[col_a]], df_wide[[col_b]]) +
        labs(
          title = paste("Bland-Altman Agreement:", var),
          subtitle = paste(method_a, "vs.", method_b, "| n =", nrow(df_wide)),
          x = "Mean of Measurements",
          y = "Difference (A - B)"
        ) +
        theme_minimal()
      
      print(p)
    })
  }
}

```


```{r, message=F, warning=F}
compare_methods_ba(trueness, "FGAS_LS", "FGAS_IOS")
compare_methods_ba(trueness, "FGAS_LS", "FGAS_CBCT")
compare_methods_ba(trueness, "FGAS_IOS", "FGAS_CBCT")


compare_methods_ba(trueness, "FHAS_LS", "FHAS_IOS")
compare_methods_ba(trueness, "FHAS_LS", "FHAS_CBCT")
compare_methods_ba(trueness, "FHAS_IOS", "FHAS_CBCT")

```


Interpretations: use FHAS_IOS vs FHAS_CBCT as an example 

1. Blue zone: mean bias value ($\bar{d}$, average of all difference), around 0.11. on average FHAS_IOS is 0.11 unit higher than FHAS_CBCT. the blue area ($\bar{d}+/-(t\times s/\sqrt{n})$, $s$, standard deviation of differences) is 95\% CI of the bias. Because solid line at 0 is outside the CI, so the bias is significant. 

2. the green zone (upper limit of agreement), top end of 95% of the data difference expected to fall  
dashed line: $\bar{d}+1.96 \times s$. shaded boundary: $dashed~line +/-(t\times \sqrt{3\times s^2/n})$


3.  red zone (lower limit of agreement), bottom end of 95% of the data difference expected to fall 

dashed line: $\bar{d}-1.96 \times s$. boundary: $dashed~line +/-(t\times \sqrt{3\times s^2/n})$



4. . most data points are within 0 and 0.2, showing relative stable agreement. 

5. all points fall within the green and red limits of agreement, indicating there are no extreme outliers in this comparison.



### precision 



```{r, echo=F, message=F, warning=F, eval=T}
precision=as_tibble(read.csv(file.path(root, "..\\2022\\202210\\Ajitesh\\Final RAW DATA ALL SAMPLES_AS_precision.csv"), header=T))


precision_data_all=list()

parameters=c("Angle", "Base.3D.offset", "Base.distal", "Base.vestibular", "Base.apical", "Tip.3D.offset", "Tip.distal", "Tip.vestibular", "Tip.apical")
for (i in 1:length(parameters))
{
precision_parameter=precision %>%  dplyr::select(ends_with(parameters[i])) %>% slice_tail(n = 191) # the last 191 rows as precision 
methods3=colnames(precision_parameter)
precision_parameter_long=data.frame(vs_distance=c(precision_parameter[,1] %>% pull, precision_parameter[,2] %>% pull, precision_parameter[,3] %>% pull, precision_parameter[,4] %>% pull, precision_parameter[,5] %>% pull, precision_parameter[,6] %>% pull), methods=rep(methods3, each=191))
precision_data_all[[i]]=precision_parameter_long
  
}

```


```{r, message=F, warning=F}
library(tidyverse)
library(blandr)

compare_methods_pairwise <- function(df, value_col = "vs_distance", method_col = "methods") {
  
  # 1. Create a Match_ID to pair the first observation of Method A 
  # with the first observation of Method B, and so on.
  df_indexed <- df %>%
    group_by(across(all_of(method_col))) %>%
    mutate(Match_ID = row_number()) %>%
    ungroup()
  
  # 2. Get a list of unique methods
  unique_methods <- unique(df[[method_col]])
  
  # 3. Generate all unique pairs (e.g., Method1 vs Method2)
  method_pairs <- combn(unique_methods, 2, simplify = FALSE)
  
  # 4. Loop through each pair and generate the analysis
  for (pair in method_pairs) {
    method_a <- pair[1]
    method_b <- pair[2]
    
    # Filter for the two methods and pivot to wide format for subtraction
    df_pair <- df_indexed %>%
      filter(.data[[method_col]] %in% c(method_a, method_b)) %>%
      select(Match_ID, !!sym(method_col), !!sym(value_col)) %>%
      pivot_wider(names_from = !!sym(method_col), values_from = !!sym(value_col)) %>%
      drop_na() # Ensure only paired samples are analyzed
    
    # Generate the Bland-Altman Plot
    # Using try() to prevent the loop from breaking if one pair has issues
    try({
      p <- blandr.draw(df_pair[[method_a]], df_pair[[method_b]]) +
        labs(
          title = "Pairwise Bland-Altman Analysis",
          subtitle = paste(method_a, "vs.", method_b),
          x = "Mean of Measurements",
          y = "Difference (A - B)"
        ) +
        theme_minimal()
      
      print(p)
    })
  }
}

```


```{r, message=F, warning=F}
compare_methods_pairwise(precision_data_all[[1]])
compare_methods_pairwise(precision_data_all[[2]])
compare_methods_pairwise(precision_data_all[[3]])
compare_methods_pairwise(precision_data_all[[4]])
compare_methods_pairwise(precision_data_all[[5]])
compare_methods_pairwise(precision_data_all[[6]])
compare_methods_pairwise(precision_data_all[[7]])
compare_methods_pairwise(precision_data_all[[8]])
compare_methods_pairwise(precision_data_all[[9]])
```
