---
title: "6/12 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-06-12"
---


```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()
```



```{r, message=F, warning=F, results=F}
#Trueness_Falcon_vs_Navident_vs_XGuide=multiplesheets(file.path(root, "../2026/202606/Arndt/Trueness_Falcon vs Navident vs XGuide.xlsx"))
#save(Trueness_Falcon_vs_Navident_vs_XGuide, file=file.path(root, "../2026/202606/Arndt/Trueness_Falcon_vs_Navident_vs_XGuide.RData"))
load(file.path(root, "../2026/202606/Arndt/Trueness_Falcon_vs_Navident_vs_XGuide.RData"))
```


```{r, message=F, warning=F}
data=Trueness_Falcon_vs_Navident_vs_XGuide$`Trueness_Falcon vs Navident vs `
codes=Trueness_Falcon_vs_Navident_vs_XGuide$Sheet1
```





## workflow 2



```{r, message=F, warning=F}
data_workflow2 <- data %>% filter(Workflow==2)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow2
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```





* From random effect table, between patients difference 0.00216. Unexplained variance 0.0776  is much  higher than patient variance, indicating random noise or position has a bigger effect. 

* Fixed effects: with the position17 as the reference, e.g. Angle is 0.20667 units higher at position18  than position17. 


* ICC (0.027), 2.7% variation due to patients, R2 (cond), total variation is 11.1% and positions explain about 8.6% (R2 (marg.)) of variations. 





```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow2)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



## workflow 1



```{r, message=F, warning=F}
data_workflow1 <- data %>% filter(Workflow==1)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow1
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```








```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow1)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



## workflow 3



```{r, message=F, warning=F}
data_workflow3 <- data %>% filter(Workflow==3)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow3
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```










```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow3)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



## figures 

```{r, message=F, warning=F}
Trueness_Falcon_vs_Navident_vs_XGuide_with_negative=read.csv(file.path(root, "../2026/202606/Arndt/Trueness_Falcon vs Navident vs XGuide_with negative.csv"), header=T)
```








```{r, message=F, warning=F}
library(tidyverse)

# Ensure data frame alias points to the actual dataset
df_raw <- Trueness_Falcon_vs_Navident_vs_XGuide_with_negative

# ==============================================================================
# 1. PROCESS AND RESTRUCTURE THE BIVARIATE DATA
# ==============================================================================
df_crest_processed <- df_raw %>%
  select(
    Sample, Workflow, Position, 
    X = Vestibular.Oral.Deviation.at.Crest, 
    Y = Mesial.Distal.Deviation.at.Crest
  ) %>%
  mutate(Type = "Platform (Crest)")

df_tip_processed <- df_raw %>%
  select(
    Sample, Workflow, Position, 
    X = Vestibular.Oral.Deviation.at.Tip, 
    Y = Mesial.Distal.Deviation.at.Tip
  ) %>%
  mutate(Type = "Apex (Tip)")

bivariate_plot_data <- bind_rows(df_crest_processed, df_tip_processed) %>%
  mutate(Type = factor(Type, levels = c("Apex (Tip)", "Platform (Crest)")))

# ==============================================================================
# FIX: PRE-CALCULATE EM-TRUE CENTERS (1 Point per Type per Workflow)
# ==============================================================================
mean_centers <- bivariate_plot_data %>%
  group_by(Workflow, Type) %>%
  summarise(
    Mean_X = mean(X, na.rm = TRUE),
    Mean_Y = mean(Y, na.rm = TRUE),
    .groups = "drop"
  )


# ==============================================================================
# 2. CONSTRUCT EXPANDED TARGET BACKGROUND RINGS (OUT TO 1.0 mm)
# ==============================================================================
make_target_circle <- function(r) {
  tibble(
    theta = seq(0, 2 * pi, length.out = 200),
    x = r * cos(theta),
    y = r * sin(theta),
    radius_group = as.character(r)
  )
}
target_rings <- map_df(seq(0.125, 2.0, by = 0.25), make_target_circle)


# ==============================================================================
# 3. LOOP TO GENERATE THE STANDALONE FIGURES
# ==============================================================================
unique_workflows <- unique(bivariate_plot_data$Workflow)
workflow_plots <- list()

for (current_wf in unique_workflows) {
  
  
  # FIX: Translate numeric Workflow IDs into your designated clear system names
  wf_title_name <- case_when(
    current_wf == 1 ~ "X-Guide",
    current_wf == 2 ~ "Falcon",
    current_wf == 3 ~ "Navident",
    TRUE            ~ paste("Workflow", current_wf) # Safety fallback
  )
  
  
  # Filter datasets for the active workflow loop iteration
  wf_ellipse_data <- bivariate_plot_data %>% filter(Workflow == current_wf)
  wf_mean_data    <- mean_centers %>% filter(Workflow == current_wf)
  
  workflow_plots[[as.character(current_wf)]] <- ggplot() +
    # A. Background pink target rings layers
    geom_path(
      data = target_rings, 
      aes(x = x, y = y, group = radius_group), 
      color = "red", 
      linewidth = 2.5, 
      alpha = 0.4
    ) +
    
    # B. Crosshairs intersecting at (0,0)
    geom_hline(yintercept = 0, linetype = "dotted", color = "black", linewidth = 0.6) +
    geom_vline(xintercept = 0, linetype = "dotted", color = "black", linewidth = 0.6) +
    
    # C. 95% Bivariate Confidence Ellipses (uses the full dataset for covariance math)
    stat_ellipse(
      data = wf_ellipse_data, 
      aes(x = X, y = Y, color = Type, linetype = Type, fill = Type), 
      geom = "polygon", 
      alpha = 0.30, 
      level = 0.95,
      linewidth = 0.6
    ) +
    
    # D. FIX: Draw ONLY the explicitly calculated single center-mean points
    geom_point(
      data = wf_mean_data,
      aes(x = Mean_X, y = Mean_Y, shape = Type, fill = Type),
      color = "black",
      size = 5.0, # Made comfortably large since it is the star of the show
      stroke = 1.0
    ) +
    
    # E. Aesthetic styling configurations
    scale_shape_manual(values = c("Platform (Crest)" = 21, "Apex (Tip)" = 25)) +
    scale_linetype_manual(values = c("Platform (Crest)" = "solid", "Apex (Tip)" = "dashed")) +
    scale_color_manual(values = c("Platform (Crest)" = "black", "Apex (Tip)" = "black")) +
    scale_fill_manual(values = c("Platform (Crest)" = "#64B5F6", "Apex (Tip)" = "#64B5F6")) + 
    
    # F. Coordinate Constraints set exactly to (-1, 1)
    coord_fixed(xlim = c(-2.0, 2.0), ylim = c(-2.0, 2.0)) +
    scale_x_continuous(breaks = seq(-2.0, 2.0, 0.5)) +
    scale_y_continuous(breaks = seq(-2.0, 2.0, 0.5)) +
    
    # G. Axis / Legend Labels
    labs(
      title = paste("Bivariate 95% Confidence Interval for Mean —", wf_title_name),
      subtitle = "True Center-Means Only (±2.0 mm space)",
      x = "Vestibular–Oral Deviation (mm)",
      y = "Mesial–Distal Deviation (mm)"
    ) +
    
    # H. Professional Engineering Themes
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold", size = 12, hjust = 0.5),
      plot.subtitle = element_text(size = 9, color = "gray30", hjust = 0.5, margin = margin(b = 12)),
      panel.background = element_rect(fill = "white", color = NA),
      panel.grid.major = element_line(color = "#EBF0F5", linewidth = 0.4),
      panel.grid.minor = element_blank(),
      legend.title = element_blank(),
      legend.position = "right"
    )
}
```



* Platform (Crest): X-Vestibular.Oral.Deviation.at.Crest, y-Mesial.Distal.Deviation.at.Crest

* Apex (Tip), X-Vestibular.Oral.Deviation.at.Tip, y-Mesial.Distal.Deviation.at.Tip


```{r, message=F, warning=F}
# Display each plot element individually in your viewer console
print(workflow_plots[[1]]) # Displays the first workflow category graph
print(workflow_plots[[2]]) # Displays the second workflow category graph
print(workflow_plots[[3]]) # Displays the third workflow category graph
```



