---
title: "8/17 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-08-17"
---

```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()

library(irr)
library(dplyr)
library(purrr)
library(tidyr)

```



```{r, message=F, warning=F}
nsduh_data=as_tibble(read_excel((file.path(root, "../2026/202608/LeeZa/NSDUH data 12 to 17 years old for analysis.xlsx"))))
```


```{r, message=F, warning=F}
table(nsduh_data$PrevMed_24)
```




## chi square test 


### Child and Family Demographic



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$sex_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)


```

* 	1 = Male; 2 = Female; 99 = missing

```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$race7_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1 = Hispanic; 2=White, non Hispanic; 3 = Black; 4 = Asian; 5 = American Indian; 6 = Native Hawaiian/Pacific Islander; 7 = Multi-race. 



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$povSCHIP_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```

* 1= 0 – 199%; 2 = 200 – 299%; 3 = 300 – 399%; 4 = 400% or more of poverty level




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$PrntNativity_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = all parents born in the US “3rd gen or higher; 2 = Any parent born outside of the US “1st and 2nd gen”; 3 = other “child born in the US, parents are not listed”; 99 = missing value




```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$AdultEduc_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 	1 = less than high school; 2 = high school/GED; 3 = some college/technical school; 4 = college degree or higher; 99 = missing


### Child-level covariates


```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$OralProb_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```


* 1 = Yes; 2 = No; 95 = less than 1 year old; 99 = missing



```{r, message=F, warning=F}
library(gmodels)
# Generate table with observed counts and expected values
CrossTable(
  nsduh_data$PrevMed_24, 
  nsduh_data$ACE2more_24, 
  expected = TRUE, 
  prop.r = FALSE, 
  prop.c = FALSE, 
  prop.t = FALSE, 
  prop.chisq = FALSE
)
```



* 1 = no ACE; 2 = experienced 1 ACE; 3 = experienced 2 or more ACE; 99 = missing





## logistic regression 

