---
title: "6/12 2026"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
date: "2026-06-12"
---


```{r, echo=F, message=F, warning=F, results=F}
library(rprojroot)
root <- rprojroot::find_rstudio_root_file()
source(file.path(root, "analysis/Rfunctions.R"))
root <- rprojroot::find_rstudio_root_file()
```



```{r, message=F, warning=F, results=F}
#Trueness_Falcon_vs_Navident_vs_XGuide=multiplesheets(file.path(root, "../2026/202606/Arndt/Trueness_Falcon vs Navident vs XGuide.xlsx"))
#save(Trueness_Falcon_vs_Navident_vs_XGuide, file=file.path(root, "../2026/202606/Arndt/Trueness_Falcon_vs_Navident_vs_XGuide.RData"))
load(file.path(root, "../2026/202606/Arndt/Trueness_Falcon_vs_Navident_vs_XGuide.RData"))
```


```{r, message=F, warning=F}
data=Trueness_Falcon_vs_Navident_vs_XGuide$`Trueness_Falcon vs Navident vs `
codes=Trueness_Falcon_vs_Navident_vs_XGuide$Sheet1
```





## workflow 2



```{r, message=F, warning=F}
data_workflow2 <- data %>% filter(Workflow==2)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow2
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```





* From random effect table, between patients difference 0.00216. Unexplained variance 0.0776  is much  higher than patient variance, indicating random noise or position has a bigger effect. 

* Fixed effects: with the position17 as the reference, e.g. Angle is 0.20667 units higher at position18  than position17. 


* ICC (0.027), 2.7% variation due to patients, R2 (cond), total variation is 11.1% and positions explain about 8.6% (R2 (marg.)) of variations. 





```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow2)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



## workflow 1



```{r, message=F, warning=F}
data_workflow1 <- data %>% filter(Workflow==1)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow1
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```








```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow1)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```



## workflow 3



```{r, message=F, warning=F}
data_workflow3 <- data %>% filter(Workflow==3)  %>%
  mutate(
    patient = sub("_.*", "", Sample),  # D01, D02, ...
    patient = factor(patient),
    Position = factor(Position)        # treat positions as fixed categories
  )
library(lme4)
library(Matrix)
library(performance)

m_angle <- lmer(
  Angle ~ Position + (1 | patient),
  data = data_workflow3
)
isSingular(m_angle)        # TRUE/FALSE
summary(m_angle)
VarCorr(m_angle)           # shows variance of random effects

model_performance(m_angle)
```










```{r, message=F, warning=F}
library(broom.mixed)
library(lmerTest)

outcomes <- c(
  "Angle",
  "3D Deviation at Crest",
  "Mesial-Distal Deviation at Crest",
  "Vestibular-Oral Deviation at Crest",
  "Vertical Deviation at Crest",
  "3D Deviation at Tip",
  "Mesial-Distal Deviation at Tip",
  "Vestibular-Oral Deviation at Tip",
  "Vertical Deviation at Tip",
  "Vertica Deviation as Total"
)

results_list <- lapply(outcomes, function(yvar) {
  # FIX: Wrap yvar in backticks so R accepts numbers and spaces in column names
  formula_str <- sprintf("`%s` ~ Position + (1 | patient)", yvar)
  
  # Fit LMM with lmerTest to get p-values
  mod <- lmer(as.formula(formula_str), data = data_workflow3)
  
  # Fixed effects with p-values
  fe <- broom.mixed::tidy(mod, effects = "fixed") %>%
    select(term, estimate, std.error, statistic, p.value) %>%
    mutate(
      estimate = round(estimate, 4),
      std.error = round(std.error, 4),
      statistic = round(statistic, 4),
      p.value = round(p.value, 4),
      outcome = yvar
    )
  
  # Random effects variance
  re <- as.data.frame(lme4::VarCorr(mod)) %>%
    select(grp, var1, vcov) %>%
    rename(Group = grp, RandomEffect = var1, Variance = vcov) %>%
    mutate(
      Variance = round(Variance, 4),
      outcome = yvar
    )
  
  list(fixed = fe, random = re)
})


fixed_table <- do.call(rbind, lapply(results_list, `[[`, "fixed")) %>%
  select(outcome, term, estimate, std.error, statistic, p.value)

fixed_table%>%
datatable(extensions = 'Buttons',
          caption = "fixed effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))


random_table <- do.call(rbind, lapply(results_list, `[[`, "random")) %>%
  select(outcome, Group, RandomEffect, Variance)

random_table%>%
datatable(extensions = 'Buttons',
          caption = "random effect", 
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))

```

