---
title: "Latent Class longitudinal data analysis"
author: "Shengtong Han"
date: ""
output: html_document
---

Review R for latent class growth analysis (LCGA) and/or growth mixture models (GMMs). 

## Jointlcmm 

This function fits joint latent class mixed models for a longitudinal outcome and a right-censored (possibly left-truncated) time-to-event. The function handles competing risks and Gaussian or non Gaussian (curvilinear) longitudinal outcomes. For curvilinear longitudinal outcomes, normalizing continuous functions (splines or Beta CDF) can be specified as in lcmm.

### Example 

Here is the [Example](https://cran.r-project.org/web/packages/lcmm/lcmm.pdf). 

```{r, echo=T}
#### Example of a joint latent class model estimated for a varying number
    # of latent classes:
    # The linear mixed model includes a subject- (ID) and class-specific
    # linear trend (intercept and Time in fixed, random and mixture components)
    # and a common effect of X1 and its interaction with time over classes
    # (in fixed).
    # The variance of the random intercept and slopes are assumed to be equal
    # over classes (nwg=F).
    # The covariate X3 predicts the class membership (in classmb).

# The baseline hazard function is modelled with cubic M-splines -3
    # nodes at the quantiles- (in hazard) and a proportional hazard over
    # classes is assumed (in hazardtype). Covariates X1 and X2 predict the
    # risk of event (in survival) with a common effect over classes for X1
    # and a class-specific effect of X2.
    # !CAUTION: for illustration, only default initial values where used but
    # other sets of initial values should be tried to ensure convergence
    # towards the global maximum.

```


```{r, echo=T, warning=F, message=F}
## Not run:
    #### estimation with 1 latent class (ng=1): independent models for the
    # longitudinal outcome and the time of event
library(lcmm)
head(data_lcmm)
    m1 <- Jointlcmm(fixed= Ydep1~X1*Time,random=~Time,subject='ID'
    ,survival = Surv(Tevent,Event)~ X1+X2 ,hazard="3-quant-splines"
    ,hazardtype="PH",ng=1,data=data_lcmm)
    #summary(m1)
    #Goodness-of-fit statistics for m1:
    #    maximum log-likelihood: -3944.77 ; AIC: 7919.54  ;  BIC: 7975.09
    ## End(Not run)

```

```{r, echo=T}
#### estimation with 2 latent classes (ng=2)
    m2 <- Jointlcmm(fixed= Ydep1~Time*X1,mixture=~Time,random=~Time,
    classmb=~X3,subject='ID',survival = Surv(Tevent,Event)~X1+mixture(X2),
    hazard="3-quant-splines",hazardtype="PH",ng=2,data=data_lcmm,
    B=c(0.64,-0.62,0,0,0.52,0.81,0.41,0.78,0.1,0.77,-0.05,10.43,11.3,-2.6,
    -0.52,1.41,-0.05,0.91,0.05,0.21,1.5))
    #summary(m2)
    #Goodness-of-fit statistics for m2:
    #       maximum log-likelihood: -3921.27; AIC: 7884.54; BIC: 7962.32

```

```{r, echo=T}
## Not run:
    #### estimation with 3 latent classes (ng=3)
    m3 <- Jointlcmm(fixed= Ydep1~Time*X1,mixture=~Time,random=~Time,
    classmb=~X3,subject='ID',survival = Surv(Tevent,Event)~ X1+mixture(X2),
    hazard="3-quant-splines",hazardtype="PH",ng=3,data=data_lcmm,
    B=c(0.77,0.4,-0.82,-0.27,0,0,0,0.3,0.62,2.62,5.31,-0.03,1.36,0.82,
    -13.5,10.17,10.24,11.51,-2.62,-0.43,-0.61,1.47,-0.04,0.85,0.04,0.26,1.5))
    #summary(m3)
    #Goodness-of-fit statistics for m3:
    #       maximum log-likelihood: -3890.26 ; AIC: 7834.53;  BIC: 7934.53

```

```{r, echo=T}
 #### estimation with 4 latent classes (ng=4)
    m4 <- Jointlcmm(fixed= Ydep1~Time*X1,mixture=~Time,random=~Time,
    classmb=~X3,subject='ID',survival = Surv(Tevent,Event)~ X1+mixture(X2),
    hazard="3-quant-splines",hazardtype="PH",ng=4,data=data_lcmm,
    B=c(0.54,-0.42,0.36,-0.94,-0.64,-0.28,0,0,0,0.34,0.59,2.6,2.56,5.26,
    -0.1,1.27,1.34,0.7,-5.72,10.54,9.02,10.2,11.58,-2.47,-2.78,-0.28,-0.57,
    1.48,-0.06,0.61,-0.07,0.31,1.5))
    #summary(m4)
    #Goodness-of-fit statistics for m4:
    #   maximum log-likelihood: -3886.93 ; AIC: 7839.86;  BIC: 7962.09
```

```{r, echo=T}
##### The model with 3 latent classes is retained according to the BIC
##### and the conditional independence assumption is not rejected at
##### the 5% level.
# posterior classification
plot(m3,which="postprob")
# Class-specific predicted baseline risk & survival functions in the
# 3-class model retained (for the reference value of the covariates)
plot(m3,which="baselinerisk",bty="l")
plot(m3,which="baselinerisk",ylim=c(0,5),bty="l")
plot(m3,which="survival",bty="l")
# class-specific predicted trajectories in the 3-class model retained
# (with characteristics of subject ID=193)
data <- data_lcmm[data_lcmm$ID==193,]
plot(predictY(m3,var.time="Time",newdata=data,bty="l"))
# predictive accuracy of the model evaluated with EPOCE
vect <- 1:15
cvpl <- epoce(m3,var.time="Time",pred.times=vect)
summary(cvpl)
plot(cvpl,bty="l",ylim=c(0,2))
############## end of example ##############
## End(Not run)
```

## lcmm-R package 

[lcmm R package can fit both GMM and LCGA](https://github.com/CecileProust-Lima/lcmm/issues/44)

* it handles both continuous longitudinal outcomes (Gaussian or non-Gaussian) as well as bounded quantitative, discrete and ordinal longitudinal outcomes

* program also works when no random-effect is included

### mixed models 

####  linear mixed model 

As in [Laird and Ware (1982)](https://www.jstor.org/stable/2529876?origin=crossref&seq=1#metadata_info_tab_contents), define linear mixed model 

$$Y_{ij}=X_{Li}(t_{ij})^T\beta+Z_i(t_{ij})^Tu_i+w_i(t_{ij})+\epsilon_{ij}$$

* $Y_{ij}$ outcome value of subject $i$ from accasion $j$.
* $X_{Li}(t_{ij}), Z_i(t_{ij})$ two vector of covariates 
* $\beta$ fixed efffect 
* $u_i$, random effect, follows $N(0, B)$
* $\epsilon_i \sim N(0, \sigma_{\epsilon}^2)$
* $w_i(.)$, zero mean Gaussian stochastic process, with $cov(w_i(t), w_i(s))=\sigma_w^2min(t,s)$

Aim: to estimate $(\beta, vec(B), \sigma_{\epsilon}^2, \sigma_w^2)$. 

#### Latent process mixed model 

Define it without measurement error 

$$\Lambda_{i}(t)=X_{Li}(t)^T\beta+Z_i(t)^Tu_i+w_i(t)$$
to define a flexible nonlinear measurement error model 

$$Y_{ij}=H(\Lambda_i(t_{ij})+\epsilon_{ij}, \eta)$$
$H$ is a paramerized link function and for a quantitative marker, $H^{-1}$ could be a  monotone increasing function. 

### Example 

This example is from [here](https://www.rdocumentation.org/packages/lcmm/versions/1.8.1.1/topics/lcmm)

```{r, echo=T, message=F, warning=F, eval=F}
library(lcmm)
#### Estimation of homogeneous mixed models with different assumed link
#### functions, a quadratic mean trajectory for the latent process and 
#### correlated random intercept and slope (the random quadratic slope 
#### was removed as it did not improve the fit of the data).
#### -- comparison of linear, Beta and 3 different splines link functions --
# linear link function
m10<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1,
data=data_lcmm,link="linear")
#summary(m10)
```
```{r, echo=T, message=F, warning=F, eval=F}
# Beta link function
m11<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1,
data=data_lcmm,link="beta")
#summary(m11)
#plot(m11,which="linkfunction",bty="l")
```

```{r,echo=T, message=F, warning=F, eval=F}
# I-splines with 3 equidistant nodes
m12<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1,
data=data_lcmm,link="3-equi-splines")
#summary(m12)
# I-splines with 5 nodes at quantiles
m13<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1,
data=data_lcmm,link="5-quant-splines")
#summary(m13)
# I-splines with 5 nodes, and interior nodes entered manually
m14<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1,
data=data_lcmm,link="5-manual-splines",intnodes=c(10,20,25))
#summary(m14)
#plot(m14,which="linkfunction",bty="l")
```

```{r, echo=T, message=F, warning=F, cache=T, eval=F}

# Thresholds
# Especially for the threshold link function, we recommend to estimate 
# models with increasing complexity and use estimates of previous ones 
# to specify plausible initial values (we remind that estimation of
# models with threshold link function involves a computationally demanding 
# numerical integration -here of size 3)
m15<-lcmm(Ydep2~Time+I(Time^2),random=~Time,subject='ID',ng=1
,data=data_lcmm,link="thresholds",maxiter=100,
B=c(-0.8379, -0.1103,  0.3832,  0.3788 , 0.4524, -7.3180,  0.5917,  0.7364,
 0.6530, 0.4038,  0.4290,  0.6099,  0.6014 , 0.5354 , 0.5029 , 0.5463,
 0.5310 , 0.5352, 0.6498,  0.6653,  0.5851,  0.6525,  0.6701 , 0.6670 ,
 0.6767 , 0.7394 , 0.7426, 0.7153,  0.7702,  0.6421))
#summary(m15)
#plot(m15,which="linkfunction",bty="l")
```

```{r, echo=T, message=F, warning=F, eval=F}
#### Plot of estimated different link functions:
#### (applicable for models that only differ in the "link function" used. 
####  Otherwise, the latent process scale is different and a rescaling
####  is necessary)
plot(m10,which="linkfunction",col=1,xlab="latent process",ylab="marker",
bty="l",xlim=c(-10,5),legend=NULL)
plot(m11,which="linkfunction",add=TRUE,col=2,legend=NULL)
plot(m12,which="linkfunction",add=TRUE,col=3,legend=NULL)
plot(m13,which="linkfunction",add=TRUE,col=4,legend=NULL)
plot(m14,which="linkfunction",add=TRUE,col=5,legend=NULL)
plot(m15,which="linkfunction",add=TRUE,col=6,legend=NULL)
legend(x="bottomright",legend=c("linear","beta","spl_3e","spl_5q","spl_5m","thresholds"),
col=1:6,lty=1,inset=.02,box.lty=0)
```

```{r, echo=T, message=F, warning=F, eval=F}
#### Estimation of 2-latent class mixed models with different assumed link 
#### functions with individual and class specific linear trend
#### for illustration, only default initial values where used but other
#### sets of initial values should also be tried to ensure convergence 
#### towards the golbal maximum
# Linear link function
m20<-lcmm(Ydep2~Time,random=~Time,subject='ID',mixture=~Time,ng=2,
idiag=TRUE,data=data_lcmm,link="linear",B=c(-0.98,0.79,-2.09,
-0.81,0.19,0.55,24.49,2.24))
#summary(m20)
#postprob(m20)
```

```{r, echo=T, message=F, warning=F, eval=F}
# Beta link function
m21<-lcmm(Ydep2~Time,random=~Time,subject='ID',mixture=~Time,ng=2,
idiag=TRUE,data=data_lcmm,link="beta",B=c(-0.1,-0.56,-0.4,-1.77,
0.53,0.14,0.6,-0.83,0.73,0.09))
summary(m21)
postprob(m21)
```

```{r, echo=T, message=F, warning=F, eval=F}
# I-splines link function (and 5 nodes at quantiles)
m22<-lcmm(Ydep2~Time,random=~Time,subject='ID',mixture=~Time,ng=2,
idiag=TRUE,data=data_lcmm,link="5-quant-splines",B=c(0.12,0.63,
-1.76,-0.39,0.51,0.13,-7.37,1.05,1.28,1.96,1.3,0.93,1.05))
summary(m22)
postprob(m22)

data <- data_lcmm[data_lcmm$ID==193,]
plot(predictL(m22,var.time="Time",newdata=data,bty="l"))
head(m22$pprob)
```

#### Reference 

* [Estimation of Extended Mixed Models Using Latent Classes and Latent Processes: The R Package lcmm](https://www.jstatsoft.org/article/view/v078i02)


## kml3d 

[kml3d](https://cran.r-project.org/web/packages/kml3d/kml3d.pdf) is a new implementation of k-means for longitudinal data (or trajectories).

* can deal with missing value (how?)
* By default, nbClusters is 2:6, with the maximum of 26, 20 times each 
* k-means is a "hill-climbing" algorithm, no guarantee of optimality

### Example 

#### Example 1

This is the [example](https://www.rdocumentation.org/packages/kml3d/versions/2.4.2/topics/kml3d)

```{r, echo=T, message=F, warning=F, eval=F}
library(kml3d)
### Generation of some data
cld1 <- generateArtificialLongData3d(15)
cld1
```

```{r, echo=T, message=F, warning=F, eval=F}
### We suspect 2, 3, 4 or 5 clusters, we want 3 redrawing.
###   We want to "see" what happen (so toPlot="both")
kml3d(cld1,2:5,3,toPlot="both")


### 3 seems to be the best.
###   We don't want to see again, we want to get the result as fast as possible.
###   Just, to check the overall process, we plot the criterion evolution
kml3d(cld1,3,10,toPlot="criterion")

```

#### Example 2 


```{r, echo=T, warning=F, message=F, eval=F}
library(kml3d)
# NOT RUN {
### 1. Data Preparation
data(pregnandiol)
head(pregnandiol)
names(pregnandiol)
cld3dPregTemp <- cld3d(pregnandiol,timeInData=list(temp=1:30*2,preg=1:30*2+1))

### 2. Building "optimal" clusteration (with only 2 redrawings)
###    Real analysis needs at least 20 redrawings
kml3d(cld3dPregTemp,3:5,nbRedrawing=2,toPlot="both")

### 3. Exporting results
try(choice(cld3dPregTemp))

### 4. Visualizing in 3D
plotMeans3d(cld3dPregTemp,4)
# }
```

