---
title: "pancreatic marker data analysis"
output: html_document
---

```{r, echo=F, warning=F, message=F}
library("readxl")
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(ggpubr)
library(lcmm)
library(survival)
```


## data mergering 

* handle missing values?

```{r, echo=F, message=F, warning=F}
path="C:/Shengtong/Research/Collaboration"
####### read into two data sets 
subdata1=read_excel(paste(path, "cA19-9_pancreatic_marker_data/2020-12-23 - Long format Chemo -- XRT.XLSX", sep="/"))
col_names_subdata1=colnames(subdata1)
subdata2=read_excel(paste(path, "cA19-9_pancreatic_marker_data/2020-12-23 - Wide format Chemo -- XRT.XLSX", sep="/"))
col_names_subdata2=colnames(subdata2)
#interest_column=union(col_names_subdata1[c(1,2,3,4,5,6, 10)], c("study_id_num",	"age", "gender", "race",	"bmi",	"metastatic", "diseaseprogression", "pfsmofromdx", 	"dead", 	"osmofromdx")) # only look at interested columns 
#pancreatic_data=full_join(subdata1, subdata2, by="study_id_num")%>% select(interest_column) %>%drop_na()  # be careful with missing value 

interest_column=c("study_id_num",  "day", "coded_time_point", "ca199_long", "osmofromdx", "dead") # start from the short list as more missing values comes in when including more variables 

pancreatic_data=full_join(subdata1, subdata2, by="study_id_num")%>% select(interest_column) %>%drop_na() 

surv.days=pancreatic_data%>%select(osmofromdx)*30  # both day and osmofromda need to be in same scale 
pancreatic_data=pancreatic_data%>%add_column(surv.days=surv.days$osmofromdx)

kable(pancreatic_data, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
#write.csv(pancreatic_data, file="C:\\Shengtong\\Research\\Collaboration\\cA19-9_pancreatic_marker_data\\pancreatic_marker_data.csv")
```

## kml3d 


### data format preparation 

```{r, echo=F, warning=F, message=F}
library(kml3d)
pancreatic_data_coded_time=pancreatic_data%>%filter(coded_time_point %in% c(0,2,10)) # only look at 3 coded time points 0, 2, 10. 
sub_id=unique(pancreatic_data_coded_time$study_id_num)

# find subjects with missing value at 0, 2, 10
sub_id_with_missing=numeric(); k=0
for (i in 1:length(sub_id))
  if (nrow(pancreatic_data_coded_time %>% filter(study_id_num==sub_id[i]))<3)
  {
      k=k+1
      sub_id_with_missing[k]=sub_id[i]
  }
# there are 67 among 219 subjects with incomplete records 
#clusterLongData3d(data.frame(pancreatic_data))
pancreatic_data_coded_time_no_missing=pancreatic_data_coded_time%>%filter(!(study_id_num %in% sub_id_with_missing)) # exclude subjects with missing values at at least one time point 
measure_at_0=seq(1,456, by=3) # extract index of time point to build array
measure_at_2=measure_at_0+1
measure_at_10=measure_at_0+2

num_sub=length(unique(pancreatic_data_coded_time_no_missing$study_id_num))
traj=array(c(pancreatic_data_coded_time_no_missing$ca199_long[measure_at_0], pancreatic_data_coded_time_no_missing$ca199_long[measure_at_2], pancreatic_data_coded_time_no_missing$ca199_long[measure_at_10]), dim=c(num_sub, 3,1))

# data preparation 
pancreatic_data_coded_time_no_missing_cluster=clusterLongData3d(traj=traj,
idAll=unique(pancreatic_data_coded_time_no_missing$study_id_num),
time=c(0,2,10)
#varNames=c("P","A"),
#maxNA=3
)
############### kml3d 
# run the method 
kml3d(pancreatic_data_coded_time_no_missing_cluster,2:6, nbRedrawing=2,toPlot="both")
# cluster 2:6
# 2 redrawings 
# plot both trajectory and criterion 

#try(choice(pancreatic_data_coded_time_no_missing_cluster))
#plotMeans3d(pancreatic_data_coded_time_no_missing_cluster,4)

################## try kml 

#kml(pancreatic_data_coded_time_no_missing_cluster,c(2,3,4,5,6),toPlot="both")

```



## lcmm 

### one cluster 

```{r, echo=T}
m10<-lcmm(ca199_long~day,random=~day,subject='study_id_num',ng=1,
data=data.frame(pancreatic_data),link="linear")
#summary(m10)
#plot(m10,which="linkfunction", bty="l")


m11<-lcmm(ca199_long~day,random=~day,subject='study_id_num',ng=1,
data=data.frame(pancreatic_data),link="beta")
#summary(m11)
#plot(m11,which="linkfunction", bty="l")


m12<-lcmm(ca199_long~day,random=~day,subject='study_id_num',ng=1,
data=data.frame(pancreatic_data),link="3-equi-splines")
#summary(m10)
#plot(m12,which="linkfunction", bty="l")

m13<-lcmm(ca199_long~day,random=~day,subject='study_id_num',ng=1,
data=data.frame(pancreatic_data),link="5-quant-splines")
#summary(m10)
#plot(m13,which="linkfunction", bty="l")

### Plot of estimated different link functions:
#### (applicable for models that only differ in the "link function" used.
plot(m10,which="linkfunction",col=1,xlab="latent process",ylab="marker",
bty="l",xlim=c(-10,5),legend=NULL)
plot(m11,which="linkfunction",add=TRUE,col=2,legend=NULL)
plot(m12,which="linkfunction",add=TRUE,col=3,legend=NULL)
plot(m13,which="linkfunction",add=TRUE,col=4,legend=NULL)
legend(x="bottomright",legend=c("linear","beta","spl_3e","spl_5q"),
col=1:6,lty=1,inset=.02,box.lty=0)
```

### two clusters 

```{r, echo=T}
# Beta link function
m21<-lcmm(ca199_long~day,random=~day,subject='study_id_num',mixture=~day,ng=2,
idiag=TRUE,data=data.frame(pancreatic_data),link="beta"
#B=c(-0.1,-0.56,-0.4,-1.77,
#0.53,0.14,0.6,-0.83,0.73,0.09)
)
summary(m21)
postprob(m21)

#The function plot.predict provides directly the plot of these class-specific predicted trajectories. The function predictY provides the class-specific predicted trajectories computed in the natural scale of the outcome(s).

data <- pancreatic_data[pancreatic_data$study_id_num==31,]
data
plot(predictL(m21,var.time="day",newdata=data,bty="l"))



#plot(m21,which="link",bty="l")
kable(m21$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
```

### 3 clusters 

```{r, echo=T}
# Beta link function
m31<-lcmm(ca199_long~day,random=~day,subject='study_id_num',mixture=~day,ng=3,
idiag=TRUE,data=data.frame(pancreatic_data),link="beta"
#B=c(-0.1,-0.56,-0.4,-1.77,
#0.53,0.14,0.6,-0.83,0.73,0.09)
)
#summary(m31)
#postprob(m31)

#The function plot.predict provides directly the plot of these class-specific predicted trajectories. The function predictY provides the class-specific predicted trajectories computed in the natural scale of the outcome(s).

data <- pancreatic_data[pancreatic_data$study_id_num==31,]
data
plot(predictL(m31,var.time="day",newdata=data,bty="l"))


#plot(m21,which="link",bty="l")
kable(m31$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
```

### 4 clusters 

```{r, echo=T}
# Beta link function
#m41<-lcmm(ca199_long~day,random=~day,subject='study_id_num',mixture=~day,ng=4,
#idiag=TRUE,data=data.frame(pancreatic_data),link="beta"
#B=c(-0.1,-0.56,-0.4,-1.77,
#0.53,0.14,0.6,-0.83,0.73,0.09)
#)
m41<-lcmm(ca199_long~day,random=~day,subject='study_id_num',mixture=~day,ng=4,
idiag=TRUE,data=data.frame(pancreatic_data),link="5-equi-splines"
#B=c(-0.1,-0.56,-0.4,-1.77,
#0.53,0.14,0.6,-0.83,0.73,0.09)
)

#link="3-equi-splines"



#summary(m41)
#postprob(m41)

#The function plot.predict provides directly the plot of these class-specific predicted trajectories. The function predictY provides the class-specific predicted trajectories computed in the natural scale of the outcome(s).

data <- pancreatic_data[pancreatic_data$study_id_num==52,]
data
plot(predictL(m41,var.time="day",newdata=data,bty="l"))


#plot(m21,which="link",bty="l")
kable(m41$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
```


#### Survival analysis 

* first cluster 

```{r, echo=T}
sub_data=pancreatic_data %>% filter(study_id_num %in% m41$pprob[which(m41$pprob$class==1),]$study_id_num) # extract subjects in class "1"
num_sub_data1=length(m41$pprob[which(m41$pprob$class==1),]$study_id_num)
model_fit1=survfit(Surv(surv.days,dead)~1, data=sub_data)
plot(model_fit1, xlab="Time", ylab="Overall survival probability", main="cluster 1")
```

* second cluster 

```{r, echo=F}
sub_data=pancreatic_data %>% filter(study_id_num %in% m41$pprob[which(m41$pprob$class==2),]$study_id_num) # extract subjects in class "2"
num_sub_data2=length(m41$pprob[which(m41$pprob$class==2),]$study_id_num)
model_fit2=survfit(Surv(surv.days,dead)~1, data=sub_data)
plot(model_fit2, xlab="Time", ylab="Overall survival probability", main="cluster 2")
```

* third cluster 

```{r, echo=F}
sub_data=pancreatic_data %>% filter(study_id_num %in% m41$pprob[which(m41$pprob$class==3),]$study_id_num) # extract subjects in class "3"
num_sub_data3=length(m41$pprob[which(m41$pprob$class==3),]$study_id_num)
model_fit3=survfit(Surv(surv.days,dead)~1, data=sub_data)
plot(model_fit3, xlab="Time", ylab="Overall survival probability", main="cluster 3")
```

* fourth cluster 

```{r, echo=F}
sub_data=pancreatic_data %>% filter(study_id_num %in% m41$pprob[which(m41$pprob$class==4),]$study_id_num) # extract subjects in class "4"
num_sub_data4=length(m41$pprob[which(m41$pprob$class==4),]$study_id_num)
model_fit4=survfit(Surv(surv.days,dead)~1, data=sub_data)
plot(model_fit4, xlab="Time", ylab="Overall survival probability", main="cluster 4")
```

```{r, echo=F}
plot(model_fit1, xlim=c(0,4000), ylim=c(0,1), xlab="Time", ylab="Survival", lty=1, col="black", conf.int = F)
lines(model_fit2, type="l", col="blue", conf.int = F)
lines(model_fit3, type="l", col="green", conf.int = F)
lines(model_fit4, type="l", col="red", conf.int = F)
legend(3000,1, legend=c("cluster 1", "cluster 2", "cluster 3", "cluster 4"), lty=c(1,1,1,1), col=c("black", "blue", "green", "red"))

num_sub_cluster=tibble(count=c(num_sub_data1, num_sub_data2, num_sub_data3, num_sub_data4), cluster=c(1,2,3,4))
ggplot(num_sub_cluster, aes(x=cluster, y=count)) +
  geom_bar(stat="identity", fill="blue")+
    ggtitle("No.sub in each cluster")+
    theme(plot.title = element_text(hjust = 0.5, size=10)) # center the title
```


### 5 clusters 

```{r, echo=T}
# Beta link function
m51<-lcmm(ca199_long~day,random=~day,subject='study_id_num',mixture=~day,ng=5,
idiag=TRUE,data=data.frame(pancreatic_data),link="beta"
#B=c(-0.1,-0.56,-0.4,-1.77,
#0.53,0.14,0.6,-0.83,0.73,0.09)
)
#summary(m51)
#postprob(m51)

#The function plot.predict provides directly the plot of these class-specific predicted trajectories. The function predictY provides the class-specific predicted trajectories computed in the natural scale of the outcome(s).

data <- pancreatic_data[pancreatic_data$study_id_num==31,]
data
plot(predictL(m51,var.time="day",newdata=data,bty="l"))


#plot(m21,which="link",bty="l")
kable(m51$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
```

```{r, echo=F}
fig1=plot(predictL(m11,var.time="day",newdata=data,bty="l", main="1 cluster"))
fig2=plot(predictL(m21,var.time="day",newdata=data,bty="l", main="2 clusters"))
fig3=plot(predictL(m31,var.time="day",newdata=data,bty="l", main="3 clusters"))
fig4=plot(predictL(m41,var.time="day",newdata=data,bty="l", main="4 clusters"))
fig5=plot(predictL(m51,var.time="day",newdata=data,bty="l", main="5 clusters"))
#figure=ggarrange(fig1, fig2, fig3, fig4, fig5,  common.legend = TRUE, legend="right") 
#annotate_figure(figure,top = text_grob(" class specific mean predicted trajectory", color = "red", face = "bold", size = 14))

```
### determine number of clusters 

```{r, echo=T}
# BIC criterion 
m11$BIC
m21$BIC
m31$BIC
m41$BIC
m51$BIC
## 1 cluster is chosen 
# log likelihood 
m11$loglik
m21$loglik
m31$loglik
m41$loglik
m51$loglik
## 5 clusters should be chosen 
```



## Jointlcmm 


This function doesn't work due to **Output can not be produced. The program stopped abnormally or there was an error in the computation
of the estimated baseline risk functions and survival functions.**



```{r, echo=F, eval=F}
m1 <- Jointlcmm(fixed=ca199_long~day+age+gender+race+bmi, random=~day	,subject="study_id_num"
    ,survival = Surv(surv.days,dead)~ age+gender+bmi ,hazard="piecewise"
    ,hazardtype="PH",ng=1,data=data.frame(pancreatic_data))
# race is not numeric 
## the input data must be data.frame!!!!!!
## variable in mixture must be from that in fixed 
## at least 3 nodes are required for spline function in hazard, but hazard="3-quant-splines", that is too strict to result in convergence issue 
summary(m1)
plot(m1)
```





```{r, echo=T, eval=F}
m2 <- Jointlcmm(fixed=ca199_long~day, mixture=~day, random=~day	,subject="study_id_num"
    ,survival = Surv(surv.days,dead)~age,hazard="piecewise"
    ,hazardtype="PH",ng=2,data=data.frame(pancreatic_data))
## race is not numeric 
## the input data must be data.frame!!!!!!
## variable in mixture must be from that in fixed 
## at least 3 nodes are required for spline function in hazard, but hazard="3-quant-splines", that is too strict to result in convergence issue
## don't use too many covariates in "fixed" 
summary(m2)
plot(m2, which="postprob")
kable(m2$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
plot(m2,which="survival",bty="l")
```



```{r, echo=F, eval=F}
m3 <- Jointlcmm(fixed=ca199_long~day, mixture=~day, random=~day	,subject="study_id_num"
    ,survival = Surv(surv.days,dead)~ age ,hazard="piecewise"
    ,hazardtype="PH",ng=3,data=data.frame(pancreatic_data))
## race is not numeric 
## the input data must be data.frame!!!!!!
## variable in mixture must be from that in fixed 
## at least 3 nodes are required for spline function in hazard, but hazard="3-quant-splines", that is too strict to result in convergence issue
summary(m3)
plot(m3, which="postprob")
kable(m3$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
plot(m3,which="survival",bty="l")
```




```{r, echo=F, eval=F}
m4 <- Jointlcmm(fixed=ca199_long~day, mixture=~day, random=~day	,subject="study_id_num"
    ,survival = Surv(surv.days,dead)~ age ,hazard="piecewise"
    ,hazardtype="PH",ng=4,data=data.frame(pancreatic_data))
## race is not numeric 
## the input data must be data.frame!!!!!!
## variable in mixture must be from that in fixed 
## at least 3 nodes are required for spline function in hazard, but hazard="3-quant-splines", that is too strict to result in convergence issue
summary(m4)
plot(m4, which="postprob")
kable(m4$pprob, caption = "")%>%
kable_styling() %>%
scroll_box(height = "500px")
plot(m4,which="survival",bty="l")
```